---
title: "DNA quanitifcation QAQC"
author: "Mariah Kachmar"
date: "4/29/2024"
output: html_document

Description: This code is used for molecular sample DNA quanitification quality control and assurance for the LISS funded Oyster Health Project. This samples were extracted using a Qiagen blood and tissue extraction kit. Quanitify of nucleic acids were determined using a Nanodrop2000 and dsDNA using a Qubit Flex. 


Updated: 06/05/24 M. Kachmar
  - combine new Qubit Files
  - Implemented datasheet clean up
    
---



#Set working directory
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
#knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
#knitr::opts_knit$set(root.dir = 'C:/Users/kelly.roper/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kelly's
```

#run packages
```{r}
library("ggplot2")
library("readxl")
library("plyr")                                     
library("dplyr")
library("Rmisc")
library("readr")  
library("lubridate")
library("purrr")
library(reshape2)
library(stringr)
library("RColorBrewer")
```

#### This code chunk merges all .csv files within the Tissue processing folder into one data fram and outputs the full dataset into a .csv master file. This allows us to download the raw data as a .csv, add it to the repository folder, and create the master data file without copying and pasting data in excel.
# reading in .csv files from local folder
```{r}

data_all <- list.files(path = "Lab_Data_DNAQuantification/raw_data",                           # Identify all CSV files
  pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>%                              # Store all files in list
  bind_rows                                         # Combine data sets into one data set 
data_all                                            # Print data to RStudio console

as.data.frame(data_all)                            # Convert tibble to data.frame


data_all <- data_all %>% filter(!is.na('Sample Name'))

data_all<- data_all %>% select(c('Test Date', 'Sample Name', 'Original Sample Conc.', 'Original sample conc. units'))

data_all <- data_all %>% rename(Date = 'Test Date', Sample_ID = 'Sample Name', Concentration = 'Original Sample Conc.', Units = 'Original sample conc. units')

data_all

write.csv(data_all, "Master_files\\DNA_quant_all_data.csv", row.names=FALSE)
```

```{r}
sessionInfo()
```