---
title: "BedCharacteristics_Oct2023Survey"
author: "Mariah Kachmar"
date: "12/13/2023"
output: html_document
updated: 3/19/2024
description: This R code is used to important and summarize bed characteristics (height, area, rugosity, density, and coverage) data from the LISS Oyster Health Project's October 2023 oyster population surveys at Ash Creek and Fence Creek intertidal sites in Connecticut and Goldstar Beach and Laurel Hollow subtidal sites in New York. 
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
#knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
#knitr::opts_knit$set(root.dir = 'C:/Users/kelly.roper/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kelly's
```


```{r, echo=FALSE}
library("dplyr")                                    
library("plyr")                                     
library("readr")             
library("Rmisc")
library("ggplot2")
library("lubridate")
```




```{r}
#Pulling all bed characteristic files
#data_all <- list.files(path = "Field_Data_Biological/raw_data/Characteristics",                           # Identify all CSV files
#  pattern = "*.csv", full.names = TRUE) %>% 
#  lapply(read_csv) %>% dplyr::bind_rows()

#data_all

#as.data.frame(data_all)

file_paths <- list.files(path = "Field_Data_Biological/raw_data/Characteristics",
                          pattern = "*.csv", full.names = TRUE)


data_all <- lapply(file_paths, function(file_path) {
  read_csv(file_path) %>%
    mutate(
      Percent_coverage = as.character(Percent_coverage)
    )
}) %>%
  bind_rows
as.data.frame(data_all) 

data_all <- data_all%>% filter(!is.na(Site))

View(data_all)

#cleaning up date date
data_all <- data_all %>%
  dplyr::rename(Date_collected = Date)

data_all<- data_all %>% mutate(Date_collected = as.Date(Date_collected,format = "%m/%d/%Y"))

#adding season columns
data_all <- data_all %>%
  mutate( month = month(Date_collected))
data_all <- data_all %>%
  mutate(Season = case_when(between(month, 5,6) ~"Spring",
                            between(month, 8,10) ~ "Fall"))
data_all <- select(data_all, -c("month"))
```


##### Bed height #####

```{r}
#Bed Height - creating master file

#removing unnecessary columns
bed_all <- select(data_all, -c("Field ID", "Quadrat_size", "Percent_coverage", "Live_count",
                                  "Box_count", "Gaper_count", "Rugosity", "Quadrat"))

bed_all <- na.omit(bed_all)
head(bed_all)

#renaming column
  bed_all <- bed_all %>% 
    dplyr::rename(Bed_height_cm =Bed_height)
  
#reordering columns
bed_all <- bed_all %>% select("Date_collected", "Site", "State", "Bed_height_cm", "Season")


```


#June 2023 (spring) survey for bed height. Changing June 2023 data to match formate of the data later collected. All data pulled form June 2023 is from the original file.
```{r}

bedheight_june2023 <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_BedHeight.csv") 


#Cleaning up June 2023 data
#renaming columns
bedheight_june2023 <- bedheight_june2023 %>%
  dplyr::rename(Date_collected = TripDate) %>%
  dplyr::rename(Bed_height_cm = BedHeight_cm)
  
bedheight_june2023$Date_collected <- as.Date(bedheight_june2023$Date_collected, format = "%m/%d/%Y")

#adding columns
bedheight_june2023$Season <- rep("Spring", nrow(bedheight_june2023))
bedheight_june2023$State <- rep("CT", nrow(bedheight_june2023))

#removing unnecessary columns
bedheight_june2023 <- select(bedheight_june2023, -c("BedHeight_Notes", "TopMark", "BottomMark", "Measure_direction", "Bed_Section"))

bedheight_june2023<- bedheight_june2023 %>%
  mutate(Site = recode(Site_Name, "Ash Creek" = "ASHC", "Fence Creek" = "FENC")) %>% 
  select(-c("Site_Name"))

head(bedheight_june2023)

#reordering columns
bedheight_june2023 <- bedheight_june2023 %>% select("Date_collected", "Site", "State", "Bed_height_cm", "Season")
```

```{r}
#Merging all bed height data into master file
Bedheight_master <- rbind(bed_all, bedheight_june2023)

write.csv(Bedheight_master, "Master_files/bed_height_all_data.csv", row.names = FALSE)
```

```{r}
#Summary of bed height at each site

bedheight_summary<- data_all %>%
  filter(!is.na(Live_count) & !is.na(Box_count) & !is.na(Gaper_count) & !is.na(Bed_height))
bedheight_summary 

bedheight_summary <- summarySE(data = Bedheight_master, measurevar = "Bed_height_cm", groupvars = c( "Date_collected", "Site"))

bedheight_summary

write.csv(bedheight_summary, "Field_Data_Biological/output/bedheight_summary.csv", row.names=FALSE)
```



#### Rugosity data ####
```{r}
#Rugosity - creating master file

#removing unnecessary columns
rugosity_all <- select(data_all, -c("Field ID", "Quadrat_size", "Percent_coverage", "Live_count",
                                  "Box_count", "Gaper_count","Bed_height", "Quadrat"))

rugosity_all <- na.omit(rugosity_all)
head(rugosity_all)
```
#June 2023 (spring) survey - rugosity data. Changing June 2023 data to match formate of the data later collected. All data pulled form June 2023 is from the original file.
```{r}
rugosity_june2023 <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_Rugosity.csv") 

#Cleaning up June 2023 data
#renaming columns
rugosity_june2023 <- rugosity_june2023 %>%
  dplyr::rename(Date_collected = TripDate)
rugosity_june2023$Date_collected <- as.Date(rugosity_june2023$Date_collected, format = "%m/%d/%Y")


#adding columns
rugosity_june2023$Season <- rep("Spring", nrow(rugosity_june2023))
rugosity_june2023$State <- rep("CT", nrow(rugosity_june2023))

#removing unnecessary columns
rugosity_june2023 <- select(rugosity_june2023, -c("RUGOS_NUM","ChainType", "Bed_Section", "Zone", "LengthContoured_cm", "LengthStraightline_cm","Notes"))

rugosity_june2023<- rugosity_june2023 %>%
  mutate(Site = recode(Site_Name, "Ash Creek" = "ASHC", "Fence Creek" = "FENC")) %>% 
  select(-c("Site_Name"))

head(rugosity_june2023)

#reordering columns
rugosity_june2023 <- rugosity_june2023 %>% select("Date_collected", "Site", "State", "Rugosity", "Season")
```

```{r}
#Merging all rugosity data into master file
Rugosity_master <- rbind(rugosity_all, rugosity_june2023)

write.csv(Rugosity_master, "Master_files/rugosity_all_data.csv", row.names = FALSE)
```

```{r}
#Summary of rugosity at each site

rugosity_summary<- data_all %>%
  filter(!is.na(Live_count) & !is.na(Box_count) & !is.na(Gaper_count) & !is.na(Bed_height))

rugosity_summary <- summarySE(data = Rugosity_master, measurevar = "Rugosity", groupvars = c( "Date_collected", "Site"))

rugosity_summary #Laural Hollow only has one rugosity measurement, so NAs will appear for the summary points

write.csv(rugosity_summary, "Field_Data_Biological/output/rugosity_summary.csv", row.names=FALSE)
```


#### Percent Coverage ####

#changing percent coverage categories
```{r}
#Percent Coverage - creating master file

percov_june2023 <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_QuadratDensity.csv") 


#Cleaning up June 2023 data
#renaming columns
percov_june2023 <- percov_june2023 %>%
  dplyr::rename(Date_collected = TripDate) %>%
dplyr::rename(Percent_coverage = Oyster_Cover)

percov_june2023$Date_collected <- factor(percov_june2023$Date_collected, levels = c("6/12/2023","6/14/2023"),
                                     labels = c("2023-06-12","2023-06-14"))
#adding columns
percov_june2023$Season <- rep("Spring", nrow(percov_june2023))
percov_june2023$State <- rep("CT", nrow(percov_june2023))

#removing unnecessary columns
percov_june2023 <- select(percov_june2023, -c("QUADRAT_NUM", "Quadrat_Type", "Quadrat_Zone", "Light_Zone", "Bed_Section", "LiveCount_Total", "GaperCount_Total", "BoxCount_Total", "Subsample_Measured", "Quadrat_Notes"))

percov_june2023<- percov_june2023 %>%
  mutate(Site = recode(Site_Name, "Ash Creek" = "ASHC", "Fence Creek" = "FENC")) %>% 
  select(-c("Site_Name"))

head(percov_june2023)

#Changing percent coverage categories to the current categories being used. In June 2023 there were different percent coverage categories being used, this change will help merge old and new data.
percov_june2023 <- percov_june2023 %>%
  mutate(Percent_coverage = dplyr::recode(Percent_coverage, 
                                    "0%" = "0-24", "1-25%" = "0-24", "26-50%" = "25-49", "51-75%"= "50-74", "76-99%"= "75-99", "100%"= "100"))

#reordering columns
percov_june2023 <- percov_june2023 %>% select("Date_collected", "Site", "State", "Percent_coverage", "Season")
```

```{r}
#October 2023 (fall) data. This data is in a different format compared to the other dates, where percent coverage is not binned.
#removing unnecessary columns
percent_coverage <- select(data_all, -c("Field ID", "Quadrat_size", "Rugosity", "Bed_height", "Quadrat", "Live_count", "Box_count", "Gaper_count"))

percent_coverage <- percent_coverage%>% filter(!is.na(Percent_coverage))

head(percent_coverage)

#Changing percent coverage to the current categories being used. In October 2023 there single percentages were being assigned, this change will help merge old and new data by putting the data points into categories.
percent_coverage$Percent_coverage <- as.factor(percent_coverage$Percent_coverage)
percent_coverage <- percent_coverage %>%
  mutate(Percent_coverage = dplyr::recode(Percent_coverage, 
                                    "15" = "0-24", "20" = "0-24", "25" = "25-49", "30" = "25-49", "40" = "25-49", "50"= "50-74", "80"= "75-99", "90"= "75-99", "100"= "100"))

#reordering columns
percent_coverage <- percent_coverage %>% select("Date_collected", "Site", "State", "Percent_coverage", "Season")

```


```{r}
#Merging all percent coverage data into master file
#Density measured in centimeters
Percentcoverage_master <- rbind(percent_coverage, percov_june2023)

#Removing all data with percent coverage less than 25%, as it is considered off of the oyster reef.
Percentcoverage_master$Percent_coverage[Percentcoverage_master$Percent_coverage == "0-24"] <- NA
Percentcoverage_master <- Percentcoverage_master%>% filter(!is.na(Percent_coverage))

#Write csv for master file of all percent coverage data
write.csv(Percentcoverage_master, "Master_files/percent_coverage_all_data.csv", row.names = FALSE)
```

```{r}
#Summary of percent cover at all sites
percentcover_summary <-  Percentcoverage_master %>%
  dplyr::group_by(Site, Season, Percent_coverage) %>%
  dplyr::summarize(Count = n())
percentcover_summary

write.csv(percentcover_summary, "Field_Data_Biological/output/percentcoverage_summary.csv", row.names=FALSE)

```


#oyster density metrics. QAQC_PopulationHeight script implements this code.
```{r}

#data_all <- data_all %>%
#  filter(!is.na(Live_count) & !is.na(Box_count) & !is.na(Gaper_count))
#data_all  

density_live_sum <- summarySE(data = data_all, measurevar = "Live_count", groupvars = c(  "Site", "Year", "Season"))
density_live_sum
density_live_sum <- density_live_sum %>%
  mutate(Count = Live_count) %>%
  select(-Live_count)


density_box_sum <- summarySE(data = data_all, measurevar = "Box_count", groupvars = c( "Site", "Year", "Season"))
density_box_sum <- density_box_sum %>%
  mutate(Count = Box_count) %>%
  select(-Box_count)
density_box_sum

density_gaper_sum <- summarySE(data = data_all, measurevar = "Gaper_count", groupvars = c( "Site", "Year", "Season"))
density_gaper_sum <- density_gaper_sum %>%
  mutate(Count = Gaper_count) %>%
  select(-Gaper_count)



density_summary<- rbind(density_gaper_sum, density_box_sum, density_live_sum)
density_summary

#sum total number of oysters counted per quadrat
 


```


# bed area calculations and heat map
```{r}
#Bed area calcualtions
# Load library 
library(leaflet)
library(dplyr)
library(gapminder)
library(tidyverse)
library(sf)
library(dplyr)
library(kml)
# Draw map
leaflet() %>%
  # Add first tile
  addTiles(group="One") %>%
  # Add second tile
  addProviderTiles(providers$Esri.WorldImagery, group="Two") %>%
  # Add first marker
  addMarkers(lng=-72.5863, lat=41.2719, group="Fence Creek",popup="Fence Creek, Madison") %>%
  # Add second marker
  addMarkers(lng=-73.2355, lat=41.1465, group="Ash Creek", popup = "Ash Creek, Fairfield") %>%
  # Add a third marker
  addMarkers(lng =-73.435313, lat = 40.89795, group = "Goldstar", popup = "Goldstar, Port Jeff")  %>%
  # Add Layer controls
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c("Fence Creek", "Ash Creek", "Goldstar"), 
                   options=layersControlOptions(collapsed=FALSE))


# should work to pull the data off the gps kml file ~ left side
kml_data <- sf::st_read('Field_Data_Biological/raw_data/Bed_area/0624ASHC_Left.kml')

kml_data <- sf::st_read('C:/Users/kelly.roper/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/raw_data/Bed_area/0624ASHC_Left.kml') # in case the the top is not loaded

kml_data$geometry

# trying to pull from the right kml file
kml_data2 <- sf::st_read('Field_Data_Biological/raw_data/Bed_area/0624ASHC_Right.kml')

#trying to elminate a row 
kml_data2 <- sf::st_read('Field_Data_Biological/raw_data/Bed_area/0624ASHC_Right.kml') %>% dplyr::rename(Coordinates =geometry, Right_Side_Coordinates = Name) %>% 
  select(-'Description')


  
#trying to eliminate a row from left side
kml_data <- sf::st_read('Field_Data_Biological/raw_data/Bed_area/0624ASHC_Left.kml') %>% dplyr::rename(Coordinates =geometry, Left_Side_Coordinates = Name) %>% 
  select(-'Description')


#for when the file is not found ~ eliminating row for left side reef
kml_data <- sf::st_read('C:/Users/kelly.roper/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/raw_data/Bed_area/0624ASHC_Left.kml') %>% dplyr::rename(Coordinates =geometry, Left_Side_Coordinates = Name) %>% 
  select(-'Description')

#for when the file is not found right side ashc ~ eliminating description column
kml_data2 <- sf::st_read('C:/Users/kelly.roper/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/raw_data/Bed_area/0624ASHC_Right.kml') %>% dplyr::rename(Coordinates =geometry, Right_Side_Coordinates = Name) %>% 
  select(-'Description')

kml_data

kml_data$Left_Side_Coordinates
kml_data$Coordinates

#made a data set with left side coordinates "kml_data"
mydf <- data.frame(Sites = c("Fence Creek", "Ash Creek", "Goldstar"),
                   Latitude = c(41.14643, 41.14642, 41.14641, 41.14638, 41.14650, 41.14660, 41.14661,41.14653, 41.14649),
                   Longitude = c(-73.23568,-73.23564,-73.23551,-73.23541,-73.23536,-73.23537, -73.23546,-73.23555,-73.23565,-73.23568),
stringAsFactors = FALSE)

#data frame for kml_data2
kml_right <- as.data.frame(kml_data2[[2]][[1]][[1]]) %>% 
  dplyr::select(!V3) %>% 
  dplyr::rename(Long=V1,
                Lat=V2)

#data frame for kml_data
kml_left <- as.data.frame(kml_data[[2]][[1]][[1]]) %>% 
  dplyr::select(!V3) %>% 
  dplyr::rename(Long=V1,
                Lat=V2)

view(kml_data2)

#kml_left$Long


#data frame for kml_data and kml_data2 again but with mutate
kml_left <- as.data.frame(kml_data[[2]][[1]][[1]]) %>%
  dplyr::select(!V3) %>%
  dplyr::rename(Long = V1,
                Lat = V2) %>%
  dplyr::mutate(Site = "Left")

kml_right <- as.data.frame(kml_data2[[2]][[1]][[1]]) %>%
  dplyr::select(!V3) %>%
  dplyr::rename(Long = V1,
                Lat = V2) %>%
  dplyr::mutate(Site = "Right")

# convert both right and left side of ash creek to one data frame
kml_final <- rbind(kml_left, kml_right)
View(kml_final)

#df.convert would be your kml_left and kml_right

#dev tools for kml understanding

#devtools::install_github("briatte/tidykml")
#library(tidykml)

#devtools::install_github("r-lib/remotes")
#options(timeout=99999999)
#getOption('timeout')

#install.packages("remotes", dependencies = TRUE)

kml_data2[,1]
kml_data[,1]

mydf <- data.frame(Sites = c("1", "2","3","4","5","6","7","8","9","10"), 
                   Latitude = c(41.14643, 41.14642, 41.14641, 41.14638, 41.14650, 41.14660, 41.14661,41.14653, 41.14649,41.14643), 
                   Longitude = c(-73.23568,-73.23564,-73.23551,-73.23541,-73.23536,-73.23537, -73.23546,-73.23555,-73.23565,-73.23568),
                   stringAsFactors = FALSE)

#this worked 
df <- data.frame(matrix(nrow = 10,ncol = 3)) # make a table template %>% 
colnames(df) <- c('Sites','Lat','Long')
df$Sites <- c("1", "2","3","4","5","6","7","8","9","10")
df$Lat <- c(41.14643, 41.14642, 41.14641, 41.14638, 41.14650, 41.14660, 41.14661,41.14653, 41.14649)
df$Long <- c(-73.23568,-73.23564,-73.23551,-73.23541,-73.23536,-73.23537, -73.23546,-73.23555,-73.23565,-73.23568)


view(kml_data2)

view(mydf)

#this is with handmaid data frame versus the kml_final
leaflet(data = mydf) %>% 
  addTiles(group="One") %>% 
  addProviderTiles(providers$Esri.WorldImagery,group = "Two") %>%
  addPolylines(lat = mydf$Latitude, lng = mydf$Longitude, color = "blue") %>% 
  addPopups(lat = ~Latitude, lng = ~Longitude,popup = ~Sites) %>% 
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c("Ash Creek"), 
                   options=layersControlOptions(collapsed=FALSE))

#this is the map with the data frames being separate has both left and right of the reef
leaflet() %>%
  # Add first tile
  addTiles(group="One") %>%
  # Add second tile
  addProviderTiles(providers$Esri.WorldImagery, group="Two") %>%
  # Add first marker
  addMarkers(lat = kml_left$Lat,lng = kml_left$Long, group="Left", popup = "Left Ash Creek, Fairfield") %>%
  # Add second marker
  addMarkers(lat = kml_right$Lat, lng = kml_right$Long, group="Right", popup = "Right Ash Creek, Fairfield") %>%
  # Add Layer controls
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c("Left Ash Creek", "Right Ash Creek"), 
                   options=layersControlOptions(collapsed=FALSE))

#map for the kml_final
leaflet() %>%
  # Add first tile
  addTiles(group="One") %>%
  # Add second tile
  addProviderTiles(providers$Esri.WorldImagery, group="Two") %>%
  # Add first marker
  addMarkers(lat = kml_final$Lat,lng = kml_final$Long, group="Left") %>%
  # Add popups
  addPopups(-73.23568, 41.14643,kml_data, options = popupOptions(closeButton = FALSE)) %>% 
  # Add Layer controls
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c("Ash Creek, Fairfield"), 
                   options=layersControlOptions(collapsed=FALSE))





#uploaded Fence Creek coordinates 
kml_fenc <- sf::st_read('Field_Data_Biological/raw_data/Bed_area/0624FENC.kml') %>% dplyr::rename(Coordinates =geometry, Fenc_Coordinates = Name) %>% 
  select(-'Description')

view(kml_fenc)

#below is if we wanted to rename column three like fence I think I would just have to not delete description and then we could bind Ashc and Fenc coordinates
#kml_fence <- as.data.frame(kml_fenc[[2]][[1]]) %>% 
  #dplyr::select(!V3) %>% 
 # dplyr::rename(Long=V1,
                #Lat=V2)

# without labeled site
kml_fence <- as.data.frame(kml_fenc[[2]][[1]][[1]]) %>% 
  dplyr::rename(Long=V1,
                Lat=V2)

#map<- paste(sep = "<br/>","fisheries.noaa.gov", "212 Rogers Ave", "Milford, CT")

#code for popup with url on ash creek and above is for noaa in milford
map2<- paste(sep = "<br/>","<b><a href='https://www.fisheries.noaa.gov/new-england-mid-atlantic/habitat-conservation/understanding-health-long-island-sounds-oyster-beds'>N.O.A.A.</a></b>", "Ash Creek","Fairfield, CT")

leaflet() %>% addTiles(group = "One") %>%
   addProviderTiles(providers$Esri.WorldImagery, group="Two") %>% 
  addPopups(-73.23568, 41.14643, map2,
    options = popupOptions(closeButton = FALSE))

#beneath says invalid map
leaflet(map2) %>% addTiles(group="One") %>%
   addProviderTiles(providers$Esri.WorldImagery, group="Two") %>%
  addPopups(-73.23568, 41.14643, map2,
    options = popupOptions(closeButton = FALSE) %>% # Add Layer controls
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c("Ash Creek"), 
                   options=layersControlOptions(collapsed=FALSE)))

#this works for ash creek with popup and layer control
leaflet() %>% addTiles(group="One") %>%
   addProviderTiles(providers$Esri.WorldImagery, group="Two") %>%
  addPopups(-73.23568, 41.14643, map2, group = "Ash Creek") %>% 
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c("Ash Creek"), 
                   options=layersControlOptions(collapsed=FALSE))
  

#<br/>","<b><a href='https://www.fisheries.noaa.gov/'>N.O.A.A.</a></b>", "Goldstar","Huntington, NY")

#https://www.fisheries.noaa.gov/new-england-mid-atlantic/habitat-conservation/understanding-health-long-island-sounds-oyster-beds

mapgoldstar<- paste(sep = "<br/>","<b><a href='https://www.fisheries.noaa.gov/new-england-mid-atlantic/habitat-conservation/understanding-health-long-island-sounds-oyster-beds'>N.O.A.A.</a></b>", "Goldstar",
            "Huntington, NY")


leaflet() %>% addTiles(group = "One") %>%
   addProviderTiles(providers$Esri.WorldImagery, group="Two") %>% 
  addPopups(-73.435303, 40.897870, mapgoldstar, group = "Gold Star") %>% 
  addLayersControl(baseGroups = c("One", "Two"),
                   overlayGroups = c("Gold Star"),
                   options = popupOptions(closeButton = FALSE))


#Starting of a heatmap need to add temperature range
library(leaflet.extras)
kml_final %>%
  leaflet() %>% 
  addTiles(group="One") %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Two") %>%
  addHeatmap(lng = kml_final$Long, lat = kml_final$Lat, blur = 40, max = 0.05, radius = 15, group = "Ash Creek") %>% 
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c("Ash Creek"), 
                   options=layersControlOptions(collapsed=FALSE))

#this does not work
library(leaflet.extras)
kml_final %>%
  leaflet() %>% 
  addTiles(group="One") %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Two") %>%
  addHeatmap(lng = kml_final$Long, lat = kml_final$Lat, blur = 40, max = 0.05, radius = 15, group = "Ash Creek") %>% 
   interp2xyz() |> as.data.frame()+
  scale_fill_gradientn("Long", na.value = NA,
  colours = c("blue", "green", "yellow", "orange")) %>% 
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c("Ash Creek"), 
                   options=layersControlOptions(collapsed=FALSE))

library(ggmap)
library(interp)

#mapheat <- get_stadiamap(qc, zoom = 7, maptype = "stamen_toner_lite")


#attempting to make a code for a heat map not working yet
ggmap() +
  geom_tile(aes(x = x, y = y, fill = z) ,
             data = with(kml_final, interp(Long, Lat, Temp, nx = 100, ny = 100,
                                       duplicate = "mean", extrap = TRUE)) |> 
               interp2xyz() |> as.data.frame()) +
  scale_fill_gradientn("Temperature", na.value = NA,
                       colours = c("blue", "green", "yellow", "orange"))





knitr::opts_knit$set(root.dir = 'C:/Users/kelly.roper/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance')

#pulling the temp data from sonde from one day from all three sites June 10 2024
tempmap <- read.csv("C:/Users/kelly.roper/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/raw_data/Bed_area/tempmap.csv")

view(tempmap)


#removed empty column
tempmap<- tempmap[, -7]
tempmap<- tempmap[, -7]
view(tempmap)

cleaned_tempmap <- tempmap %>% drop_na(Long, Lat)

view(cleaned_tempmap)

#can you just add "addheatmaps" to this and then it would work? -> had to delete N/A from coordinates this is just needs the temperature on top and a way to click the sights on and off
#add popups like (popup="Ash Creek, Fairfield", "Fence Creek, Madison", "Gold Star, Huntington")
library(ggplot2)

leaflet(cleaned_tempmap) %>%
  # Add first tile
  addTiles(group="One") %>%
  # Add second tile
  addProviderTiles(providers$Esri.WorldImagery, group="Two") %>% 
  #add heat map 
  addHeatmap(lng = cleaned_tempmap$Long, lat = cleaned_tempmap$Lat, blur = 40, max = 0.05, radius = 15, group = "Site") %>%
  # Add Layer controls
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c("Site"), 
                   options=layersControlOptions(collapsed=FALSE))




leaflet(cleaned_tempmap) %>%
  # Add first tile
  addTiles(group="One") %>%
  # Add second tile
  addProviderTiles(providers$Esri.WorldImagery, group="Two") %>% 
  #add heat map 
  addHeatmap(lng = cleaned_tempmap$Long, lat = cleaned_tempmap$Lat, blur = 40, max = 0.05, radius = 15, group = cleaned_tempmap$"Site") %>%
  # Add Layer controls
  addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c(cleaned_tempmap$"Site"), 
                   options=layersControlOptions(collapsed=FALSE)) %>% 
  leaflet.extras2::addPlayback(cleaned_tempmap,
                               time = "Date",
                               options = leaflet.extras2::playbackOptions(speed = 100))
library(sf)
df <- cleaned_tempmap %>% 
  dplyr::select(!X.1) %>% 
  dplyr::rename(lon = Long,
                lat = Lat) %>% 
  dplyr::mutate(datetime = lubridate::mdy_hm(Date)) %>% 
                # lat = signif(lat, digits = 3),
                # lon = signif(lon, digits = 3)) %>% 
  sf::st_as_sf(coords = c("lon", "lat"), crs = "WGS84", remove= F)

leaflet() %>% 
  addTiles() %>% 
  leaflet.extras2::addPlayback(data = df,
                               time = "datetime",
                               options = leaflet.extras2::playbackOptions(speed = 100000))

```

# more trying to make it into a temp map 
```{r}

#not sure
#hottempmap <- map_data("world") #ggplot2

#view(hottempmap)

#hottempmap <- left_join(hottempmap,tempmap, by= "lat")

#not sure if we need to remove the na in the lat and long -> update 8/29 "cleaned_tempmap" has N/A removed
#heatedmap <- tempmap %>% filter(!is.na(tempmap$Lat))

#tempmap1<-
  ggplot(cleaned_tempmap,aes(x = Long, y= Lat, group=Site))+
  geom_polygon(aes(fill=Temperature), color = "blue")




mapstatetemp <- colorNumeric("viridis", tempmap$Temperature)

label_state <- function(Lat,Long){
  str_glue("{Lat} with temperature of {Long}")
}
#doesnt work
tempmap %>% 
  leaflet() %>% 
  addPolygons(weight = 1,
              color = "white",
              fillColor = ~mapstatetemp(Temperature),
              fillOpacity = 1,
              popup = ~label_state(Sites, temperature)) %>% 
  addLegend(pal = mapstatetemp(),
            values = ~temperature,
            opacity = 1)


#comparison of temp between the sites from tempmap excel sheet
ggplot(tempmap, aes(x = tempmap$Date, y = tempmap$Temperature, color = Site ))+ geom_point() + labs(x = "Date (hours)", y = "Temperature (C)", title = "Date vs Temperature at 3 sites") +geom_smooth(method = "lm", se = FALSE)
#same but with facet wrap
ggplot(tempmap, aes(x = tempmap$Date, y = tempmap$Temperature, color = Site))+ geom_bin_2d() + labs(x = "Date (hours)", y = "Temperature (C)", title = "Date vs Temperature at 3 sites") +geom_smooth(method = "lm", se = FALSE)+ facet_wrap(~tempmap$Site)

#the date/time does not look right on the x axis
ggplot(
  cleaned_tempmap = cleaned_tempmap ,
  mapping = aes(x = cleaned_tempmap$Time, y = cleaned_tempmap$Temperature)
) +
  geom_point(aes(color = cleaned_tempmap$Site, shape= cleaned_tempmap$Site)) +
  geom_smooth(method = "lm") +
  labs(
    title = "Three Sites vs Water Temp",
    subtitle = "Fence Creek, Ash Creek, and Gold Star",
    x = "Date (hours)", y = "Temperature (C)",
    color = "Site", shape = "Site"
  ) 

#not working 
ggplot(tempmap) +
 geom_histogram(bins = 50, aes(x = tempmap$Site, y = tempmap$Temperature)) +
 xlab("Date") +
 ylab("Distribution") +
 ggtitle("Distribution of Temperature at three sites ") +
 theme_minimal() 


#leag add ons could be an option but we have to download from website
# leaflet-heatmap.js.
#
library(ggplot2)
library(gganimate)
library(gapminder)
library(plotly)
library(leaflet)
library(tidyverse)
library(sf)
library(mapview)

ggplot(cleaned_tempmap, aes(x = cleaned_tempmap$Site)) + geom_bar()

ggplot(tempmap, aes(x= tempmap$"Site", y = tempmap$"Temperature")) +geom_line()


library("ggpubr")
ggline(tempmap, x = "Site", y = "Temperature",
       add = c("mean_se", "jitter"),
       order = c("Ashc", "Gold", "Fenc"),
       ylab = "Temperature", xlab = "Site")




#does not work #cordtempmap <- st_as_sf(tempmap, coords = c(tempmap$"Long", tempmap$"Lat"),  crs = 4326)
library(gganimate)
library(ggplot2)
library(dplyr)
library(gapminder)
library(ggthemes)
library(leaflet)

graphgapminder = gapminder %>%
  ggplot(aes(x= gdpPercap, y = lifeExp, color = continent, size = pop)) +
  geom_point(alpha = 0.7, stroke = 0)+
  theme_fivethirtyeight()+
  scale_size(range =c(2,12), guide = "none")+
  scale_x_log10()+
  labs(title = "Life Expectancy vs GDP Per Capita by Country",
       x= "Income per person (GDP/capital)",
       y = "Life expectancy (years)",
       color = "Continent",
       caption = "Source: Gapminder")+
  theme(axis.title = element_text(),
        text = element_text(family = "Rubik"),
        legend.text = element_text(size = 10)) +
  scale_color_brewer(palette = "Set2")

graphgapminder

graphgapminder.animation = graphgapminder+
transition_time(year) +
  labs(subtitle = "Year: {frame_time}")+
  shadow_wake(wake_length = 0.1)

animate(graphgapminder.animation, height = 500, width = 800, fps = 30, duration = 10,
        end_pause = 60, res = 100)

pal <- colorNumeric(palette = "YlOrRd", domain = tempmap$Temperature)

leaflet(tempmap) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(lng = ~tempmap$Long, lat = tempmap$Lat, 
                   stroke = FALSE, radius = 6, fillOpacity = 0.8,
                   color = ~pal(Temperature))

leaflet(tempmap) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(lng = ~tempmap$Long, lat = ~tempmap$Lat, stroke = FALSE, radius = 6, 
                   color = ~pal(Temperature), fillOpacity = 0.7) %>%
  addLegend(position = "bottomright",
            pal = pal, values = ~Temperature, opacity = 1)

leaflet(cleaned_tempmap) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(lng = ~cleaned_tempmap$Long, lat = ~cleaned_tempmap$Lat, stroke = FALSE, radius = 6, color = ~pal(Temperature), fillOpacity = 0.7, 
                   popup = ~Temperature) %>%
  addLegend(position = "bottomright",
            pal = pal, values = ~Temperature, opacity = 1)


pal.gen <- colorFactor(palette = "Dark2", domain = cleaned_tempmap$Temperature)

  
leaflet(cleaned_tempmap) %>%
  # Add first tile
  addTiles(group="One") %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Two") %>%
  setView(lng = -6, lat = 37.38, zoom = 15) %>%
  addCircleMarkers(lng = ~cleaned_tempmap$Long, lat = ~cleaned_tempmap$Lat, stroke = FALSE, radius = 8, 
                   color = ~pal.gen(cleaned_tempmap$Temperature), fillOpacity = 0.7,
                   popup = ~leafpop::popupTable(cleaned_tempmap,
                                       zcol = c("Site", "Time", "Temperature"),
                                       row.numbers = FALSE, feature.id = FALSE)) %>% 
addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c(cleaned_tempmap$"Site"), 
                   options=layersControlOptions(collapsed=FALSE))

pal <- colorNumeric(palette = "YlOrRd", domain = cleaned_tempmap$Temperature)

leaflet(cleaned_tempmap) %>%
  # Add first tile
  addTiles(group="One") %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Two") %>%
  setView(lng = -6, lat = 37.38, zoom = 15) %>%
  addCircleMarkers(lng = ~cleaned_tempmap$Long, lat = ~cleaned_tempmap$Lat, stroke = FALSE, radius = 8, 
                   color = ,~pal(cleaned_tempmap$Temperature), fillOpacity = 0.7,
                   popup = ~leafpop::popupTable(cleaned_tempmap,
                                       zcol = c("Site", "Time", "Temperature"),
                                       row.numbers = FALSE, feature.id = FALSE)) %>% 
addLayersControl(baseGroups=c("One", "Two"), 
                   overlayGroups=c(cleaned_tempmap$"Site"), 
                   options=layersControlOptions(collapsed=FALSE))
```



```{r}
sessionInfo()
```