
---
title: "QAQC_PopulationSurveyMetrics"
author: "Mariah Kachmar"
date: "2023-06-29"
output: html_document

description: This R code is used to important and summarize shell height data from the LISS Oyster Health Project's 2023 oyster population surveys at Ash Creek and Fence Creek intertidal sites in Connecticut and Goldstar beach and Laurel Hollow subtidal sites on Long Island, NY. June 2023 data was originally input into the Access database (LISS_Database_FieldCollectionData_2023-07-18.accb) and files needed to be converted and standardize to the new collection method. All original or raw data can be accessed in the GitHub repository. 
---

Last updated 10/18/24 K. Lenderman




```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
```


```{r}
library(tidyverse)
library(gtools)
library(Rmisc)
library(gtools)
library(readxl)
library(plyr)
library(dplyr)
library(lubridate)
library(Rmisc)
library(ggplot2)
library(readr)
library(ggpubr)

```

```{r}
##Changed working directory for file path, should be able to use now (1/30/24)##
#### need to work on this chunk to read in all files at once - not ready to use  
#data_all <- list.files(path = "Field_Data_Biological",                                                               
 # pattern = "*.xlsx", full.names = TRUE) %>%         # Identify all xlsx files
 # lapply(read_excel)                           # Store all files in list
#
 # data_all                                            # Print data to RStudio console

#as.data.frame(data_all)                            # Convert tibble to data.frame





```

# Spring Survey Data - June 2023
```{r}

#read in all population survey sheets 


#June 2023
shellsize <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_ShellSize.csv") 

quadratdensity <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_QuadratDensity.csv") 

rugosity <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_Rugosity.csv") 

BedHeight <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_BedHeight.csv") 
```

#Cleaning up June 2023 survey data to be meragable with other data
```{r}

#renaming columns
shellsize <- shellsize %>% dplyr::rename(Date_collected = TripDate) %>% dplyr::rename(Quadrat = QUADRAT_NUM) %>% dplyr::rename(Height = Height_mm) %>% dplyr::rename(Survival_status = SpecimenType)
colnames(shellsize)
shellsize$Date_collected <- factor(shellsize$Date_collected, levels = c("6/12/2023","6/14/2023"),
                                     labels = c("2023-06-12","2023-06-14"))

#adding columns
shellsize$Season<- rep("Spring", nrow(shellsize))
shellsize$State<- rep("CT", nrow(shellsize))

#removing unneeded columns
shellsize<- select( shellsize, -c("QuadSpec_NUM", "Year", "Month", "Day", "Length_mm", "Width_mm", "Specimen_Notes")) 

#Changing site name and removing unneeded column
shellsize<- shellsize %>%
  mutate(Site = recode(Site_Name, "Ash Creek" = "ASHC", "Fence Creek" = "FENC")) %>% 
  select(-c("Site_Name"))

head(shellsize)

shellsize

#reorder columns
shellsize <- shellsize %>% select("Date_collected", "Site", "State", "Quadrat", "Height", "Survival_status", "Season")

```


# This chunk is exploritory for fall surveys. Thinking about best way to pull, clean, and merge data and best ways to standardize June and October survey data

#Pulling all height data into single sheet
```{r}

## Shell Height Data

# Use this code to reformat the dates to match

file_paths <- list.files(path = "Field_Data_Biological/raw_data/Height",
                          pattern = "*.csv", full.names = TRUE)


height_all <- lapply(file_paths, function(file_path) {
  read_csv(file_path) %>%
    mutate(
      Date_collected = as.Date(Date_collected,format = "%m/%d/%Y")
    )
}) %>%
  bind_rows
as.data.frame(height_all) 

#View(height_all)

#height_all <- list.files(path = "Field_Data_Biological/raw_data/Height",                           # Identify all CSV files
#  pattern = "*.csv", full.names = TRUE) %>% 
#  lapply(read_csv) %>%    # Store all files in list
#  bind_rows 

 

 #Removing 'Count' column
 height_all$Count<- NULL

#adding season columns

#height_all$Date_collected <- factor(height_all$Date_collected, levels = c("10/3/2023","10/5/2023", "10/16/2023", "10/17/2023" ),
#                                     labels = c("2023-10-03","2023-10-05","2023-10-16", "2023-10-17" ))
 height_all <- height_all %>%
  mutate(month = month(Date_collected))
 
height_all <- height_all %>%
  mutate(Season = case_when(between(month, 5,6) ~"Spring",
                            between(month, 8,10) ~ "Fall"))
height_all <- select(height_all, -c("month"))


```

#Cleaning up height data
```{r}

# Subset by category height (live, box, gaper)

#Live

height_live <- select(height_all, 'Field ID', 'Date_collected', 'Site', 'State', 'Quadrat','Height_live', 'Season')
height_live <- na.omit(height_live)
height_live$Survival_status<- rep("Live", nrow(height_live))
height_live <- height_live %>% dplyr::rename(Height = Height_live)
height_live


#Box

height_box <- select(height_all, 'Field ID', 'Date_collected', 'Site', 'State', 'Quadrat','Height_box', 'Season')
height_box <- na.omit(height_box)
height_box$Survival_status<- rep("Box", nrow(height_box))
height_box <- height_box %>% dplyr::rename(Height = Height_box)

#Gaper

height_gaper <- select(height_all, 'Field ID', 'Date_collected', 'Site', 'State', 'Quadrat','Height_gaper', 'Season')
height_gaper <- na.omit(height_gaper)
height_gaper$Survival_status<- rep("Gaping", nrow(height_gaper))
height_gaper <- height_gaper %>% dplyr::rename(Height = Height_gaper)

Height_all<- rbind(height_live,height_box,height_gaper)
Height_all

Height_all$`Field ID`<- NULL

#reorder columns
Height_all <- Height_all %>% select("Date_collected", "Site", "State", "Quadrat", "Height", "Survival_status", "Season")

```

#Merging spring and fall 2023,2024 Height data
```{r}

Height_master<- rbind(Height_all, shellsize)
Height_master

Height_master<-na.omit(Height_master)

Height_master$Year<- year(Height_master$Date_collected)

View(Height_master)
# Output to repository
write_csv(Height_master, path= "Master_files/height_all_data.csv") #row.names=FALSE)


```
#Oyster density metrics
```{r}

#Merge all quadrates data from surveys 
#Sum total number of oyster counter per quadrat

#This code does not include the oysters above 100 (which are not included in the height_master)
#quadratdensity_all_old<- Height_master %>%
#  dplyr::group_by(Quadrat, Season, Year, Survival_status, Site, Date_collected, State) %>%
#  dplyr::summarize(Count = n())
#quadratdensity_all_old

quadratdensity_all <- read.csv("Field_Data_Biological//raw_data//Population_survey_density.csv") 

#summary of each oyster type by site. output = Site, N, Mean, stnd dev, stnd error, and confidence interval
all_density_SE <-summarySE(data = quadratdensity_all, measurevar = "Count", groupvars=c("Site", "Survival_status", "Season", "Date_collected"))
all_density_SE

#calculate percent standard error as 100*se/mean
all_density_SE$PSE_all <- 100*(all_density_SE$se/all_density_SE$Count)

#calculate completeness as 100*N/4, where 4 is the desired number of quadrats per site. 2023 surveys had 12 quadrates measured. 
  densitysummary <- all_density_SE %>%
    mutate(PercentComplete_Quad = ((N/4)*100))
densitysummary


write_csv(densitysummary, "Field_Data_Biological/Output/populationdensity_summary.csv") #, row.names=FALSE)

```
```{r}
#changing density master. Create new master with "all quadrat" data and do not use data from height master
```

#oyster size distribution
```{r}

Height_master$Year<- year(Height_master$Date_collected)
      
shellsize_all <- 
  Height_master %>% dplyr::group_by(Site, Season, Year) %>%
  dplyr::summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
 dplyr:: mutate(Survival_status = "All")
shellsize_all

shellsize_live <- 
  Height_master %>% dplyr::group_by(Site, Season, Year) %>% dplyr::filter(Survival_status=="Live") %>%
   dplyr::summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  dplyr::mutate(Survival_status = "Live")
shellsize_live

shellsize_box <- 
  Height_master %>%  dplyr::group_by(Site, Season, Year) %>% dplyr::filter(Survival_status=="Box") %>%
   dplyr::summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  dplyr::mutate(Survival_status = "Box")

shellsize_gaper <- 
  Height_master %>%  dplyr::group_by(Site, Season, Year) %>% dplyr::filter(Survival_status=="Gaping") %>%
   dplyr::summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  dplyr::mutate(Survival_status = "Gaper")

#rbind together 

shellsize_summary <- rbind(shellsize_all, shellsize_live, shellsize_box, shellsize_gaper)
shellsize_summary

#size distribution summary
#note that calculating PSE and accuracy do not make sense for size distributions. Will need to figure out new metrics for the QAPP
write_csv(shellsize_summary, "Field_Data_Biological/Output/shellsize_summary.csv") #, row.names=FALSE)
```

#graphing shell height all sites
```{r}


ggplot(Height_master, aes(x=Season, y=Height, fill=Site)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
  facet_wrap(~Site +Year)

```

#ASHC
```{r}
#graphing shell height ASHC

height_ASHC<- Height_master %>% filter(Site == "ASHC")

#height_ASHC<- height_ASHC %>%
#  mutate(Month = recode(Season, "fall" = "October", "spring" = "June")) 

live_height_ASHC<- height_ASHC %>%
 group_by(Site, Season)%>%
  filter(Survival_status == "Live")%>%
  summarize(Mean_Height = mean(Height))
live_height_ASHC

#How many animals fall within the distributions
# Define size bins (modify these according to your size ranges)
size_breaks <- seq(0, 190, by = 10)  # Define size breaks (0, 10, 20, 30, 40, 50)
size_labels <- paste(size_breaks[-length(size_breaks)], size_breaks[-1], sep = "-")  # Labels for size ranges

# Create size bins and count animals in each bin
height_ASHC$Size_Group <- cut(height_ASHC$Height, breaks = size_breaks, labels = size_labels)
animals_count <- table(height_ASHC$Size_Group)
animals_count

# Display the count of animals in each size range
print(animals_count)


#Subset by survival status
height_ASHC_Live <- height_ASHC[height_ASHC$Survival_status == "Live",]
print(height_ASHC_Live)
height_ASHC_Live

height_ASHC_Dead <- height_ASHC[height_ASHC$Survival_status == "Box"|height_ASHC$Survival_status == "Gaper",]
print(height_ASHC_Dead)

#plots
ggplot(height_ASHC, aes(x=factor(Season, levels = c("Spring", "Fall")), y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12)) + facet_wrap(~Year)

#Distribution Live
ASHC_Distribution_Live<-ggplot(data=height_ASHC_Live, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Height Live Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,190), breaks = seq(0,190, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))+
 facet_wrap(~ factor(Season, levels = c("Spring", "Fall")) + Year, scales = "free", ncol = 2, nrow=2)
ASHC_Distribution_Live
pdf(paste0(path = "Field_Data_Biological/Output/ASHC_Distribution_Live.pdf"), height = 6, width = 11)
print(ASHC_Distribution_Live)
dev.off()

#Distribution Dead
ASHC_Distribution_Dead<-ggplot(data=height_ASHC_Dead, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Height Dead Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,190), breaks = seq(0,190, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))+
   facet_wrap(~ factor(Season, levels = c("Spring", "Fall")) + Year, scales = "free", ncol = 2, nrow=2)
ASHC_Distribution_Dead
pdf(paste0(path = "Field_Data_Biological/Output/ASHC_Distribution_Dead.pdf"), height = 6, width = 11)
print(ASHC_Distribution_Dead)
dev.off()

```

#ASHC Density and mortality
```{r}


df_quadrat_ASHC <- quadratdensity_all%>%
  filter(Site == "ASHC") %>% filter(!Count == "0")
df_quadrat_ASHC

#Quadrat size is 25 x25cm (.0625 m^2). To calculate density (oysters per m^2) multiply number of oysters counted X 16

df_density_ASHC <- df_quadrat_ASHC %>%
  dplyr::group_by(Site, Season, Quadrat, Survival_status, Year) %>% 
  dplyr::summarize(Density = sum(Count)*16)
df_density_ASHC

#Mean of Oysters per m^2 across all quadrats
mean_total_oysters_ASHC <- df_density_ASHC %>%
 dplyr:: group_by(Site, Season, Survival_status, Year, Quadrat) %>%
 dplyr::summarize(Total_Density = mean(Density))
mean_total_oysters_ASHC

survival_sum_ASHC <- summarySE(mean_total_oysters_ASHC, "Total_Density", groupvars=c( "Season", "Survival_status", "Year")) #creating stats (sd, se, ci) about data
 

#Density per quadrat totals - 2023
df_quadrat_ASHC_2023 <- df_quadrat_ASHC %>% filter(Year == "2023")
d.2023 <- ggplot(data=df_quadrat_ASHC_2023, aes(x= Survival_status, y = Count, fill = Survival_status)) +
  geom_bar( stat="identity", show.legend = FALSE)+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Count - 2023 ", x ="Survival status", y= "Density")+
  facet_wrap(~ factor(Season, levels = c("Spring", "Fall")), scales = "free")+
  scale_color_brewer("Accent")
#+geom_text(aes(label=Count ), vjust=-0.3, size = 3.5)

#Density per quadrat totals - 2024
df_quadrat_ASHC_2024 <- df_quadrat_ASHC %>% filter(Year == "2024")
d.2024<- ggplot(data=df_quadrat_ASHC_2024, aes(x= Survival_status, y = Count, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Count - 2024 ", x ="Survival status", y= "Density")+
  facet_wrap(~ factor(Season, levels = c("Spring", "Fall")), scales = "free")
#+geom_text(aes(label=Count ), vjust=-0.3, size = 3.5)
ggarrange(d.2023, d.2024)

d.2024
#Density of oysters per meter squared - 2023
mean_total_oysters_ASHC_2023 <- mean_total_oysters_ASHC %>% filter(Year == "2023")
ggplot(data=survival_sum_ASHC, aes(x= Survival_status, y = Total_Density, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Density", x ="Survival status", y= "Density (# oyster / meter squared)")+
  facet_grid(Season ~Year)+
  geom_errorbar(aes(ymin=Total_Density-se, ymax=Total_Density+se), width=.2, position=position_dodge(.9))


#Density of oysters per meter squared - 2024
mean_total_oysters_ASHC_2024 <- mean_total_oysters_ASHC %>% filter(Year == "2024")
ggplot(data=mean_total_oysters_ASHC_2024, aes(x= Survival_status, y = Total_Density, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Density - 2024 ", x ="Survival status", y= "Density (# oyster / meter squared)")+
  facet_wrap(~ factor(Season, levels = c("Spring", "Fall")), scales = "free")+
 geom_text(aes(label=Total_Density), vjust=-0.3, size = 3.5)

```
#FENC

```{r}
#graphing shell height FENC

height_FENC<- Height_master %>% filter(Site == "FENC")

#View(height_FENC)

#height_FENC<- height_FENC %>%
#  mutate(Month = recode(Season, "fall" = "October", "spring" = "June")) 

live_height_FENC<- height_FENC %>%
 group_by(Site, Season, Year)%>%
  filter(Survival_status == "Live")%>%
  summarize(Mean_Height = mean(Height))
live_height_FENC

#How many animals fall within the distributions
# Define size bins (modify these according to your size ranges)
size_breaks <- seq(0, 240, by = 10) # Define size breaks (0, 10, 20, 30, 40, 50)
size_labels <- paste(size_breaks[-length(size_breaks)], size_breaks[-1], sep = "-")  # Labels for size ranges

height_FENC$Size_Group <- cut(height_FENC$Height, breaks = size_breaks, labels = size_labels)
animals_count <- table(height_FENC$Size_Group)
animals_count

# Display the count of animals in each size range
print(animals_count)

#Subset by survival status
height_FENC_Live <- height_FENC[height_FENC$Survival_status == "Live",]
print(height_FENC_Live)
height_FENC_Live

height_FENC_Dead <- height_FENC[height_FENC$Survival_status == "Box"|height_FENC$Survival_status == "Gaper",]
print(height_FENC_Dead)

#plots
ggplot(height_FENC, aes(x=factor(Season, levels = c("Spring", "Fall")), y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height Fence Creek", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
 facet_grid(~ Year)

#Distribution Live
FENC_Distribution_Live<-ggplot(data=height_FENC_Live, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Fence Creek Height Live Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,200), breaks = seq(0,200, by =10) )+
  scale_y_continuous(limits = c(0,100), breaks = seq(0,100, by = 10))+
 facet_wrap(~ factor(Season, levels = c("Spring", "Fall")) + Year,  scales = "free", ncol = 2, nrow=2)
FENC_Distribution_Live
pdf(paste0(path = "Field_Data_Biological/Output/FENC_Distribution_Live.pdf"), height = 6, width = 11)
print(FENC_Distribution_Live)
dev.off()

#Distribution Dead
FENC_Distribution_Dead<-ggplot(data=height_FENC_Dead, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Fence Creek Height Dead Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,180), breaks = seq(0,180, by =10) )+
  scale_y_continuous(limits = c(0,50), breaks = seq(0,50, by = 5))+
   facet_wrap(~ factor(Season, levels = c("Spring", "Fall")) + Year,  scales = "free", ncol = 2, nrow=2)
FENC_Distribution_Dead
pdf(paste0(path = "Field_Data_Biological/Output/FENC_Distribution_Dead.pdf"), height = 6, width = 11)
print(FENC_Distribution_Dead)
dev.off()


#ggplot(data=height_FENC, aes(x= Height)) +
#  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
#  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
#  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
#  labs(title="Fence Creek Creek Height ", x ="Height (mm)")+
 # facet_wrap(~ factor(Season, levels = c("Spring", "Fall")) + Year, scales = "free", ncol = 1)

```

#FENC density and mortality calculations
```{r}

df_quadrat_FENC <- quadratdensity_all%>%
  filter(Site == "FENC")
df_quadrat_FENC


#Quadrat size is 25 x25cm (.0625 m^2). To calculate density (oysters per m^2) multiply number of oysters counted X 16

df_density_FENC <- df_quadrat_FENC %>%
  dplyr::group_by(Site, Season, Quadrat, Survival_status, Year) %>% 
  dplyr::summarize(Density = sum(Count)*16)
df_density_FENC




#Mean of Oysters per m^2 across all quadrats
mean_total_oysters_FENC <- df_density_FENC %>%
  dplyr::group_by(Site, Season, Survival_status, Year, Quadrat) %>%
  dplyr::summarize(Total_Density = mean(Density))
mean_total_oysters_FENC

survival_sum_FENC <- summarySE(mean_total_oysters_FENC, "Total_Density", groupvars=c( "Season", "Survival_status", "Year")) #creating stats (sd, se, ci) about data

#Density per quadrat totals
ggplot(data=survival_sum_FENC, aes(x= Survival_status, y = Density, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  geom_errorbar(aes(ymin=Density-se, ymax=Density+se), width=.2, position=position_dodge(.9))+
  labs(title="Fence Creek Count ", x ="Survival status", y= "Density")+
  facet_wrap(Year ~ Season)

#Density of oysters per meter squared
ggplot(data=survival_sum_FENC, aes(x= Survival_status, y = Total_Density, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
    geom_errorbar(aes(ymin=Total_Density-se, ymax=Total_Density+se), width=.2, position=position_dodge(.9))+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Fence Creek Density ", x ="Survival status", y= "Density (# oyster / meter squared)")+
  facet_grid(Year ~ Season)


```

#GOLD
```{r}
#graphing shell height GOLD

height_GOLD<- Height_master %>% filter(Site == "GOLD")
height_GOLD

#height_GOLD<- height_GOLD %>%
#  mutate(Month = recode(Season, "fall" = "October", "spring" = "June")) 

live_height_GOLD<- height_GOLD %>%
 group_by(Site, Season, Year)%>%
  filter(Survival_status == "Live")%>%
  summarize(Mean_Height = mean(Height))
live_height_GOLD

#How many animals fall within the distributions
# Define size bins (modify these according to your size ranges)
size_breaks <- seq(0, 190, by = 10)  # Define size breaks (0, 10, 20, 30, 40, 50)
size_labels <- paste(size_breaks[-length(size_breaks)], size_breaks[-1], sep = "-")  # Labels for size ranges

# Create size bins and count animals in each bin
height_GOLD$Size_Group <- cut(height_GOLD$Height, breaks = size_breaks, labels = size_labels)
animals_count <- table(height_GOLD$Size_Group)
animals_count

# Display the count of animals in each size range
print(animals_count)

#plots
class(height_GOLD$Month)
height_GOLD

height_GOLD_Live <- height_GOLD[height_GOLD$Survival_status == "Live",]
print(height_GOLD_Live)

height_GOLD_Dead <- height_GOLD[height_GOLD$Survival_status == "Box"|height_GOLD$Survival_status == "Gaper",]
print(height_GOLD_Dead)

ggplot(height_GOLD, aes(x = Year, y = Height, fill = Year)) +
  geom_boxplot() +  
  theme_bw() +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(title = "Shell Height", x = "Year", y = "Height (mm)") +
  theme(axis.title.y = element_text(size = rel(1.3), angle = 90), axis.title.x = element_text(size = rel(1.3), angle = 0)) +
  theme(axis.text = element_text(size = 12))

#Distribution Live
GOLD_Distribution_Live<-ggplot(data=height_GOLD_Live, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Gold Star Beach Height Live Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,170), breaks = seq(0,170, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))+
  facet_wrap(~ Year, scales = "free", ncol = 1)
GOLD_Distribution_Live
pdf(paste0(path = "Field_Data_Biological/Output/GOLD_Distribution_Live.pdf"), height = 6, width = 11)
print(GOLD_Distribution_Live)
dev.off()

#Distribution Dead
GOLD_Distribution_Dead<-ggplot(data=height_GOLD_Dead, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Gold Star Beach Height Dead Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,170), breaks = seq(0,170, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))+
  facet_wrap(~ Year, scales = "free", ncol = 1)
GOLD_Distribution_Dead
pdf(paste0(path = "Field_Data_Biological/Output/GOLD_Distribution_Dead.pdf"), height = 6, width = 11)
print(GOLD_Distribution_Dead)
dev.off()

```
#GOLD density & mortality
```{r}
df_quadrat_GOLD <- quadratdensity_all%>%
  filter(Site == "GOLD")
df_quadrat_GOLD

#Quadrat size is 50 x50cm (.25 m^2). To calculate density (oysters per m^2) multiply number of oysters counted X 4 to = 1 meter

df_density_GOLD <- df_quadrat_GOLD %>%
  dplyr::group_by(Site, Season, Year, Date_collected, Quadrat, Survival_status) %>% 
  dplyr::summarize(Density = sum(Count)*4)
df_density_GOLD

#Mean of Oysters per m^2 across all quadrats
mean_total_oysters_GOLD <- df_density_GOLD %>%
  dplyr::group_by(Site, Season, Year, Date_collected, Survival_status, Quadrat) %>%
  dplyr::summarize(Total_Density = mean(Density))
mean_total_oysters_GOLD
 
survival_sum_GOLD <- summarySE(mean_total_oysters_GOLD, "Total_Density", groupvars=c( "Season", "Survival_status", "Year")) #creating stats (sd, se, ci) about data
survival_sum_GOLD <- survival_sum_GOLD[-c(3,4),]

#Density per quadrat totals
ggplot(data=df_quadrat_GOLD, aes(x= Survival_status, y = Count, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Gold Star Count ", x ="Survival status", y= "Density")+
  facet_wrap(~ Year, scales = "free")

#Density of oysters per meter squared
ggplot(data=survival_sum_GOLD, aes(x= Survival_status, y = Total_Density, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Gold Star Density ", x ="Survival status", y= "Density (# oyster / meter squared)")+
  geom_errorbar(aes(ymin=Total_Density-se, ymax=Total_Density+se), width=.2, position=position_dodge(.9))+
  facet_grid(~ Year)
```


#LAUR
```{r}
#graphing shell height LAUR

height_LAUR<- Height_master %>% filter(Site == "LAUR")

height_LAUR<- height_LAUR %>%
  mutate(Month = recode(Season, "fall" = "October", "spring" = "June")) 

ggplot(height_LAUR, aes(x=Season, y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

live_height_LAUR<- height_LAUR %>%
 group_by(Site, Season)%>%
  filter(Survival_status == "Live")%>%
  summarize(Mean_Height = mean(Height))
live_height_LAUR

#How many animals fall within the distributions
# Define size bins (modify these according to your size ranges)
size_breaks <- seq(0, 190, by = 10)  # Define size breaks (0, 10, 20, 30, 40, 50)
size_labels <- paste(size_breaks[-length(size_breaks)], size_breaks[-1], sep = "-")  # Labels for size ranges

# Create size bins and count animals in each bin
height_LAUR$Size_Group <- cut(height_LAUR$Height, breaks = size_breaks, labels = size_labels)
animals_count <- table(height_LAUR$Size_Group)
animals_count

# Display the count of animals in each size range
print(animals_count)

#plots
class(height_LAUR$Month)
height_LAUR

height_LAUR_Live <- height_LAUR[height_LAUR$Survival_status == "Live",]
print(height_LAUR_Live)

height_LAUR_Dead <- height_LAUR[height_LAUR$Survival_status == "Box"|height_LAUR$Survival_status == "Gaper",]
print(height_LAUR_Dead)

ggplot(height_LAUR, aes(x = Date_collected, y = Height, color = Date_collected)) +
  geom_boxplot() +  
  theme_bw() +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(title = "Shell Height", x = "Month", y = "Height (mm)") +
  theme(axis.title.y = element_text(size = rel(1.3), angle = 90), axis.title.x = element_text(size = rel(1.3), angle = 0)) +
  theme(axis.text = element_text(size = 12))

#Distribution Live
ggplot(data=height_LAUR_Live, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Laurel Hollow Height Live Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,170), breaks = seq(0,170, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))
 # facet_wrap(~ Month, scales = "free", ncol = 1)

#Distribution Dead
ggplot(data=height_LAUR_Dead, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Laurel Hollow Height Dead Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,170), breaks = seq(0,170, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))

```
#LAUR density & mortality
```{r}
df_quadrat_LAUR <- quadratdensity_all%>%
  filter(Site == "LAUR")
df_quadrat_LAUR

#Quadrat size is 50 x50cm (.25 m^2). To calculate density (oysters per m^2) multiply number of oysters counted X 4

df_density_LAUR <- df_quadrat_LAUR %>%
  dplyr::group_by(Site, Season, Quadrat, Survival_status) %>% 
  dplyr::summarize(Density = sum(Count)*4)
df_density_LAUR

#Mean of Oysters per m^2 across all quadrats
mean_total_oysters_LAUR <- df_density_LAUR %>%
  dplyr::group_by(Site, Season, Survival_status) %>%
  dplyr::summarize(Total_Density = mean(Density))
mean_total_oysters_LAUR
 

#Density per quadrat totals
ggplot(data=df_quadrat_LAUR, aes(x= Survival_status, y = Count, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Gold Star Beach Count ", x ="Survival status", y= "Density")+
  facet_wrap(~ Season, scales = "free")
```






```{r}
sessionInfo()
```