---
title: "BedCharacteristics_Oct2023Survey"
author: "Mariah Kachmar"
date: "12/13/2023"
output: html_document
updated: 3/19/2024
description: This R code is used to important and summarize bed characteristics (height, area, rugosity, density, and coverage) data from the LISS Oyster Health Project's October 2023 oyster population surveys at Ash Creek and Fence Creek intertidal sites in Connecticut and Goldstar Beach and Laurel Hollow subtidal sites in New York. 
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
```


```{r, echo=FALSE}
library("dplyr")                                    
library("plyr")                                     
library("readr")             
library("Rmisc")
library("ggplot2")
library("lubridate")
```




```{r}
#Pulling all bed characteristic files
data_all <- list.files(path = "Field_Data_Biological/raw_data/Characteristics",                           # Identify all CSV files
  pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% dplyr::bind_rows()
data_all

as.data.frame(data_all)

#cleaning up date date
data_all <- data_all %>%
  dplyr::rename(Date_collected = Date)
data_all$Date_collected <- factor(data_all$Date_collected, levels = c("10/3/2023","10-5-23", "10/16/2023", "10/17/2023" ),
                                     labels = c("2023-10-03","2023-10-05","2023-10-16", "2023-10-17" ))

#adding season columns
data_all <- data_all %>%
  mutate(Date_collected = as.Date(Date_collected), month = month(Date_collected))
data_all <- data_all %>%
  mutate(Season = case_when(between(month, 5,6) ~"Spring",
                            between(month, 10,11) ~ "Fall"))
data_all <- select(data_all, -c("month"))
```


##### Bed height #####

```{r}
#Bed Height - creating master file

#removing unnecessary columns
bed_all <- select(data_all, -c("Field ID", "Quadrat_size", "Percent_coverage", "Live_count",
                                  "Box_count", "Gaper_count", "Rugosity", "Quadrat"))

bed_all <- na.omit(bed_all)
head(bed_all)

#renaming column
  bed_all <- bed_all %>% 
    dplyr::rename(Bed_height_cm =Bed_height)
  
#reordering columns
bed_all <- bed_all %>% select("Date_collected", "Site", "State", "Bed_height_cm", "Season")
```


#June 2023 (spring) survey for bed height. Changing June 2023 data to match formate of the data later collected. All data pulled form June 2023 is from the original file.
```{r}

bedheight_june2023 <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_BedHeight.csv") 

#Cleaning up June 2023 data
#renaming columns
bedheight_june2023 <- bedheight_june2023 %>%
  dplyr::rename(Date_collected = TripDate) %>%
  dplyr::rename(Bed_height_cm = BedHeight_cm)
  
bedheight_june2023$Date_collected <- factor(bedheight_june2023$Date_collected, levels = c("6/12/2023","6/14/2023"),
                                     labels = c("2023-06-12","2023-06-14"))
#adding columns
bedheight_june2023$Season <- rep("Spring", nrow(bedheight_june2023))
bedheight_june2023$State <- rep("CT", nrow(bedheight_june2023))

#removing unnecessary columns
bedheight_june2023 <- select(bedheight_june2023, -c("BedHeight_Notes", "TopMark", "BottomMark", "Measure_direction", "Bed_Section"))

bedheight_june2023<- bedheight_june2023 %>%
  mutate(Site = recode(Site_Name, "Ash Creek" = "ASHC", "Fence Creek" = "FENC")) %>% 
  select(-c("Site_Name"))

head(bedheight_june2023)

#reordering columns
bedheight_june2023 <- bedheight_june2023 %>% select("Date_collected", "Site", "State", "Bed_height_cm", "Season")
```

```{r}
#Merging all bed height data into master file
Bedheight_master <- rbind(bed_all, bedheight_june2023)

write.csv(Bedheight_master, "Master_files/bed_height_all_data.csv", row.names = FALSE)
```

```{r}
#Summary of bed height at each site

bedheight_summary<- data_all %>%
  filter(!is.na(Live_count) & !is.na(Box_count) & !is.na(Gaper_count) & !is.na(Bed_height))
bedheight_summary 

bedheight_summary <- summarySE(data = Bedheight_master, measurevar = "Bed_height_cm", groupvars = c( "Date_collected", "Site"))

bedheight_summary

write.csv(bedheight_summary, "Field_Data_Biological/output/bedheight_summary.csv", row.names=FALSE)
```



#### Rugosity data ####
```{r}
#Rugosity - creating master file

#removing unnecessary columns
rugosity_all <- select(data_all, -c("Field ID", "Quadrat_size", "Percent_coverage", "Live_count",
                                  "Box_count", "Gaper_count","Bed_height", "Quadrat"))

rugosity_all <- na.omit(rugosity_all)
head(rugosity_all)
```
#June 2023 (spring) survey - rugosity data. Changing June 2023 data to match formate of the data later collected. All data pulled form June 2023 is from the original file.
```{r}
rugosity_june2023 <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_Rugosity.csv") 

#Cleaning up June 2023 data
#renaming columns
rugosity_june2023 <- rugosity_june2023 %>%
  dplyr::rename(Date_collected = TripDate)

#adding columns
rugosity_june2023$Season <- rep("Spring", nrow(rugosity_june2023))
rugosity_june2023$State <- rep("CT", nrow(rugosity_june2023))

#removing unnecessary columns
rugosity_june2023 <- select(rugosity_june2023, -c("RUGOS_NUM","ChainType", "Bed_Section", "Zone", "LengthContoured_cm", "LengthStraightline_cm","Notes"))

rugosity_june2023<- rugosity_june2023 %>%
  mutate(Site = recode(Site_Name, "Ash Creek" = "ASHC", "Fence Creek" = "FENC")) %>% 
  select(-c("Site_Name"))

head(rugosity_june2023)

#reordering columns
rugosity_june2023 <- rugosity_june2023 %>% select("Date_collected", "Site", "State", "Rugosity", "Season")
```

```{r}
#Merging all rugosity data into master file
Rugosity_master <- rbind(rugosity_all, rugosity_june2023)

write.csv(Rugosity_master, "Master_files/rugosity_all_data.csv", row.names = FALSE)
```

```{r}
#Summary of rugosity at each site

rugosity_summary<- data_all %>%
  filter(!is.na(Live_count) & !is.na(Box_count) & !is.na(Gaper_count) & !is.na(Bed_height))
bedheight_summary 

rugosity_summary <- summarySE(data = Rugosity_master, measurevar = "Rugosity", groupvars = c( "Date_collected", "Site"))

rugosity_summary #Laural Hollow only has one rugosity measurement, so NAs will appear for the summary points

write.csv(rugosity_summary, "Field_Data_Biological/output/rugosity_summary.csv", row.names=FALSE)
```


#### Percent Coverage ####

#changing percent coverage categories
```{r}
#Percent Coverage - creating master file

percent_coverage <- read.csv("Field_Data_Biological\\raw_data\\qry_2023-06_Survey_QuadratDensity.csv") 


#Cleaning up June 2023 data
#renaming columns
percov_june2023 <- percov_june2023 %>%
  dplyr::rename(Date_collected = TripDate) %>%
  dplyr::rename(Bed_height =BedHeight_cm)
  
percov_june2023$Date_collected <- factor(percov_june2023$Date_collected, levels = c("6/12/2023","6/14/2023"),
                                     labels = c("2023-06-12","2023-06-14"))
#adding columns
percov_june2023$Season <- rep("Spring", nrow(percov_june2023))
percov_june2023$State <- rep("CT", nrow(percov_june2023))

#removing unnecessary columns
percov_june2023 <- select(percov_june2023, -c("BedHeight_Notes", "TopMark", "BottomMark", "Measure_direction", "Bed_Section"))

percov_june2023<- percov_june2023 %>%
  mutate(Site = recode(Site_Name, "Ash Creek" = "ASHC", "Fence Creek" = "FENC")) %>% 
  select(-c("Site_Name"))

head(percov_june2023)

#reordering columns
percov_june2023 <- percov_june2023 %>% select("Date_collected", "Site", "State", "Bed_height", "Season")
```

```{r}
#October 2023 (fall) data. This data is in a different format compared to the other dates, where percent coverage is not binned.
#removing unnecessary columns
percov_all <- select(percov_all, -c("Field ID", "Quadrat_size", "Rugosity", "Bed_height", "Quadrat"))

percov_all <- percov_all[!is.na(percov_all$Percent_coverage),]
head(percov_all)

#removing percent coverage < 25% (anything below 25% is considered off the oyster bed)
percov_all<- subset(percov_all, Percent_coverage>21)

#reordering columns
percov_all <- percov_all %>% select("Date_collected", "Site", "State", "Percent_coverage", "Live_count",
                                  "Box_count", "Gaper_count", "Season")

#binning percent coverage
```


```{r}
#Merging all percent coverage data into master file
#Density measured in centimeters
Percentcoverage_master <- rbind(percov_all, percov_june2023)

write.csv(Percentcoverage_master, "Master_files/percent_coverage_all_data.csv", row.names = FALSE)
```



#oyster density metrics. QAQC_PopulationHeight script implements this code.
```{r}

#data_all <- data_all %>%
#  filter(!is.na(Live_count) & !is.na(Box_count) & !is.na(Gaper_count))
#data_all  

density_live_sum <- summarySE(data = data_all, measurevar = "Live_count", groupvars = c(  "Site"))
density_live_sum
density_live_sum <- density_live_sum %>%
  mutate(Count = Live_count) %>%
  select(-Live_count)


density_box_sum <- summarySE(data = data_all, measurevar = "Box_count", groupvars = c( "Site"))
density_box_sum <- density_box_sum %>%
  mutate(Count = Box_count) %>%
  select(-Box_count)
density_box_sum

density_gaper_sum <- summarySE(data = data_all, measurevar = "Gaper_count", groupvars = c( "Site"))
density_gaper_sum <- density_gaper_sum %>%
  mutate(Count = Gaper_count) %>%
  select(-Gaper_count)



density_summary<- rbind(density_gaper_sum, density_box_sum, density_live_sum)
density_summary

#sum total number of oysters counted per quadrat
 


```


```{r}
sessionInfo()
```