
---
title: "QAQC_PopulationSurveyMetrics"
author: "Meghana Parikh"
date: "2023-06-29"
output: html_document

description: This R code is used to important and summarize shell height data from the LISS Oyster Health Project's 2023 oyster population surveys at Ash Creek and Fence Creek intertidal sites in Connecticut and Goldstar beach and Laurel Hollow subtidal sites on Long Island, NY. June 2023 data was originally input into the Access database (LISS_Database_FieldCollectionData_2023-07-18.accb) and files needed to be converted and standardize to the new collection method. All original or raw data can be accessed in the GitHub repository. 
---

Last updated 12/26/23 by M.Kachmar


```{r, setup, include=FALSE}

knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological')


install.packages("tidyverse")
install.packages("gtools")
install.packages("Rmisc")
library(gtools)
library(readxl)
library(plyr)
library(dplyr)
library(lubridate)
library(Rmisc)
library(ggplot2)

```

```{r}

#### need to work on this chunk to read in all files at once - not ready to use
#data_all <- list.files(path = "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological",                                                               
 # pattern = "*.xlsx", full.names = TRUE) %>%         # Identify all xlsx files
 # lapply(read_excel)                           # Store all files in list
#
 # data_all                                            # Print data to RStudio console

#as.data.frame(data_all)                            # Convert tibble to data.frame





```

# Spring Survey Data - June 2023
```{r}

#read in all population survey sheets 


#June 2023
shellsize <- read_excel("C:\\Users\\mariah.kachmar\\Documents\\Github\\EAD-ASEB_EPA_LISS_Disease_Surveillance\\Field_Data_Biological\\qry_2023-06_Survey_ShellSize.xlsx",
                     sheet = 1, col_names = TRUE) 

quadratdensity <- read_excel("C:\\Users\\mariah.kachmar\\Documents\\Github\\EAD-ASEB_EPA_LISS_Disease_Surveillance\\Field_Data_Biological\\qry_2023-06_Survey_QuadratDensity.xlsx",
                     sheet = 1, col_names = TRUE) 

rugosity <- read_excel("C:\\Users\\mariah.kachmar\\Documents\\Github\\EAD-ASEB_EPA_LISS_Disease_Surveillance\\Field_Data_Biological\\qry_2023-06_Survey_Rugosity.xlsx",
                     sheet = 1, col_names = TRUE) 

BedHeight <- read_excel("C:\\Users\\mariah.kachmar\\Documents\\Github\\EAD-ASEB_EPA_LISS_Disease_Surveillance\\Field_Data_Biological\\qry_2023-06_Survey_BedHeight.xlsx",
                     sheet = 1, col_names = TRUE) 
```

#Cleaning up June 2023 survey data to be meragable with other data
```{r}


#renaming columns
shellsize <- shellsize %>% rename(Date_collected = TripDate) %>% rename(Quadrat = QUADRAT_NUM) %>% rename(Height= Height_mm) %>% rename(Survival_status= SpecimenType)

#adding columns
shellsize$Season<- rep("spring", nrow(shellsize))
shellsize$State<- rep("CT", nrow(shellsize))

#removing unneeded columns
shellsize<- select( shellsize, -c("QuadSpec_NUM", "Year", "Month", "Day", "Length_mm", "Width_mm", "Specimen_Notes")) 

#Changing site name and removing unneeded column
shellsize<- shellsize %>%
  mutate(Site = recode(Site_Name, "Ash Creek" = "ASHC", "Fence Creek" = "FENC")) %>% 
  select(-c("Site_Name"))

head(shellsize)

shellsize

#reorder columns
shellsize <- shellsize %>% select("Date_collected", "Site", "State", "Quadrat", "Height", "Survival_status", "Season")



```


# This chunk is exploritory for fall surveys. Thinking about best way to pull, clean, and merge data and best ways to standardize June and October survey data

#Pulling all length data into single sheet
```{r}

## OCTOBER FALL SURVEY 



length_all <- list.files(path = "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/Length",                           # Identify all CSV files
  pattern = "*.xlsx", full.names = TRUE) %>% 
  lapply(read_excel) %>%    # Store all files in list
  bind_rows 

 length_all

 #Removing 'Count' column
 length_all$Count<- NULL


```

#Cleaning up length data
#Need to fix "length" and change to "height" - using terms incorrectly
```{r}

# Subset by category length (live, box, gaper)

#Live

length_live <- select(length_all, 'Field ID', 'Date_collected', 'Site', 'State', 'Quadrat','Length_live')
length_live <- na.omit(length_live)
length_live$Survival_status<- rep("Live", nrow(length_live))
length_live <- length_live %>% rename(Height = Length_live)
length_live

#Box

length_box <- select(length_all, 'Field ID', 'Date_collected', 'Site', 'State', 'Quadrat','Length_box')
length_box <- na.omit(length_box)
length_box$Survival_status<- rep("Box", nrow(length_box))
length_box <- length_box %>% rename(Height = Length_box)

#Gaper

length_gaper <- select(length_all, 'Field ID', 'Date_collected', 'Site', 'State', 'Quadrat','Length_gaper')
length_gaper <- na.omit(length_gaper)
length_gaper$Survival_status<- rep("Gaping", nrow(length_gaper))
length_gaper <- length_gaper %>% rename(Height = Length_gaper)

Height_all<- rbind(length_live,length_box,length_gaper)
Height_all$Season<- rep("fall", nrow(Height_all))
Height_all

Height_all$`Field ID`<- NULL
```

#Merging spring and fall 2023 Height data
```{r}

Height_master<- rbind(Height_all, shellsize)
Height_master

Height_master<-na.omit(Height_master)

# Output to repository
write.csv(Height_master, "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/Output/Height_master.csv", row.names=FALSE)

```
#Oyster density metrics
```{r}


#Sum total number of oyster counter per quadrat
quadratdensity_all<- Height_master %>%
  group_by(Quadrat, Season, Survival_status, Site, Date_collected, State) %>%
  summarize(Count = n())
quadratdensity_all

#summary of each oyster type by site. output = Site, N, Mean, stnd dev, stnd error, and confidence interval
all_density_SE <-summarySE(data = quadratdensity_all, measurevar = "Count", groupvars=c("Site", "Survival_status", "Season"))
all_density_SE

#calculate percent standard error as 100*se/mean
all_density_SE$PSE_all <- 100*(all_density_SE$se/all_density_SE$Count)

#calculate completeness as 100*N/12, where 12 is the desired number of quadrats per site 
  densitysummary <- all_density_SE %>%
    mutate(PercentComplete_Quad = ((N/12)*100))
densitysummary


write.csv(densitysummary, "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/Output/populationdensity_summary.csv", row.names=FALSE)

```
#oyster size distribution
```{r}

      
shellsize_all <- 
  Height_master %>% group_by(Site, Season) %>%
  summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  mutate(Survival_status = "All")
shellsize_all

shellsize_live <- 
  Height_master %>% group_by(Site, Season) %>% filter(Survival_status=="Live") %>%
   summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  mutate(Survival_status = "Live")
shellsize_live

shellsize_box <- 
  Height_master %>%  group_by(Site, Season) %>%filter(Survival_status=="Box") %>%
   summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  mutate(Survival_status = "Box")

shellsize_gaper <- 
  shellsize %>%  group_by(Site, Season) %>% filter(Survival_status=="Gaping") %>%
   summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  mutate(Survival_status = "Gaper")

#rbind together 

shellsize_summary <- rbind(shellsize_all, shellsize_live, shellsize_box, shellsize_gaper)
shellsize_summary

#size distribution summary
#note that calculating PSE and accuracy do not make sense for size distributions. Will need to figure out new metrics for the QAPP
write.csv(shellsize_summary, "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/Output/shellsize_summary.csv", row.names=FALSE)
```

#graphing shell height all sites
```{r}


ggplot(Height_master, aes(x=Season, y=Height, fill=Site)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
  facet_wrap(~Site)

```

#ASHC
```{r}
#graphing shell height ASHC

height_ASHC<- Height_master %>% filter(Site == "ASHC")

height_ASHC<- height_ASHC %>%
  mutate(Month = recode(Season, "fall" = "October", "spring" = "June")) 

live_height_ASHC<- height_ASHC %>%
 group_by(Site, Season)%>%
  filter(Survival_status == "Live")%>%
  summarize(Mean_Height = mean(Height))
live_height_ASHC

#How many animals fall within the distributions
# Define size bins (modify these according to your size ranges)
size_breaks <- seq(0, 190, by = 10)  # Define size breaks (0, 10, 20, 30, 40, 50)
size_labels <- paste(size_breaks[-length(size_breaks)], size_breaks[-1], sep = "-")  # Labels for size ranges

# Create size bins and count animals in each bin
height_ASHC$Size_Group <- cut(height_ASHC$Height, breaks = size_breaks, labels = size_labels)
animals_count <- table(height_ASHC$Size_Group)
animals_count

# Display the count of animals in each size range
print(animals_count)



#Subset by survival status
height_ASHC_Live <- height_ASHC[height_ASHC$Survival_status == "Live",]
print(height_ASHC_Live)
height_ASHC_Live

height_ASHC_Dead <- height_ASHC[height_ASHC$Survival_status == "Box"|height_ASHC$Survival_status == "Gaper",]
print(height_ASHC_Dead)

#plots
ggplot(height_ASHC, aes(x=Season, y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

#Distribution Live
ggplot(data=height_ASHC_Live, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Height Live Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,190), breaks = seq(0,190, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))+
 facet_wrap(~ Month, scales = "free", ncol = 1)

#Distribution Dead
ggplot(data=height_ASHC_Dead, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Height Dead Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,190), breaks = seq(0,190, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))+
   facet_wrap(~ Month, scales = "free", ncol = 1)

```

#ASHC Density and mortality
```{r}


df_quadrat_ASHC <- quadratdensity_all%>%
  filter(Site == "ASHC")
df_quadrat_ASHC

#Quadrat size is 25 x25cm (.0625 m^2). To calculate density (oysters per m^2) multiply number of oysters counted X 16

df_density_ASHC <- df_quadrat_ASHC %>%
  dplyr::group_by(Site, Season, Quadrat, Survival_status) %>% 
  dplyr::summarize(Density = sum(Count)*16)
df_density_ASHC

#Mean of Oysters per m^2 across all quadrats
mean_total_oysters_ASHC <- df_density_ASHC %>%
  group_by(Site, Season, Survival_status) %>%
  summarize(Total_Density = mean(Density))
mean_total_oysters_ASHC
 

#Density per quadrat totals
ggplot(data=df_quadrat_ASHC, aes(x= Survival_status, y = Count, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Count ", x ="Survival status", y= "Density")+
  facet_wrap(~ Season, scales = "free")

#Density of oysters per meter squared
ggplot(data=mean_total_oysters_ASHC, aes(x= Survival_status, y = Total_Density, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Density ", x ="Survival status", y= "Density (# oyster / meter squared)")+
  facet_wrap(~ Season, scales = "free")

```
#FENC

```{r}
#graphing shell height FENC

height_FENC<- Height_master %>% filter(Site == "FENC")

ggplot(height_FENC, aes(x=Season, y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

ggplot(data=height_FENC, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Fence Creek Creek Height ", x ="Height (mm)")+
  facet_wrap(~ Season, scales = "free", ncol = 1)

```

#FENC density and mortality calculations
```{r}

df_quadrat_FENC <- quadratdensity_all%>%
  filter(Site == "FENC")
df_quadrat_FENC

#Quadrat size is 25 x25cm. To calculate density (oysters per m^2) multiply number of oysters counted X 4

df_density_FENC <- df_quadrat_FENC %>%
  dplyr::group_by(Site, Season, Quadrat, Survival_status) %>% 
  dplyr::summarize(Density = sum(Count)*4)
df_density_FENC

#mean of Oysters per m^2 across all quadrats
mean_total_oysters_FENC <- df_density_FENC %>%
  group_by(Site, Season, Survival_status) %>%
  summarize(Total_Density = mean(Density))
mean_total_oysters_FENC

#Density per quadrat totals
ggplot(data=df_quadrat_FENC, aes(x= Survival_status, y = Count, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Fence Creek Count ", x ="Survival status", y= "Density")+
  facet_wrap(~ Season, scales = "free")

#Density of oysters per meter squared
ggplot(data=mean_total_oysters_FENC, aes(x= Survival_status, y = Total_Density, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Fence Creek Density ", x ="Survival status", y= "Density (# oyster / meter squared)")+
  facet_wrap(~ Season, scales = "free")

#Gaper mortality


```

#GOLD
```{r}
#graphing shell height GOLD

height_GOLD<- Height_master %>% filter(Site == "GOLD")
height_GOLD

height_GOLD<- height_GOLD %>%
  mutate(Month = recode(Season, "fall" = "October", "spring" = "June")) 

live_height_GOLD<- height_GOLD %>%
 group_by(Site, Season)%>%
  filter(Survival_status == "Live")%>%
  summarize(Mean_Height = mean(Height))
live_height_GOLD

#How many animals fall within the distributions
# Define size bins (modify these according to your size ranges)
size_breaks <- seq(0, 190, by = 10)  # Define size breaks (0, 10, 20, 30, 40, 50)
size_labels <- paste(size_breaks[-length(size_breaks)], size_breaks[-1], sep = "-")  # Labels for size ranges

# Create size bins and count animals in each bin
height_GOLD$Size_Group <- cut(height_GOLD$Height, breaks = size_breaks, labels = size_labels)
animals_count <- table(height_GOLD$Size_Group)
animals_count

# Display the count of animals in each size range
print(animals_count)

#plots
class(height_GOLD$Month)
height_GOLD

height_GOLD_Live <- height_GOLD[height_GOLD$Survival_status == "Live",]
print(height_GOLD_Live)

height_GOLD_Dead <- height_GOLD[height_GOLD$Survival_status == "Box"|height_GOLD$Survival_status == "Gaper",]
print(height_GOLD_Dead)

ggplot(height_GOLD, aes(x = Date_collected, y = Height, color = Date_collected)) +
  geom_boxplot() +  
  theme_bw() +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(title = "Shell Height", x = "Month", y = "Height (mm)") +
  theme(axis.title.y = element_text(size = rel(1.3), angle = 90), axis.title.x = element_text(size = rel(1.3), angle = 0)) +
  theme(axis.text = element_text(size = 12))

#Distribution Live
ggplot(data=height_GOLD_Live, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Gold Star Beach Height Live Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,170), breaks = seq(0,170, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))
 # facet_wrap(~ Month, scales = "free", ncol = 1)

#Distribution Dead
ggplot(data=height_GOLD_Dead, aes(x= Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Gold Star Beach Height Dead Oysters ", x ="Height (mm)")+ scale_x_continuous(limits= c(0,170), breaks = seq(0,170, by =10) )+
  scale_y_continuous(limits = c(0,20), breaks = seq(0,20, by = 5))


```
#GOLD density & mortality
```{r}
df_quadrat_GOLD <- quadratdensity_all%>%
  filter(Site == "GOLD")
df_quadrat_GOLD

#Quadrat size is 25 x25cm (.0625 m^2). To calculate density (oysters per m^2) multiply number of oysters counted X 16

df_density_GOLD <- df_quadrat_GOLD %>%
  dplyr::group_by(Site, Season, Quadrat, Survival_status) %>% 
  dplyr::summarize(Density = sum(Count)*16)
df_density_GOLD

#Mean of Oysters per m^2 across all quadrats
mean_total_oysters_GOLD <- df_density_GOLD %>%
  group_by(Site, Season, Survival_status) %>%
  summarize(Total_Density = mean(Density))
mean_total_oysters_GOLD
 

#Density per quadrat totals
ggplot(data=df_quadrat_GOLD, aes(x= Survival_status, y = Count, fill = Survival_status)) +
  geom_bar( stat="identity")+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Gold Star Beach Count ", x ="Survival status", y= "Density")+
  facet_wrap(~ Season, scales = "free")
```
#LAUR
```{r}
#graphing shell height LAUR

height_LAUR<- Height_master %>% filter(Site == "LAUR")

ggplot(height_LAUR, aes(x=Season, y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```


#Old code originally for June 2023 survey data format
```{r}
#oyster density metrics 


#sum total number of oysters counted per quadrat
quadratdensity$AllCount_Total <- rowSums(quadratdensity[, c("LiveCount_Total", "BoxCount_Total", "GaperCount_Total")])

#summary of each oyster type by site. output = Site, N, Mean, stnd dev, stnd error, and confidence interval
all_density_SE <-summarySE(data = quadratdensity, measurevar = "AllCount_Total", groupvars=c("Site_Name"))
all_density_SE
live_density_SE <- summarySE(data = quadratdensity, measurevar = "LiveCount_Total", groupvars=c("Site_Name"))
box_density_SE <-summarySE(data = quadratdensity, measurevar = "BoxCount_Total", groupvars=c("Site_Name"))
gaper_density_SE <-summarySE(data = quadratdensity, measurevar = "GaperCount_Total", groupvars=c("Site_Name"))

#calculate percent standard error as 100*se/mean
all_density_SE$PSE_all <- 100*(all_density_SE$se/all_density_SE$AllCount_Total)
live_density_SE$PSE_live <- 100*(live_density_SE$se/live_density_SE$LiveCount_Total)
box_density_SE$PSE_box <- 100*(box_density_SE$se/box_density_SE$BoxCount_Total)
gaper_density_SE$PSE_gaper <- 100*(gaper_density_SE$se/gaper_density_SE$GaperCount_Total)


#join into 1 table 
densitysummary <- subset(all_density_SE, select = -c(sd,se,ci)) %>%
    left_join(subset(live_density_SE, select = -c(N,sd,se,ci)), by = "Site_Name") %>%
    left_join(subset(box_density_SE, select = -c(N,sd,se,ci)), by = "Site_Name") %>%
    left_join(subset(gaper_density_SE, select = -c(N,sd,se,ci)), by = "Site_Name") %>%

#renaming for clarity. need to use dplyr:: because another package is overriding the function
#densitysummary <- densitysummary %>%
    dplyr::rename(
      AllCount_Mean = AllCount_Total,
      LiveCount_Mean = LiveCount_Total,
      BoxCount_Mean = BoxCount_Total, 
      GaperCount_Mean = GaperCount_Total, 
      NumQuad = N) %>%
  
#calculate completeness as 100*N/12, where 12 is the desired number of quadrats per site 
  mutate(PercentComplete_Quad = ((NumQuad/12)*100) )


write.csv(densitysummary, "C:/Users/meghana.parikh/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological\\populationdensity_summary.csv", row.names=FALSE)
#note that PSE is >20 percent at Ash Creek, and at Fence creek in box and gaper categories. This is due to the different levels of sampling. Need to redo with categories 


```



```{r}

#oyster size distribution

#finding the empty values - these are oyster samples collected for lab use I think?
emptyvalues <- shellsize %>% filter(is.na(Height_mm))
      
shellsize_all <- 
  shellsize %>% group_by(Site_Name) %>%
  summarise(
    median_height=median(Height_mm, na.rm = TRUE), 
    min_height=min(Height_mm, na.rm = TRUE), 
    max_height=max(Height_mm, na.rm = TRUE), 
    Q1=quantile(Height_mm,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height_mm,probs = 0.75, na.rm = TRUE))%>%
  mutate(SpecimenType = "All")

shellsize_live <- 
  shellsize %>% filter(SpecimenType=="Live") %>%
   summarise(
    median_height=median(Height_mm, na.rm = TRUE), 
    min_height=min(Height_mm, na.rm = TRUE), 
    max_height=max(Height_mm, na.rm = TRUE), 
    Q1=quantile(Height_mm,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height_mm,probs = 0.75, na.rm = TRUE))%>%
  mutate(SpecimenType = "Live")

shellsize_box <- 
  shellsize %>% filter(SpecimenType=="Box") %>%
   summarise(
    median_height=median(Height_mm, na.rm = TRUE), 
    min_height=min(Height_mm, na.rm = TRUE), 
    max_height=max(Height_mm, na.rm = TRUE), 
    Q1=quantile(Height_mm,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height_mm,probs = 0.75, na.rm = TRUE))%>%
  mutate(SpecimenType = "Box")

shellsize_gaper <- 
  shellsize %>% filter(SpecimenType=="Gaping") %>%
   summarise(
    median_height=median(Height_mm, na.rm = TRUE), 
    min_height=min(Height_mm, na.rm = TRUE), 
    max_height=max(Height_mm, na.rm = TRUE), 
    Q1=quantile(Height_mm,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height_mm,probs = 0.75, na.rm = TRUE))%>%
  mutate(SpecimenType = "Gaper")

#rbind together 

shellsize_summary <- rbind(shellsize_all, shellsize_live, shellsize_box, shellsize_gaper)

#size distribution summary
#note that calculating PSE and accuracy do not make sense for size distributions. Will need to figure out new metrics for the QAPP
write.csv(shellsize_summary, "C:/Users/meghana.parikh/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological\\shellsize_summary.csv", row.names=FALSE)

  
```
```{r}
sessionInfo()
```