
---
title: "QAQC_PopulationSurveyMetrics"
author: "Meghana Parikh"
date: "2023-06-29"
output: html_document

description: This R code is used to important and summarize shell height data from the LISS Oyster Health Project's 2023 oyster population surveys at Ash Creek and Fence Creek intertidal sites in Connecticut and Goldstar beach and Laurel Hollow subtidal sites on Long Island, NY. June 2023 data was originally input into the Access database (LISS_Database_FieldCollectionData_2023-07-18.accb) and files needed to be converted and standardize to the new collection method. All original or raw data can be accessed in the GitHub repository. 
---

Last updated 11/22/23 by M.Kachmar
Calculated density metrics - need to go through and check quadrat numbers
Output of both population density and height master file in github
started creating graphs - need to fix data, there is a height measurement reading very high for ASHC, GOLD which is effecting the calculations. 

```{r, setup, include=FALSE}

knitr::opts_knit$set(root.dir = 'C:/Users/meghana.parikh/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological')


install.packages("tidyverse")
install.packages("gtools")
install.packages("Rmisc")
library(gtools)
library(readxl)
library(plyr)
library(dplyr)
library(lubridate)
library(Rmisc)
library(ggplot2)

```

```{r}

#### need to work on this chunk to read in all files at once - not ready to use
data_all <- list.files(path = "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological",                                                               
  pattern = "*.xlsx", full.names = TRUE) %>%         # Identify all xlsx files
  lapply(read_excel) %>%                            # Store all files in list
data_all                                            # Print data to RStudio console

as.data.frame(data_all)                            # Convert tibble to data.frame





```

# Spring Survey Data - June 2023
```{r}

#read in all population survey sheets 


#June 2023
shellsize <- read_excel("C:\\Users\\mariah.kachmar\\Documents\\Github\\EAD-ASEB_EPA_LISS_Disease_Surveillance\\Field_Data_Biological\\qry_2023-06_Survey_ShellSize.xlsx",
                     sheet = 1, col_names = TRUE) 

quadratdensity <- read_excel("C:\\Users\\mariah.kachmar\\Documents\\Github\\EAD-ASEB_EPA_LISS_Disease_Surveillance\\Field_Data_Biological\\qry_2023-06_Survey_QuadratDensity.xlsx",
                     sheet = 1, col_names = TRUE) 

rugosity <- read_excel("C:\\Users\\mariah.kachmar\\Documents\\Github\\EAD-ASEB_EPA_LISS_Disease_Surveillance\\Field_Data_Biological\\qry_2023-06_Survey_Rugosity.xlsx",
                     sheet = 1, col_names = TRUE) 

BedHeight <- read_excel("C:\\Users\\mariah.kachmar\\Documents\\Github\\EAD-ASEB_EPA_LISS_Disease_Surveillance\\Field_Data_Biological\\qry_2023-06_Survey_BedHeight.xlsx",
                     sheet = 1, col_names = TRUE) 
```

#Cleaning up June 2023 survey data to be meragable with other data
```{r}


#renaming columns
shellsize <- shellsize %>% rename(Date_collected = TripDate) %>% rename(Quadrat = QUADRAT_NUM) %>% rename(Height= Height_mm) %>% rename(Survival_status= SpecimenType)

#adding columns
shellsize$Season<- rep("spring", nrow(shellsize))
shellsize$State<- rep("CT", nrow(shellsize))

#removing unneeded columns
shellsize<- select( shellsize, -c("QuadSpec_NUM", "Year", "Month", "Day", "Length_mm", "Width_mm", "Specimen_Notes")) 

#Changing site name and removing unneeded column
shellsize<- shellsize %>%
  mutate(Site = recode(Site_Name, "Ash Creek" = "ASHC", "Fence Creek" = "FENC")) %>% 
  select(-c("Site_Name"))

head(shellsize)

shellsize

#reorder columns
shellsize <- shellsize %>% select("Date_collected", "Site", "State", "Quadrat", "Height", "Survival_status", "Season")



```


# This chunk is exploritory for fall surveys. Thinking about best way to pull, clean, and merge data and best ways to standardize June and October survey data

#Pulling all length data into single sheet
```{r}

## OCTOBER FALL SURVEY 



length_all <- list.files(path = "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/Length",                           # Identify all CSV files
  pattern = "*.xlsx", full.names = TRUE) %>% 
  lapply(read_excel) %>%    # Store all files in list
  bind_rows 

 length_all

 #Removing 'Count' column
 length_all$Count<- NULL


```

#Cleaning up length data
#Need to fix "length" and change to "height" - using terms incorrectly
```{r}

# Subset by category length (live, box, gaper)

#Live

length_live <- select(length_all, 'Field ID', 'Date_collected', 'Site', 'State', 'Quadrat','Length_live')
length_live <- na.omit(length_live)
length_live$Survival_status<- rep("Live", nrow(length_live))
length_live <- length_live %>% rename(Height = Length_live)
length_live

#Box

length_box <- select(length_all, 'Field ID', 'Date_collected', 'Site', 'State', 'Quadrat','Length_box')
length_box <- na.omit(length_box)
length_box$Survival_status<- rep("Box", nrow(length_box))
length_box <- length_box %>% rename(Height = Length_box)

#Gaper

length_gaper <- select(length_all, 'Field ID', 'Date_collected', 'Site', 'State', 'Quadrat','Length_gaper')
length_gaper <- na.omit(length_gaper)
length_gaper$Survival_status<- rep("Gaping", nrow(length_gaper))
length_gaper <- length_gaper %>% rename(Height = Length_gaper)

Height_all<- rbind(length_live,length_box,length_gaper)
Height_all$Season<- rep("fall", nrow(Height_all))
Height_all

Height_all$`Field ID`<- NULL
```

#Merging spring and fall 2023 Height data
```{r}

Height_master<- rbind(Height_all, shellsize)
Height_master


# Output to repository
write.csv(Height_master, "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/Output/Height_master.csv", row.names=FALSE)

```
```{r}
#Oyster density metrics

#Sum total number of oyster counter per quadrat
quadratdensity_all<- Height_master %>%
  group_by(Quadrat, Season, Survival_status, Site, Date_collected, State) %>%
  summarize(Count = n())
quadratdensity_all

#summary of each oyster type by site. output = Site, N, Mean, stnd dev, stnd error, and confidence interval
all_density_SE <-summarySE(data = quadratdensity_all, measurevar = "Count", groupvars=c("Site", "Survival_status", "Season"))
all_density_SE

#calculate percent standard error as 100*se/mean
all_density_SE$PSE_all <- 100*(all_density_SE$se/all_density_SE$Count)

#calculate completeness as 100*N/12, where 12 is the desired number of quadrats per site 
  densitysummary <- all_density_SE %>%
    mutate(PercentComplete_Quad = ((N/12)*100))


write.csv(densitysummary, "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/Output/populationdensity_summary.csv", row.names=FALSE)

```

```{r}
#oyster size distribution
      
shellsize_all <- 
  Height_master %>% group_by(Site, Season) %>%
  summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  mutate(Survial_status = "All")
shellsize_all

shellsize_live <- 
  Height_master %>% group_by(Season) %>% filter(Survival_status=="Live") %>%
   summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  mutate(Survival_status = "Live")
shellsize_live

shellsize_box <- 
  Height_master %>%  group_by(Season) %>%filter(Survival_status=="Box") %>%
   summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  mutate(Survival_status = "Box")

shellsize_gaper <- 
  shellsize %>%  group_by(Season) %>% filter(Survival_status=="Gaping") %>%
   summarise(
    median_height=median(Height, na.rm = TRUE), 
    min_height=min(Height, na.rm = TRUE), 
    max_height=max(Height, na.rm = TRUE), 
    Q1=quantile(Height,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height,probs = 0.75, na.rm = TRUE))%>%
  mutate(Survival_status = "Gaper")

#rbind together 

shellsize_summary <- rbind(shellsize_all, shellsize_live, shellsize_box, shellsize_gaper)
shellsize_summary

#size distribution summary
#note that calculating PSE and accuracy do not make sense for size distributions. Will need to figure out new metrics for the QAPP
write.csv(shellsize_summary, "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological/Output/shellsize_summary.csv", row.names=FALSE)
```


```{r}
#graphing shell height all sites

ggplot(Height_master, aes(x=Season, y=Height, fill=Site)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
  facet_wrap(~Site)

```

```{r}

## Stacked bar graph showing height proportions for all sites

df_height_proportions<- Height_master %>%
  mutate(height_bin = cut(Height, breaks = c(0,5,10,20,30,40,50,60,70,80,90,110,120,140,150,160,170,180))) %>%
  group_by(Site, Season, height_bin) %>%
  summarise(Count= n()) %>%
  ungroup() %>%
  mutate(Proportion = Count/sum(Count))

df_height_proportions<- na.omit(df_height_proportions)

df_height_proportions

ggplot(data=df_height_proportions, aes(x=Season, y= Proportion, fill=height_bin)) +
  geom_bar(width = 0.25, stat="identity", position = "fill")+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Proportion of height", x ="Season", y = "Proportion")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
  facet_wrap(~ Site)

```

```{r}
#graphing shell height ASHC

height_ASHC<- Height_master %>% filter(Site == "ASHC")

ggplot(height_ASHC, aes(x=Season, y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

ggplot(data=height_ASHC, aes(x= Height, fill = )) +
  geom_bar()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Ash Creek Height ", x ="Height (mm)")+
  facet_wrap(~ Season, scales = "free")

```
```{r}
#graphing shell height FENC

height_FENC<- Height_master %>% filter(Site == "FENC")

ggplot(height_FENC, aes(x=Season, y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```
```{r}
#graphing shell height GOLD

height_GOLD<- Height_master %>% filter(Site == "GOLD")

ggplot(height_GOLD, aes(x=Season, y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```
```{r}
#graphing shell height LAUR

height_LAUR<- Height_master %>% filter(Site == "LAUR")

ggplot(height_LAUR, aes(x=Season, y=Height, fill=Season)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Shell Height", x ="Season", y = "Height (mm)")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```
#Old code originally for June 2023 survey data format
```{r}
#oyster density metrics 


#sum total number of oysters counted per quadrat
quadratdensity$AllCount_Total <- rowSums(quadratdensity[, c("LiveCount_Total", "BoxCount_Total", "GaperCount_Total")])

#summary of each oyster type by site. output = Site, N, Mean, stnd dev, stnd error, and confidence interval
all_density_SE <-summarySE(data = quadratdensity, measurevar = "AllCount_Total", groupvars=c("Site_Name"))
all_density_SE
live_density_SE <- summarySE(data = quadratdensity, measurevar = "LiveCount_Total", groupvars=c("Site_Name"))
box_density_SE <-summarySE(data = quadratdensity, measurevar = "BoxCount_Total", groupvars=c("Site_Name"))
gaper_density_SE <-summarySE(data = quadratdensity, measurevar = "GaperCount_Total", groupvars=c("Site_Name"))

#calculate percent standard error as 100*se/mean
all_density_SE$PSE_all <- 100*(all_density_SE$se/all_density_SE$AllCount_Total)
live_density_SE$PSE_live <- 100*(live_density_SE$se/live_density_SE$LiveCount_Total)
box_density_SE$PSE_box <- 100*(box_density_SE$se/box_density_SE$BoxCount_Total)
gaper_density_SE$PSE_gaper <- 100*(gaper_density_SE$se/gaper_density_SE$GaperCount_Total)


#join into 1 table 
densitysummary <- subset(all_density_SE, select = -c(sd,se,ci)) %>%
    left_join(subset(live_density_SE, select = -c(N,sd,se,ci)), by = "Site_Name") %>%
    left_join(subset(box_density_SE, select = -c(N,sd,se,ci)), by = "Site_Name") %>%
    left_join(subset(gaper_density_SE, select = -c(N,sd,se,ci)), by = "Site_Name") %>%

#renaming for clarity. need to use dplyr:: because another package is overriding the function
#densitysummary <- densitysummary %>%
    dplyr::rename(
      AllCount_Mean = AllCount_Total,
      LiveCount_Mean = LiveCount_Total,
      BoxCount_Mean = BoxCount_Total, 
      GaperCount_Mean = GaperCount_Total, 
      NumQuad = N) %>%
  
#calculate completeness as 100*N/12, where 12 is the desired number of quadrats per site 
  mutate(PercentComplete_Quad = ((NumQuad/12)*100) )


write.csv(densitysummary, "C:/Users/meghana.parikh/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological\\populationdensity_summary.csv", row.names=FALSE)
#note that PSE is >20 percent at Ash Creek, and at Fence creek in box and gaper categories. This is due to the different levels of sampling. Need to redo with categories 


```



```{r}

#oyster size distribution

#finding the empty values - these are oyster samples collected for lab use I think?
emptyvalues <- shellsize %>% filter(is.na(Height_mm))
      
shellsize_all <- 
  shellsize %>% group_by(Site_Name) %>%
  summarise(
    median_height=median(Height_mm, na.rm = TRUE), 
    min_height=min(Height_mm, na.rm = TRUE), 
    max_height=max(Height_mm, na.rm = TRUE), 
    Q1=quantile(Height_mm,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height_mm,probs = 0.75, na.rm = TRUE))%>%
  mutate(SpecimenType = "All")

shellsize_live <- 
  shellsize %>% filter(SpecimenType=="Live") %>%
   summarise(
    median_height=median(Height_mm, na.rm = TRUE), 
    min_height=min(Height_mm, na.rm = TRUE), 
    max_height=max(Height_mm, na.rm = TRUE), 
    Q1=quantile(Height_mm,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height_mm,probs = 0.75, na.rm = TRUE))%>%
  mutate(SpecimenType = "Live")

shellsize_box <- 
  shellsize %>% filter(SpecimenType=="Box") %>%
   summarise(
    median_height=median(Height_mm, na.rm = TRUE), 
    min_height=min(Height_mm, na.rm = TRUE), 
    max_height=max(Height_mm, na.rm = TRUE), 
    Q1=quantile(Height_mm,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height_mm,probs = 0.75, na.rm = TRUE))%>%
  mutate(SpecimenType = "Box")

shellsize_gaper <- 
  shellsize %>% filter(SpecimenType=="Gaping") %>%
   summarise(
    median_height=median(Height_mm, na.rm = TRUE), 
    min_height=min(Height_mm, na.rm = TRUE), 
    max_height=max(Height_mm, na.rm = TRUE), 
    Q1=quantile(Height_mm,probs = 0.25, na.rm = TRUE),
    Q3=quantile(Height_mm,probs = 0.75, na.rm = TRUE))%>%
  mutate(SpecimenType = "Gaper")

#rbind together 

shellsize_summary <- rbind(shellsize_all, shellsize_live, shellsize_box, shellsize_gaper)

#size distribution summary
#note that calculating PSE and accuracy do not make sense for size distributions. Will need to figure out new metrics for the QAPP
write.csv(shellsize_summary, "C:/Users/meghana.parikh/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Biological\\shellsize_summary.csv", row.names=FALSE)

  
```
```{r}
sessionInfo()
```