---
title: "RFTM"
author: ""
date: "1/22/2024"
output: html_document

description: This R code is used to import and summarize RFTM (Rays Fluid Thioglycollate Medium) intensity scoring from the LISS Oyster Health Project's monthly sampling at Ash Creek and Fence Creek intertidal sites in Connecticut and Goldstar beach and Laurel Hollow subtidal sites on Long Island, NY. The scale used to score intensity for individuals is the Mackins Scale (citation). This score can be used to calculate prevalence, weighted prevalence and intensity across the population. 
---

Last updated 1/22/2024 by Kyra Lenderman




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
library("dplyr")                                    
library("plyr")                                     
library("readr")             
library("Rmisc")
library("ggplot2")
library("lubridate")
```

```{r}
# knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
#knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
knitr::opts_knit$set(root.dir = 'C:/Users/kelly.roper/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kelly's

```

### This code chunk merges all .csv files within the Tissue processing folder into one data fram and outputs the full dataset into a .csv master file. This allows us to download the raw data as a .csv, add it to the repository folder, and create the master data file without copying and pasting data in excel.
# reading in .csv files from local folder
```{r}
data_all <- list.files(path = "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Lab_Data_RFTM/Files_by_Month",                           # Identify all CSV files
  pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>%                              # Store all files in list
  bind_rows                                         # Combine data sets into one data set 
data_all                                            # Print data to RStudio console

as.data.frame(data_all)                            # Convert tibble to data.frame

tail(data_all)

write.csv(data_all, "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Lab_Data_RFTM\\All_RFTM_data.csv", row.names=FALSE)
```


## adding a month column to the data

```{r}
data_all <- data_all %>%
  mutate(date_collected= as.Date(date_collected), month = month(date_collected))

data_all
```

#Filtering NAs 
```{r}
data_all <- data_all %>% filter(!is.na(date_collected))
data_all

```

#This chunk of code is removing 0723LAUR_20 and 0723LAUR_26 from the datasheet as they have been identified as spat on shell to avoid bias in the data. During this sample collection there were animals that were significantly smaller than the single set oysters. 
```{r}
data_all <- data_all %>%
  subset(lab_id != "0723LAUR_20") %>%
  subset(lab_id != "0723LAUR_26")



```

# Summary of all data and Completeness Check
```{r}
st_rftm_final <- summarySE(data_all, measurevar="rftm_final", groupvars=c("site", "date_collected"))
st_rftm_final

#Calculate completeness for QC
st_rftm_final$Completeness <- st_rftm_final$N /30

st_rftm_final

write.csv(st_rftm_final, "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Lab_Data_RFTM\\Completeness_RFTM_intensity_data.csv", row.names=FALSE)
```

# Comparied reader 1 and reader 2
  --- THis is not currently working properly -- Currently calling everything with two reads to be TRUE
  
```{r}
data_all$results = ifelse(data_all$rftm_intensity_read1 < data_all$rftm_intensity_read2, 'FALSE',
  ifelse(data_all$rftm_intensity_read1 > data_all$rftm_intensity_read2, 'FALSE',
  ifelse(data_all$rftm_intensity_read1 == data_all$rftm_intensity_read2, 'TRUE', NA)))
  
data_all
```



```{r}
Data_Accuracy = data.frame(data_all$lab_id,data_all$date_collected, data_all$site, data_all$rftm_intensity_read1, data_all$rftm_intensity_read2, data_all$results)

Data_Accuracy <- na.omit(Data_Accuracy)
Data_Accuracy
```

# Accuracy Output
```{r}
#count TRUE values in vector
x <- Data_Accuracy %>% 
  dplyr::group_by(data_all.site, data_all.date_collected, data_all.results) %>% 
  dplyr::summarise(count = n())
x2 <- x %>% 
  dplyr::group_by()
x
T <- nrow(Data_Accuracy %>% filter(data_all.results == 'TRUE'))
F <- nrow(Data_Accuracy %>% filter(data_all.results == 'FALSE'))

Accuracy <- T/(T+F)
Accuracy

#write.csv(Data_Accuracy, "C:/Users/katherine.mcfarland/Documents/4. GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Lab_Data_RFTM\\Accuracy_RFTM_intenisty_data.csv", row.names=FALSE)
```

#Graphing Weighted prevalence(= Sum of individual intensity scores / total number of oyster sampled)

```{r, echo=FALSE}
ggplot(data=data_all, aes(x=month, y=rftm_final, fill=site)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted prevalence of Dermo infection", x ="Date", y = "Weighted prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
  facet_wrap(~site)

```
```{r}
#Graphing mean weighted prevalence over time
df_wp_summary <- data_all %>%
  dplyr::group_by(site, month) %>% 
  dplyr::summarize( Weighted_prevalence = mean(rftm_final))
df_wp_summary

ggplot(data=df_wp_summary, aes(x=month, y=Weighted_prevalence, color=site)) +
  geom_point()+  
  geom_line(aes(group = site))+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted Prevalence of Dermo infection", x ="Month", y = "Weighted Prevalence Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```

# Prevalence calculations for all sites
# Prevalence = # infected/ total # sampled
```{r}
## Prevalence T/F

data_all<-data_all%>% filter(!is.na(rftm_final))
data_all

data_all$prevalent = ifelse(data_all$rftm_final == 0, '0',
  ifelse(data_all$rftm_final > 0, '1', NA))
  
data_all

# YEARLY PREVALENCE %
present <- nrow(data_all %>% filter(prevalent == '1'))
absent <- nrow(data_all %>% filter(prevalent == '0'))

prevalence_all <- present/(present+absent)
prevalence_all
# 67.9%

str(data_all$prevalent)
data_all$prevalent <- as.numeric(data_all$prevalent)

df_prevalence_summary <- data_all %>%
  dplyr::group_by(site, month) %>% 
  dplyr::summarize( prevalence_precentage= mean(prevalent)* 100)
df_prevalence_summary

```
#Graphing mean prevalence 
```{r}

ggplot(data=df_prevalence_summary, aes(x=month, y=prevalence_precentage, color=site)) +
  geom_point()+  
  geom_line(aes(group = site))+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence of Dermo infection", x ="Month", y = "Dermo Prevaence %")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))
```
```{r}

ggplot(data=df_prevalence_summary, aes(x=site, y=prevalence_precentage, fill = site)) +
 geom_boxplot()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence of Dermo infection", x ="Site", y = "Dermo Prevaence %")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))
```

# Intensity all sites (Sum of intensity scores/# of infected oysters)
# intensity calculation for august gold star needs to be fixed. 
```{r}
data_all

data_all$rftm_final<-as.numeric(as.character(data_all$rftm_final))

df_intensity_summary <- data_all %>%
  dplyr::group_by(site, month) %>% 
  dplyr::summarize( intensity = sum(rftm_final, na.rm= TRUE)/sum(prevalent, na.rm = TRUE))
df_intensity_summary

# Need to fix 0823GOLD? Looked at the raw data sheet and the scores were all 0. 
```
```{r}

ggplot(data=df_intensity_summary, aes(x=month, y=intensity, color=site)) +
  geom_point()+  
  geom_line(aes(group = site))+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Intensity of Dermo infection", x ="Month", y = "Intensity score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12)) + scale_y_continuous(limits = c(0, 3))

```
```{r}

## Stacked bar graph showing proportions per month of intensity scores

## Not letting be add a 5 category - need to figure out why
## Also gold star is missing data? 


df_intensity_proportions<- data_all %>%
  mutate(rftm_final_numeric = as.numeric(rftm_final),intensity_bin = case_when(rftm_final == 0 ~ "0", rftm_final == 0.5 ~"0.5",rftm_final == 1 ~ "1", rftm_final == 2 ~"2",rftm_final == 3 ~ "3", rftm_final == 4 ~"4",rftm_final == 5 ~ "5", TRUE ~ as.character(rftm_final))) %>%
  group_by(site, month, intensity_bin) %>%
  summarise(Count= n()) %>%
  ungroup() %>%
  mutate(Proportion = Count/sum(Count))

df_intensity_proportions<- na.omit(df_intensity_proportions)

df_intensity_proportions

ggplot(data=df_intensity_proportions, aes(x=month, y= Proportion, fill=intensity_bin)) +
  geom_bar(width = .5, stat="identity", position = "fill",colour = "black")+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Proportion of Intensity scores of Dermo infection", x ="month", y = "Proportion")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
 scale_fill_brewer() +
  facet_wrap(~ site)

```

# Ash Creek Summary
```{r}
df_ASHC <- data_all%>%
  filter(site=="ASHC")
df_ASHC 

#Weighted prevalence 
st_intensity_ASHC <- summarySE(df_ASHC, measurevar="rftm_final", groupvars=c("month"))
st_intensity_ASHC

#Prevalence
df_ASHC_prevalence <- df_prevalence_summary %>% 
  filter(site == "ASHC")
df_ASHC_prevalence

#Intensity Index
df_ASHC_intensity <- df_intensity_summary %>%
  filter(site == "ASHC")
df_ASHC_intensity


```


```{r, echo=FALSE}
#Graphing weighted prevalence ASHC

ggplot(data=df_ASHC, aes(x=month, y=rftm_final, group= month)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Ash Creek Weighted Prevalence Dermo infection", x ="Month", y = "Weighted Prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))


#Weighted prevalence
ggplot(data=st_intensity_ASHC, aes(x=month, y=rftm_final)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted Prevalence of Dermo infection", x ="Month", y = "Weighted Prevalence Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

##Prevalence
ggplot(data=df_ASHC_prevalence, aes(x=month, y=prevalence_precentage)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence", x ="Month", y = "Prevalence precent")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

#Intensity index
ggplot(data=df_ASHC_intensity, aes(x=month, y=intensity)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Ash Creek Intensity Index", x ="Month", y = "Intensity Index")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))
```



# Fence Creek Summary
```{r}
df_FENC <- data_all%>%
  filter(site=="FENC")
df_FENC 

#Weighted prevalence

st_intensity_FENC <- summarySE(df_FENC, measurevar="rftm_final", groupvars=c("month"))
st_intensity_FENC

#Prevalence
df_FENC_prevalence <- df_prevalence_summary %>% 
  filter(site == "FENC")
df_FENC_prevalence

#Intensity Index
df_FENC_intensity <- df_intensity_summary %>%
  filter(site == "FENC")
df_FENC_intensity

```

```{r, echo=FALSE}
#Graphing weighted prevalence FENC

ggplot(data=df_FENC, aes(x=date_collected, y=rftm_final, group= date_collected)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Fence Creek Weighted prevalence Dermo infection", x ="Date", y = "Weighted prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))


#Weighted prevalence
ggplot(data=st_intensity_FENC, aes(x=month, y=rftm_final)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted Prevalence of Dermo infection", x ="Month", y = "Weighted Prevalence Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

##Prevalence
ggplot(data=df_FENC_prevalence, aes(x=month, y=prevalence_precentage)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence", x ="Month", y = "Prevalence precent")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

#Intensity index
ggplot(data=df_FENC_intensity, aes(x=month, y=intensity)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Fence Creek Intensity Index", x ="Month", y = "Intensity Index")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```
# Laurel Hollow summary
```{r}
df_LAUR <- data_all%>%
  filter(site=="LAUR")
df_LAUR 

#weighted prevalence
st_intensity_LAUR <- summarySE(df_LAUR, measurevar="rftm_final", groupvars=c("date_collected"))
st_intensity_LAUR

```

```{r, echo=FALSE}

#Graphing weighted prevalence LAUR

ggplot(data=df_LAUR, aes(x=date_collected, y=rftm_final, group= date_collected)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Laurel Hollow Weighted prevalence of Dermo infection", x ="Date", y = "Weighted Prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```

# Gold Star summary
```{r}
df_GOLD <- data_all%>%
  filter(site=="GOLD")
df_GOLD 

df_GOLD <- df_GOLD %>% filter(!is.na(rftm_final))

#Weighted prevalence
st_intensity_GOLD <- summarySE(df_GOLD, measurevar="rftm_final", groupvars=c("month"))
st_intensity_GOLD

#Prevalence
df_GOLD_prevalence <- df_prevalence_summary %>% 
  filter(site == "GOLD")
df_GOLD_prevalence

#Intensity Index
df_GOLD_intensity <- df_intensity_summary %>%
  filter(site == "GOLD")
df_GOLD_intensity


df_GOLD_proportions<-df_intensity_proportions %>%
  filter(site =="GOLD")

df_GOLD_proportions
```

```{r, echo=FALSE}

#Graphing weighted prevalence GOLD

ggplot(data=df_GOLD, aes(x=month, y=rftm_final, group= date_collected)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Gold Star Beach Weighted prevalence of Dermo infection", x ="Date", y = "Weighted Prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

#Weighted prevalence
ggplot(data=st_intensity_GOLD, aes(x=month, y=rftm_final)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted Prevalence of Dermo infection", x ="Month", y = "Weighted Prevalence Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

##Prevalence
ggplot(data=df_GOLD_prevalence, aes(x=month, y=prevalence_precentage)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence", x ="Month", y = "Prevalence precent")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

#Intensity index
ggplot(data=df_GOLD_intensity, aes(x=month, y=intensity)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Goldstar Beach Intensity Index", x ="Month", y = "Intensity Index")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

#Proportions

ggplot(data=df_GOLD_proportions, aes(x=month, y= Proportion, fill=intensity_bin)) +
  geom_bar(width = .5, stat="identity", position = "fill", colour = "black")+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Proportion of Intensity scores of Dermo infection", x ="month", y = "Proportion", fill = "Intensity Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
   scale_fill_brewer() +
   scale_x_continuous( breaks = seq(5,12, by =1) )
#+facet_wrap(~ site)

```
# This chunk of data combines tissue processing and RFTM data into one sheet to observe disease across zones and light regimes for ASHC and FENC
# We want to determine whether or not to continue using zone and light regime for collections - are there differences between them? 
```{r}
#Tissue processing data
data_all_tissue <- list.files(path = "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Lab_Data_TissueProcessing/Files_by_Month",                           # Identify all CSV files
  pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>%                              # Store all files in list
  bind_rows                                         # Combine data sets into one data set 
data_all_tissue      

data_all_tissue <- data_all_tissue %>%
  mutate(date_collected= as.Date(date_collected), month = month(date_collected))

data_all_tissue<- data_all_tissue %>%
  mutate(condition_score = recode(condition, 
                                     "1_very_good" = 1, "2_good" = 2, "3_good_minus"= 3, "4_fair_plus"= 4, "5_fair"= 5,"6_fair_minus"= 6, "7_poor_plus"=7,
                                     "8_poor"= 8, "9_very_poor"= 9))
head(data_all_tissue)

# Print data to RStudio console

as.data.frame(data_all_tissue)                            # Convert tibble to data.frame

# Subset CT sites using zone and light regime 
df_tissue_CT<- data_all_tissue%>%
  filter(site %in% c("ASHC", "FENC"))
df_tissue_CT

#merging tissue processing and RFTM 
df_combined <- merge(data_all, df_tissue_CT, by= c("lab_id", "date_collected", "site", "lab_sample"))
df_combined

df_combined2 <- merge(data_all, data_all_tissue, by= c("lab_id", "date_collected", "site", "lab_sample"))
df_combined2

#subset by site
df_combined_ASHC<- df_combined%>%
  filter(site == "ASHC")
df_combined_ASHC

df_combined_FENC<- df_combined%>%
  filter(site == "FENC")
df_combined_FENC
```
```{r}
#graphing intensity scores by body condition to see if there is a relationship across all sites
ggplot(data=df_combined2, aes(x=rftm_final, y=condition_score)) +
  geom_point()+   
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Intensity of Dermo infection vs body condition score", x ="Intensity Dermo Score", y = "Body Condition Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```

```{r, echo=FALSE}
# ASHC 
ggplot(data=df_combined_ASHC, aes(x=oyster_zone, y=rftm_final, group= oyster_zone, fill = oyster_zone)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Intensity of Dermo infection", x ="Zone", y = "Dermo Intensity Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```
```{r, echo=FALSE}
# FENC 
#Zone
ggplot(data=df_combined_FENC, aes(x=oyster_zone, y=rftm_final, group= oyster_zone, fill = oyster_zone)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Intensity of Dermo infection", x ="Zone", y = "Dermo Intensity Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

#Light regime
ggplot(data=df_combined_FENC, aes(x=light_regime, y=rftm_final, group= light_regime, fill = light_regime)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Intensity of Dermo infection", x ="Light Regime", y = "Dermo Intensity Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))


```

Version
```{r}
sessionInfo()
```

