---
title: "Cleanup_TEST"
author: "Mariah Kachmarr"
date: "2024-07-25"
output: html_document
---

# Objective:

* call the raw data files for fence creek 2023 & 2024. We recovered what we thought was lost data.This code is pulling in that data file, cleaning, and graphing to make sure that it will be suitable to incorporate with our previous data. 

* **output**: "Sonde_master_FENC.csv"


## Setup: 

* call your root directory, using opts_knit assigns for the entire script so your paths will alwyas be from this start point!

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      cache = TRUE)

#knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/EAD-ASEB_EPA_LISS_Disease_Surveillance/Sonde_Data")
#knitr::opts_knit$set(root.dir = "C:/Users/kyra.lenderman/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Sonde_Data")
knitr::opts_knit$set(root.dir = "C:/Users/mariah.kachmar/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Sonde_Data")
#knitr::opts_knit$set(root.dir = "C:/Users/kelly.roper/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Sonde_Data") 
```
```

* load libraries

```{r load_libraries, include = TRUE}
# load libraries - notes show the install command needed to install (pre installed)
# Plotting
library(ggplot2)
library(dplyr)
library(gplots)
library(RColorBrewer)
library(ggpubr)
library(stringr)
library(lubridate)
library(readr)
library(reshape2)
library(tidyverse) # read_csv call from readr, included in tidyverse
```


* set your data path, this is a string name as "path.raw" will will 'paste' this to the end of 
our path (called above) to output to the folder raw_data. 

* *Note* in order to run this properly there must be an existing folder called "raw_data" in the Sonde_Data folder

```{r}

path.raw <- "raw_data/"

# using the paste0 function we will add the whole path together, check it out in the example below! 
# paste0 does not require you to set your separation between calls, so we will manually assign as "/"
paste0(getwd(),"/",path.raw) # you see the whole directory prints including the raw_data folder! yay.


```

## Ready. Set. ReadAndFormatRawDataToMerge! 

*IMPORTANT*: We realized that there are a few cases in which raw Sonde data differ, so the following is a bit cumbersome
built to successfully reformat dates according to how they are presented raw, using **lubridate**! 

* first, we need to make a generate a list of file names

```{r generate list of file names}

file.names         <- data.frame(txt.files = 
                                         (basename(list.files(path = paste0(getwd(),"/",path.raw), 
                                                              pattern = "csv$", 
                                                              recursive = FALSE)))) 

file.names

```

* second, assign your *blank* master dataframe 

```{r}

Master_FENC <- data.frame() 

```

* third, run the loop

  * calls each csv file in 'file.names.2024' one by one, reformts them using 'lubridate', and 'rbind' (row bind) to Master_2023
  

  
```{r run the crazy loop}

# for loop to merge all csv files to one dataframe

for (m in 1:nrow(file.names)) { # this is your loop, for each row in th filenames tbale, do the followin!
  # NOTE: you will 'm' used in this loop to read and assign data
  
  
  # call the dir of the csv file in loop using paste0 to 'paste' the strings for the 
  # working directry, path to raw data, and the mth file name in the loop
  raw_Sonde_rootdir        <- paste0(getwd(),"/",path.raw,file.names[m,1]) #reads in the data files
  
  # We need to skip some lines, and this can differ Sonde to Sonde based on the equipment tech specs info, etc. 
  # to do this we will use readLines then grep to call the row that contains the delimiter 'Date Time', 
  # becasue this is where the target data begins! (actual measured readings!)
  D        <- readLines(raw_Sonde_rootdir) 
  ind      <- grep('Date Time',D) # the row number where the data begins, containing 'Date Time'

  # read the data using read_csv and skip columns based on 'ind' above 
  raw      <- read_csv(raw_Sonde_rootdir,skip=ind-1,col_types = cols())
  raw_df   <- as.data.frame(raw) # ocnvert the dataframe now that you skipped the crappola 
  
  # if you look at the raw data, its MESSY , containing the Sonde=--specific ID number in each column, this will NOT let us merge datasets
  # a few more lines, commented to explain why...
  # columns  <- names(raw) # what are the column names?  - youll see why
  raw_df[2:(ncol(raw_df))] <- lapply(raw_df[2:(ncol(raw_df))],as.numeric) # convert all data  to numeric
  names(raw_df) <- sapply(strsplit(names(raw_df), '\\s*[()]'), `[`, 1) # ommit all numeric column data, also the format of the units does not pair between datasets
  # raw_df[,1] # remove the # and reun this if you want to see th raw date format of an individual file - rationalize why we have a crazy conditioninal statement below

  # As of 6/3/2024, all data is in format mdy_hm, use lubridate to format to POSIXct format 
  raw_df[,1] <- mdy_hm(raw_df[,1])
  
  # add a column for the site 
  filename      <- file.names[m,1]
  raw_df        <- raw_df %>% 
                    dplyr::mutate(Site = sub(".*_(.*)_.*","\\1",filename),
                    Date = gsub("_.*","",filename)) 
  
  Master_FENC <- rbind(raw_df, Master_FENC) #bind to a cumulative list dataframe
}

names(raw_df)
names(Master_FENC)

```


## Cleanup and print 

* remove the columns "External Voltage", "Battery Capacity", "Barometric Pressure", "Date" ( DAte is an extra column we have a correct date in there already)

```{r cleanup and r}

Master_FENC_output <- Master_FENC %>%  
                      dplyr::select(-c("External Voltage", "Battery Capacity", "Barometric Pressure", "Date")) 
Master_FENC_output <- na.omit(Master_FENC_output)

write.csv(Master_FENC_output, "output/Sonde_master_FENC.csv")
```

```{r load data}

Master_FENC_table <- Master_FENC_output # check.names = F allows with col names with spaces (opthwise fills with a '.' )

Master_FENC_table$'Date Time' <- lubridate::ymd_hms(Master_FENC_table$'Date Time')



```

```{r}
# melt is akin to pivot_longer, but I like that its called melt so I prefer it
# Im melting Im melting
library(reshape2)
Master_table_LONG <- Master_FENC_table %>%  
                      melt(id.vars = c('Date Time', 'Site'),
                                    measure.vars = c('Actual Conductivity', 'Salinity', 'Resistivity', 
                                                     'Total Dissolved Solids' ,'RDO Concentration', 'RDO Saturation',
                                                     'Oxygen Partial Pressure', 'Chlorophyll-a Fluorescence', 'pH', 'pH mV', 
                                                     'Temperature'))

# View the blobs! 
ggplot(Master_table_LONG,
         aes(x='Date Time',
             y= value,
             )) +
  geom_point() +
  theme_classic() + 
  facet_wrap(~variable, scales = "free_y")

```

* As suspected this visual is horrible.. we have TONS of data, every 10 seconds to be exact! 

* if we want to view trends, we need to narrow down 

### Hourly means


```{r}
Master_table_LONG_means <- Master_FENC_table %>%  
                      dplyr::mutate('Date Time' = as.factor(substr('Date Time',1,13))) %>% # remove minutes and seconds
                      melt(id.vars = c("Date Time", "Site"),
                                    measure.vars = c('Actual Conductivity', 'Salinity', 'Resistivity', 
                                                     'Total Dissolved Solids' ,'RDO Concentration', 'RDO Saturation',
                                                     'Oxygen Partial Pressure', 'Chlorophyll-a Fluorescence', 'pH', 'pH mV', 
                                                     'Temperature')) %>% 
                      dplyr::group_by('Date Time', Site, variable) %>% 
                      summarise_each(funs(mean, sd, se=sd(.)/sqrt(n())), value) %>% 
                      #dplyr::mutate('Date Time' = ymd_h('Date Time')) # reformat back to date
                      dplyr::mutate('Date Time' = as.Date('Date Time', format = "%Y-%m-%d %H"))


vars <- as.data.frame(
          list(
            as.character(
              unique(
                Master_table_LONG_means$variable)))) %>% 
        dplyr::rename(dat = 1)


```

```{r}


FENC_pH          <- Master_FENC_output %>% select('Date Time', pH, Site)
FENC_Salinity   <- Master_table_LONG_means %>% dplyr::filter(variable == 'Salinity' & Site %in% c('FENC'))
FENC_Temperature <- Master_table_LONG_means %>% dplyr::filter(variable == 'Temperature' & Site %in% c('FENC'))
FENC_DO          <- Master_table_LONG_means %>% dplyr::filter(variable == 'RDO Concentration' & Site %in% c('FENC'))
FENC_CHLA        <- Master_table_LONG_means %>% dplyr::filter(variable == 'Chlorophyll-a Fluorescence' & Site %in% c('FENC'))

# pH 

FENC_pH_2023 <- FENC_pH %>% na.omit() %>%
             dplyr::filter(`Date Time` > '2023-06-01 00:00:00' & `Date Time` < '2023-11-30 00:00:00')  %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Ash Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=pH, # the mean values
                      group= Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
             # geom_errorbar(aes(ymin=(mean)-(se), 
              #                  ymax=(mean)+(se)), 
              #              width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("pH 2023") +
              labs(x = "Time", y = "pH") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))


FENC_pH_2023


#pdf(paste0(path = "output/raw_plots/Report_plots/FENC_pH_2023.pdf"), height = 7, width = 14)
#print(FENC_pH_2023)
#dev.off()
  
FENC_pH_2024 <- FENC_pH %>% na.omit() %>%
             dplyr::filter('Date Time' > '2024-03-01 00:00:00' & 'Date Time' < '2024-11-30 00:00:00' ) %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Ash Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=mean, # the mean values
                       group=Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
              geom_errorbar(aes(ymin=(mean)-(se), 
                                ymax=(mean)+(se)), 
                            width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("pH 2024 ") +
              labs(x = "Time", y = "pH") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))


FENC_pH_2024


#pdf(paste0(path= "output/raw_plots/Report_plots/FENC_pH_.pdf"), height = 7, width = 14)
#print(FENC_pH_2024)
#dev.off()

# Salinity 

FENC_Salinity_2023 <- FENC_Salinity %>% na.omit() %>%
             dplyr::filter('Date Time' > '2023-06-01 00:00:00' & 'Date Time' < '2023-11-30 00:00:00' ) %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Fence Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=mean, # the mean values
                       group=Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
              geom_errorbar(aes(ymin=(mean)-(se), 
                                ymax=(mean)+(se)), 
                            width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("Salinity 2023") +
              labs(x = "Time", y = "Salinity") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))+
              scale_y_continuous(breaks = seq(0,30, by = 2))

FENC_Salinity_2023

#pdf(paste0(path = "output/raw_plots/Report_plots/FENC_Salinity_2023.pdf"), height = 7, width = 14)
#print(FENC_Salinity_2023)
#dev.off()

FENC_Salinity_2024 <- FENC_Salinity %>% na.omit() %>%
             dplyr::filter('Date Time' > '2024-03-01 00:00:00' & 'Date Time' < '2024-11-30 00:00:00' ) %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Fence Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=mean, # the mean values
                       group=Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
              geom_errorbar(aes(ymin=(mean)-(se), 
                                ymax=(mean)+(se)), 
                            width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("Salinity 2024") +
              labs(x = "Time", y = "Salinity") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))+
              scale_y_continuous(breaks = seq(0,30, by = 2))

FENC_Salinity_2024

#pdf(paste0(path = "output/raw_plots/Report_plots/FENC_Salinity_2024.pdf"), height = 7, width = 14)
#print(FENC_Salinity_2024)
#dev.off()

# Temperature 

FENC_Temperature_2023 <-FENC_Temperature %>% na.omit() %>%
             dplyr::filter('Date Time' > '2023-06-01 00:00:00' & 'Date Time' < '2023-11-30 00:00:00' ) %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Fence Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=mean, # the mean values
                       group=Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
              geom_errorbar(aes(ymin=(mean)-(se), 
                                ymax=(mean)+(se)), 
                            width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("Temperature 2023") +
              labs(x = "Time", y = "Temperature (Celcius)") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))
FENC_Temperature_2023


#pdf(paste0(path="output/raw_plots/Report_plots/FENC_Temperature_2023.pdf"), height = 7, width = 14)
#print(FENC_Temperature_2023)
#dev.off()

FENC_Temperature_2024 <-FENC_Temperature %>% na.omit() %>%
             dplyr::filter('Date Time' > '2024-03-01 00:00:00' & 'Date Time' < '2024-11-30 00:00:00' ) %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Fence Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=value, # the mean values
                       group=Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
              geom_errorbar(aes(ymin=(mean)-(se), 
                                ymax=(mean)+(se)), 
                            width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("Temperature") +
              labs(x = "Time", y = "Temperature (Celcius)") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))
FENC_Temperature_2024


#pdf(paste0(path="output/raw_plots/Report_plots/FENC_Temperature_2024.pdf"), height = 7, width = 14)
#print(FENC_Temperature_2024)
#dev.off()

# DO 

FENC_DO_2023 <- FENC_DO %>% na.omit() %>%
             dplyr::filter('Date Time' > '2023-06-01 00:00:00' & 'Date Time' < '2023-11-30 00:00:00' ) %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Fence Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=mean, # the mean values
                       group=Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
              geom_errorbar(aes(ymin=(mean)-(se), 
                                ymax=(mean)+(se)), 
                            width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("DO Concentration 2023") +
              labs(x = "Time", y = "DO Concentration (mg/L)") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))

#pdf(paste0(path = "output/raw_plots/Report_plots/FENC_DO_2023.pdf"), height = 7, width = 14)
#print(FENC_DO_2023)
#dev.off()

FENC_DO_2024 <- FENC_DO %>% na.omit() %>%
             dplyr::filter('Date Time' > '2024-03-01 00:00:00' & 'Date Time' < '2024-11-30 00:00:00' ) %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Fence Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=mean, # the mean values
                       group=Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
              geom_errorbar(aes(ymin=(mean)-(se), 
                                ymax=(mean)+(se)), 
                            width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("DO Concentration 2024") +
              labs(x = "Time", y = "DO Concentration (mg/L)") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))

#pdf(paste0(path = "output/raw_plots/Report_plots/FENC_DO_2024.pdf"), height = 7, width = 14)
#print(FENC_DO_2024)
#dev.off()

#Chlorophyll-a

FENC_CHLA_2023 <- FENC_CHLA %>% na.omit() %>%
             dplyr::filter('Date Time' > '2023-06-01 00:00:00' & 'Date Time' < '2023-11-30 00:00:00' ) %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Fence Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=mean, # the mean values
                       group=Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
              geom_errorbar(aes(ymin=(mean)-(se), 
                                ymax=(mean)+(se)), 
                            width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("Chlorophyll-a flourescences 2023") +
              labs(x = "Time", y = "Chlorophyll-a (RFU)") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))

FENC_CHLA_2023

#pdf(paste0(path="output/raw_plots/Report_plots/FENC_CHLA_2023.pdf"), height = 7, width = 14)
#print(FENC_CHLA_2023)
#dev.off()

FENC_CHLA_2024 <- FENC_CHLA %>% na.omit() %>%
             dplyr::filter('Date Time' > '2024-03-01 00:00:00' & 'Date Time' < '2024-11-30 00:00:00' ) %>% 
             dplyr::mutate(Site = case_when(Site == 'FENC' ~ 'Fence Creek', .default = 'Fence Creek')) %>% 
             ggplot(aes(x='Date Time', 
                       y=mean, # the mean values
                       group=Site)) + # call the new mean
              geom_line(aes(group = factor(Site), # lines for site
                                linetype = Site), 
                            size = 0.2, 
                            position=position_dodge(.4)) + 
              # scale_linetype_manual(values=c("solid", "dashed")) +
              geom_point(aes(shape=Site, 
                             fill=Site)) + 
              scale_shape_manual(values=c(21, 22, 24, 25)) + 
              scale_fill_manual(values=c("#D55E00",  "#0072B2")) + # "#CC79A7","#009E73"
              geom_errorbar(aes(ymin=(mean)-(se), 
                                ymax=(mean)+(se)), 
                            width=0,position=position_dodge(.4)) +
              facet_grid(rows = vars(Site)) + # , scales = "free_y" - if you wnat different y axis labels
              ggtitle("Chlorophyll-a flourescences 2024") +
              labs(x = "Time", y = "Chlorophyll-a (RFU)") +
              theme_classic() +
              theme(legend.position = "none", axis.text= element_text(size= 15))

FENC_CHLA_2024

#pdf(paste0(path="output/raw_plots/Report_plots/FENC_CHLA_2024.pdf"), height = 7, width = 14)
#print(FENC_CHLA_2024)
#dev.off()
```