---
title: "Merge_Clean_Files"
author: "Samuel Gurr"
date: "2024-06-03"
output: html_document
---

# Objective:

* super breif script to simply merge the generated master files from Cleanup_2023, Cleanup_2024, etc. into one


## Setup: 

* call your root directory, using opts_knit assigns for the entire script so your paths will alwyas be from this start point!

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      cache = TRUE)

knitr::opts_knit$set(root.dir = "C:/Users/samjg/Documents/Github_repositories/EAD-ASEB_EPA_LISS_Disease_Surveillance/Sonde_Data")
#knitr::opts_knit$set(root.dir = "C:/Users/kyra.lenderman/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Sonde_Data")
#knitr::opts_knit$set(root.dir = "C:/Users/mariah.kachmar/documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Sonde_Data")

```


## Load data:

```{r load data}

Sonde_2023 <- read.csv("output/Sonde_master_2023.csv", check.names = F) %>% dplyr::select(-1)
Sonde_2024 <- read.csv("output/Sonde_master_2024.csv", check.names = F) %>% dplyr::select(-1)

```
## Merge 

* 'Rbind' is a base call, meaning no packages are required, you load R, you got it!

* *NOTE* rbind is dependent on all columns being the same, we made a diligent effor in our Cleanup files so that these are exact replications, just with different data!

```{r merge and output}

?rbind # 

Sonde_master <- rbind(Sonde_2023, Sonde_2024)


write.csv(Sonde_master, "output/Sonde_master.csv")
```
