---
title: "Juvenile Growth"
author: 
date: "6/20/2024"
output: html_document

description: 
---
Last updated 07/18/24 by K. Lenderman
  - Commented for more details
  - Note: Check lines 59-99 as R does not recognize "Month", needs to be created
 
 -Colors that can be used in ggplot https://sape.inf.usi.ch/quick-reference/ggplot2/colour

```{r setup, include=FALSE}
#make sure that your path is not commented (#) out and all others are
#this shows the path that R will take to find the data within your files on your computer

knitr::opts_chunk$set(echo = TRUE) 
#knitr::opts_knit$set(root.dir = 'C:/Users/kennedy.mcgrath/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kennedy's
#knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
#knitr::opts_knit$set(root.dir = 'C:/Users/kelly.roper/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kelly's
#knitr::opts_knit$set(root.dir = 'C:/Users/katherine.mcfarland/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Katie's
```


```{r,echo = FALSE}
#this code loads all packages that the code will need
#make sure all packages are installed before running this code
library("ggplot2")
library("readxl")
library("plyr")                                     
library("dplyr")
library("Rmisc")
library("readr")  
library("lubridate")
library("purrr")
library("tidyr")
```

### This code chunk merges all .csv files within the Tissue processing folder into one data fram and outputs the full dataset into a .csv master file. This allows us to download the raw data as a .csv, add it to the repository folder, and create the master data file without copying and pasting data in excel.
# reading in .csv files from local folder
```{r}
#Collecting and merging all raw data
data_all <- list.files(path = "Side_projects/Juvenile_growth/raw_data",  #path in files
                       pattern = "*.csv" #calling all csv files
                       , full.names = TRUE)%>% lapply(read_csv) %>% bind_rows() #combines all raw data from the path/folder into one tibble
data_all

as.data.frame(data_all)  # Convert tibble to data.frame. This helps when working with raw date

data_all <- data_all %>% filter(!is.na(Date))  #filtering NAs only in column "Date"

write.csv(data_all, "Master_files\\juv_growth_all_data.csv", row.names=FALSE)  #creating/printing csv file of all raw data merged together
```
#This code chunk with specify to R the order in which you want month presented. When not using a data and grouping by month, the default is to put in alphabetical order, this chuck will correct that. 
#Chuck does not work, R does not recognize "Month"
```{r}
neworder <- c("June","July")
data_all <- arrange(transform(data_all,
             Month=factor(Month,levels=neworder)),Month)
```


```{r}
# Summary of all data

st_height <- summarySE(data_all%>% filter(!is.na(Shell_Height)), measurevar="Shell_Height", groupvars=c("Site", "Month"))

st_height 


```

```{r}
ggplot(data=data_all, aes(x=Site, y=Shell_Height, fill=Site)) +
  geom_boxplot()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Mean Shell Height ", x ="Site", y = "Mean Shell Height (mm)") +
  facet_wrap(~Month)
```
Based on the graph above, it looks like we have greater shell growth at FENCE, so 


```{r}

```


```{r}
ggplot(data=data_all, aes(x=Shell_Height)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Juvenile Shell Height", x ="Height (mm)")+ scale_x_continuous(limits= c(0,80), breaks = seq(0,80, by =5) )+
  scale_y_continuous(limits = c(0,70), breaks = seq(0,70, by = 5))+
 facet_wrap(~ Site + Month, scales = "free", ncol = 1)
# add date to facet wrap after July collection
```


# Read in a summary file for counts and growth rate. Normally we would build code that does this for us, but to ensure you have plots to work with for your presenations, we will use this work around. 

```{r}
df<-read.csv("Side_projects/Juvenile_growth/summary_count_data.csv", header = T) #calling out path to read file
#$Survival=as.numeric(df$Survival)
```
```{r}
df2 <- df%>%na.omit(Survival) #removing rows within data frame that have NAs in Survival column
df2

survival_sum <- summarySE(df2, "Survival", groupvars=c("Site")) #creating stats (sd, se, ci) about data
survival_sum
```

```{r}
#This chunk is creating a ggplot of the data
prop.survived <- ggplot(data=survival_sum, aes(x=Site, y=Survival, fill=Site))+ #describe what data frame to use and the what rows should be on the x and y axis. Fill is the data that color codes the individual bars
geom_col(color = "black", linewidth =  0.75) + #codes the outline of the bars
geom_bar(stat="identity")+ #defines the type of graph to be bar
geom_errorbar(aes(ymin=Survival-se, ymax=Survival+se), width=.2, position=position_dodge(.9))+ #adds error bars previously calculated
theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ #removing grid lines
scale_fill_manual(values = c("orange1", "cornflowerblue") )+ #filling bars with specific colors
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ #can adjust angle of axis text
labs(x ="Site", y = "Propotion Survived") +
#facet_wrap(~Date)+ # could add a facet_wrap for date but would need to add to data frame first
theme(axis.title = element_text(size = rel(1.7)), axis.text = element_text(size = rel(1.3)), plot.margin = margin(10, 150, 10, 150), legend.text = element_text(size = 13), legend.title = element_text(size = 19))+
#changes axis and legend text and title, also plot.margin removes the white space within the graph
  ylim(0,1) #restrcting y axis limits from 0 to 1
prop.survived
```
```{r}
pdf(paste0(path = "Side_projects/Juvenile_growth/outputs/" ,"NEWprop_survived2024.pdf"), height = 7, width = 11) #printing a PDF within the path of the code, with specific dimensions of PDF
print(prop.survived) #specify the graph
dev.off()
```

#Look at previous graph's code for a description of each line when creating a ggplot graph
```{r}
growth.rate <- ggplot(data=df, aes(x=Site, y=GR_mergedT0, fill=Site)) +
  geom_boxplot(width = 2)+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+scale_fill_manual(values = c("orange1", "cornflowerblue") )+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(x ="Site", y = "Growth Rate (mm / month)") +
# could add a facet_wrap for date
  theme(axis.title = element_text(size = rel(1.7)), axis.text = element_text(size = rel(1.3)), plot.margin = margin(10, 150, 10, 150))+
  ylim(0,16)
  

growth.rate
```

# use to save indivdual graphs as a pdf in the outputs folder. must make graph an object first
```{r}
pdf(paste0(path = "Side_projects/Juvenile_growth/outputs/" ,"NEWgrowthrate2024.pdf"), height = 7, width = 11)
print(growth.rate)
dev.off()
```


Testing assumptions for statistical analysis (Survival and Growth rate)

  #### Code not working - resume edits here (km, 7/14/2024).
```{r}
library(rstatix)

leveneTest(Survival ~ Site, data=df)
shapiro.test(df$Survival)

leveneTest(Growth_rate ~ Site, data=df
shapiro.test(df$Growth_rate)
```


```{r}
sessionInfo()
```


