---
title: "Juvenile Growth"
author: Kyra Lenderman + Mariah Kachmar
date: "6/20/2024"
output: html_document

description: This code is for the Juvenille Growth Study looking at growth rates and survival of ~1 year old spat produced from the natural oyster bed at Ash Creek. The spat were divided into replicates of 3 spat bags with 100 individuals per bag and placed at Ash Creek, Fairfield CT and Fence Creek, Madison CT. The goal is to compare growth and survival at each site and determine if and what environmental factors may influence the population. 

Important Notes: Fence Creek 06/10/24 measurements for height after individual 50 were deleted/lost due to tablet glitch. Total counts should be based on the survival metric taken to determine live counts. 

---
Last updated 10/9/24 by M.Kachmar
  -incorporated Kaplan Meier survival statistics and curves

  
 

```{r setup, include=FALSE}
#make sure that your path is not commented (#) out and all others are
#this shows the path that R will take to find the data within your files on your computer

knitr::opts_chunk$set(echo = TRUE) 
#knitr::opts_knit$set(root.dir = 'C:/Users/kennedy.mcgrath/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kennedy's
#knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
#knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
#knitr::opts_knit$set(root.dir = 'C:/Users/kelly.roper/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kelly's
knitr::opts_knit$set(root.dir = 'C:/Users/katherine.mcfarland/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Katie's
```


```{r,echo = FALSE}
#this code loads all packages that the code will need
#make sure all packages are installed before running this code
library("ggplot2")
library("ggpubr")
library("readxl")
library("plyr")                                     
library("dplyr")
library("Rmisc")
library("readr")  
library("lubridate")
library("purrr")
library("tidyr")
library("survminer")
library("survival")
library("ggpubr")
```

### This code chunk merges all .csv files within the Tissue processing folder into one data fram and outputs the full dataset into a .csv master file. This allows us to download the raw data as a .csv, add it to the repository folder, and create the master data file without copying and pasting data in excel.
# reading in .csv files from local folder
```{r}
#Collecting and merging all raw data

file_paths <- list.files(path = "Side_projects/Juvenile_growth/raw_data",
                          pattern = "*.csv", full.names = TRUE)


data_all <- lapply(file_paths, function(file_path) {
  read_csv(file_path) %>%
    mutate(
      Date = as.Date(Date,format = "%m/%d/%Y"))
}) %>%
  bind_rows

as.data.frame(data_all)  # Convert tibble to data.frame

View(data_all)

data_all <- data_all %>% filter(!is.na(Date))  #filtering NAs only in column "Date"

data_all <- data_all %>% select(where(~ !all(is.na(.)))) #removing excess columns with NA

#View(data_all)

write.csv(data_all, "Master_files\\juv_growth_all_data.csv", row.names=FALSE)  #creating/printing csv file of all raw data merged together
```

#This code chunk with specify to R the order in which you want month presented. When not using a data and grouping by month, the default is to put in alphabetical order, this chuck will correct that. 

#This code chunk is not working. it is reading the format as dd/mm/yy instead of mm/dd/yy and giving a month associated with the date. 
```{r}
#The dates in the data files are reading as a character "chr" so we need to change them to date format

data_all <- data_all %>% dplyr::mutate(Month = month(Date,label = TRUE, abbr = FALSE))



#changing numeric month to month name
#data_all$Month <- factor(data_all$Month, levels = c("1","2","3","4","5","6","7", "8", "9", "10", "11", "12"),
    #    labels=c("Jan","Feb", "March","April","May", "June", "July", "Aug", "Sept", "Oct", "Nov", "Dec"))

#data_all

```


```{r}
# Summary of all height data

st_height <- summarySE(data_all%>% filter(!is.na(Shell_length)), measurevar="Shell_length", groupvars=c("Site", "Date", "Month"))

st_height 


#Summary of all height data per bag

st_height_bag <- summarySE(data_all%>% filter(!is.na(Shell_length)), measurevar="Shell_length", groupvars=c("Site", "Date", "Bag_number", "Month"))

st_height_bag 
```
#Let's take a look at the data - Shell length! 
```{r}

st_height$Site< - as.factor(st_height$Site) 
str(st_height)

ggplot(data=st_height, aes(x=Month, y=Shell_length, fill=Site)) +
                 geom_point()
```

```{r}
#Average shell height per month per site
  ### Why is the color and the lin plot not working????)

ggplot(data=st_height, aes(x=Month, y=Shell_length, fill=Site)) +
                 geom_point()+geom_line()+
        geom_errorbar(aes(ymin=Shell_length-se, ymax=Shell_length+se), width=.2,
          position=position_dodge(0)) +  
  # scale_color_manual(values=c("green4", "darkorange1"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs( x ="Month", y = "Mean Shell Height (mm)") 
```

```{r}
#Average shell height per month per site

ggplot(data=data_all, aes(x=Site, y=Shell_length, fill=Site)) +
  geom_boxplot()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Mean Shell Height ", x ="Site", y = "Mean Shell Height (mm)") +
  facet_wrap(~Month, ncol = 4)
```
```{r}
#Average shell height per month per site

ggplot(data=data_all, aes(x=Month, y=Shell_length, fill=Site)) +
  geom_boxplot()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Mean Shell Height ", x ="Site", y = "Mean Shell Height (mm)")
```

```{r}
# size class distribution graph per site per month

ASHC<- data_all %>% filter(Site == "ASHC")
FENC<- data_all %>% filter(Site == "FENC")

ggplot(data=ASHC, aes(x=Shell_length)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Juvenile Shell Height - Ash Creek", x ="Height (mm)")+ scale_x_continuous(limits= c(0,80), breaks = seq(0,80, by =5) )+
  scale_y_continuous(limits = c(0,70), breaks = seq(0,70, by = 5))+
 facet_wrap(~ Month, scales = "free", ncol = 1)
# add date to facet wrap after July collection

ggplot(data=FENC, aes(x=Shell_length)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Juvenile Shell Height - Fence Creek", x ="Height (mm)")+ scale_x_continuous(limits= c(0,80), breaks = seq(0,80, by =5) )+
  scale_y_continuous(limits = c(0,70), breaks = seq(0,70, by = 5))+
 facet_wrap(~ Month, scales = "free", ncol = 1)
```

#Mortality calculations
```{r}
#Lets great some summaries to see numbers and calculate the survival %
#Create a summary of counts across all bags
Survival_counts_all <- data_all %>% 
  dplyr::group_by(Site, Date, Survival) %>% 
  dplyr::summarise(count = n())
Survival_counts_all

#Create a summary of counts per bag
Survival_counts_bag <- data_all %>% 
  dplyr::group_by(Site, Date, Survival, Bag_number) %>% 
  dplyr::summarise(count = n())
Survival_counts_bag

#Survival summary
survival_sum_all <- summarySE(data_all, "Survival", groupvars=c("Site", "Date")) #creating stats (sd, se, ci) about data
survival_sum_all


```
#Proportions of survival - graphing survival summary
```{r}
#This chunk is creating a ggplot of the data
prop.survived <- ggplot(data=survival_sum_all, aes(x=Site, y=Survival, fill=Site))+ #describe what data frame to use and the what rows should be on the x and y axis. Fill is the data that color codes the individual bars
geom_col(color = "black", linewidth =  0.75) + #codes the outline of the bars
geom_bar(stat="identity")+ #defines the type of graph to be bar
geom_errorbar(aes(ymin=Survival-se, ymax=Survival+se), width=.2, position=position_dodge(.9))+ #adds error bars previously calculated
theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ #removing grid lines
scale_fill_manual(values = c("orange1", "cornflowerblue") )+ #filling bars with specific colors
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ #can adjust angle of axis text
labs(x ="Site", y = "Propotion Survived") +
#facet_wrap(~Date)+ # could add a facet_wrap for date but would need to add to data frame first
theme(axis.title = element_text(size = rel(1.7)), axis.text = element_text(size = rel(1.3)), plot.margin = margin(10, 150, 10, 150), legend.text = element_text(size = 13), legend.title = element_text(size = 19))+
#changes axis and legend text and title, also plot.margin removes the white space within the graph
  ylim(0,1) #restrcting y axis limits from 0 to 1
prop.survived


#output of graph
pdf(paste0(path = "Side_projects/Juvenile_growth/outputs/" ,"NEWprop_survived2024.pdf"), height = 7, width = 11) #printing a PDF within the path of the code, with specific dimensions of PDF
print(prop.survived) #specify the graph
dev.off()
```

#Calculating Growth Rate
#Reading this paper : Osei et al. 2022 - "monthly growth rate = (H2 − H1)/(t/30), where H1 is initial shell height (cm), H2 is final shell height (cm) and t is the number days between sampling" - how to tell R to do this?
#Is the correct? I am not sure - needs to be checked over and adjusted. I have it a whirl LOL - MK
```{r}

#Create summary of height per bag per time period per site

st_height_bag <- summarySE(data_all%>% filter(!is.na(Shell_length)), measurevar="Shell_length", groupvars=c("Site", "Date", "Bag_number", "Month"))

st_height_bag 

#So we need to calculate how many days between each measurement to calculate the growth rate
# Sort data by site and sampling date (important if dates are not ordered)
st_height_bag <- st_height_bag %>%
  arrange(Site, Date, Bag_number)

# Calculate the number of days between sampling dates and the monthly growth rate per site per replicate
st_height_bag <- st_height_bag %>%
  group_by(Site, Bag_number) %>%
  mutate(Days_between = c(NA, diff(Date)), H1 = lag(Shell_length), H2 = Shell_length, monthly_growth_rate = (H2-H1)/(Days_between))

st_height_bag



```

#graphing growth rate
#this needs to be fixed/updated
```{r}
growth.rate <- ggplot(data=survival_sum_all, aes(x=Site, y=GR_mergedT0, fill=Site)) +
  geom_boxplot(width = 2)+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+scale_fill_manual(values = c("orange1", "cornflowerblue") )+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(x ="Site", y = "Growth Rate (mm / month)") +
# could add a facet_wrap for date
  theme(axis.title = element_text(size = rel(1.7)), axis.text = element_text(size = rel(1.3)), plot.margin = margin(10, 150, 10, 150))+
  ylim(0,16)
  

growth.rate
```


#Kaplan Meier Survival Statistics
```{r}

#View(ASHC)
#View(FENC)

# Create a survival object per bag and plot 
ASHC$Survival <-as.numeric(ASHC$Survival) #need to make sure everything is in numeric format
ASHC$Month <-as.numeric(ASHC$Month)
FENC$Survival <-as.numeric(FENC$Survival) #need to make sure everything is in numeric format
FENC$Month <-as.numeric(FENC$Month)

# Ash Creek survival by bag

Surv_ASHC <- Surv(time = ASHC$Month, event = ASHC$Survival)
fit.surv_ASHC <- survfit(formula = Surv_ASHC ~ Bag_number, data = ASHC)

ASHC_survival_plot<-ggsurvplot(fit.surv_ASHC, data = ASHC, break.x.by = 1,
           linetype= c(1, 2, 3),xlab = "Month", ylab= "Survival", xlim = c(5,9), legend.labs= c("bag 1", "bag 2",
                                                                 "bag 3"),
           legend.title = "Replicate:", legend = "top", risk.table =FALSE )+ theme_survminer(base_size = 20,font.legend = c(15))+ggtitle("Ash Creek, CT")
ASHC_survival_plot

#output of graph
pdf(paste0(path = "Side_projects/Juvenile_growth/outputs/" ,"ASHC_Kaplan_Survival.pdf"), height = 7, width = 11) #printing a PDF within the path of the code, with specific dimensions of PDF
print(ASHC_survival_plot) #specify the graph
dev.off()



# Fence Creek survival
Surv_FENC <- Surv(time = FENC$Month, event = FENC$Survival)
fit.surv_FENC <- survfit(formula = Surv_FENC ~ Bag_number, data = FENC)

FENC_survival_plot<-ggsurvplot(fit.surv_FENC, data = FENC,break.x.by = 1,
           linetype= c(1, 2, 3),xlab = "Month", ylab= "Survival", xlim = c(5,9), legend.labs= c("bag 1", "bag 2",
                                                                 "bag 3"),
           legend.title = "Replicate:", legend = "top", risk.table =FALSE )+ theme_survminer(base_size = 20,font.legend = c(15))+ggtitle("Fence Creek, CT") 
FENC_survival_plot

#output of graph
pdf(paste0(path = "Side_projects/Juvenile_growth/outputs/" ,"FENC_Kaplan_Survival.pdf"), height = 7, width = 11) #printing a PDF within the path of the code, with specific dimensions of PDF
print(FENC_survival_plot) #specify the graph
dev.off()


#Survival comparing sites

data_all$Month<-as.numeric(data_all$Month)
data_all$Survival<-as.numeric(data_all$Survival)

Surv_CT <- Surv(time = data_all$Month, event = data_all$Survival)
fit.surv_CT <- survfit(formula = Surv_CT ~ Site, data = data_all)

CT_survival_plot<-ggsurvplot(fit.surv_CT, data = data_all, break.x.by = 1,
           linetype= c(1, 2),xlab = "Month", ylab= "Survival", xlim = c(5,9), legend.labs= c("Ash Creek", "Fence Creek"),
           legend.title = "Replicate:", legend = "top", risk.table =FALSE )+ theme_survminer(base_size = 20,font.legend = c(15))+ggtitle("Survival between Ash Creek, CT and Fence Creek, CT")
CT_survival_plot

#output of graph
pdf(paste0(path = "Side_projects/Juvenile_growth/outputs/" ,"JuvGrowth_Kaplan_Survival.pdf"), height = 7, width = 11) #printing a PDF within the path of the code, with specific dimensions of PDF
print(CT_survival_plot) #specify the graph
dev.off()


#Statistics
#Pairwise comparisons using long rank tests
#H: There is a significant difference in survival between sites
pc_site <- pairwise_survdiff(Surv(Month, Survival)~ Site, data = data_all)
pc_site

#Chi sq values
surv_diff_site<-survdiff(Surv(Month, Survival) ~ Site, data = data_all)
surv_diff_site

## Survival probability for all of sites & bags
summary(survfit(Surv(Month, Survival) ~ Site, data = data_all))
summary(survfit(Surv(Month, Survival) ~ Site + Bag_number, data = data_all))


#Cox proportional hazard
fit.coxph <- coxph(Surv_CT ~ Site, data = data_all)
fit.coxph
ggforest(fit.coxph, data = data_all, fontsize = 1.5)

```


#ALL OF THE CODE BELOW IS OLD CODE 


Testing assumptions for statistical analysis (Survival and Growth rate)

  #### Code not working - resume edits here (km, 7/14/2024).
```{r}
library(rstatix)

leveneTest(Survival ~ Site, data=df)
shapiro.test(df$Survival)

leveneTest(Growth_rate ~ Site, data=df
shapiro.test(df$Growth_rate)
```


```{r}
sessionInfo()
```


