---
title: "Juvenile Growth"
author: 
date: "6/20/2024"
output: html_document

description: This code is for the Juvenille Growth Study looking at growth rates and survival of ~1 year old spat produced from the natural oyster bed at Ash Creek. The spat were divided into replicates of 3 spat bags with 100 individuals per bag and placed at Ash Creek, Fairfield CT and Fence Creek, Madison CT. The goal is to compare growth and survival at each site and determine if and what environmental factors may influence the population. 

Important Notes: Fence Creek 06/10/24 measurements for height after individual 50 were deleted/lost due to tablet glitch. Total counts should be based on the survival metric taken to determine live counts. 

---
Last updated 08/7/24 by M.Kachmar
  - reorganized the files to now have monthly measurements that will be merged like how our other data is set up
  - started to redo code and reorganize to make sense for metrics that we want to run
  
 

```{r setup, include=FALSE}
#make sure that your path is not commented (#) out and all others are
#this shows the path that R will take to find the data within your files on your computer

knitr::opts_chunk$set(echo = TRUE) 
#knitr::opts_knit$set(root.dir = 'C:/Users/kennedy.mcgrath/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kennedy's
knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
#knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
#knitr::opts_knit$set(root.dir = 'C:/Users/kelly.roper/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kelly's
#knitr::opts_knit$set(root.dir = 'C:/Users/katherine.mcfarland/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Katie's
```


```{r,echo = FALSE}
#this code loads all packages that the code will need
#make sure all packages are installed before running this code
library("ggplot2")
library("readxl")
library("plyr")                                     
library("dplyr")
library("Rmisc")
library("readr")  
library("lubridate")
library("purrr")
library("tidyr")
library("survminer")
library("survival")
library("ggpubr")
```

### This code chunk merges all .csv files within the Tissue processing folder into one data fram and outputs the full dataset into a .csv master file. This allows us to download the raw data as a .csv, add it to the repository folder, and create the master data file without copying and pasting data in excel.
# reading in .csv files from local folder
```{r}
#Collecting and merging all raw data

file_paths <- list.files(path = "Side_projects/Juvenile_growth/raw_data",
                          pattern = "*.csv", full.names = TRUE)


data_all <- lapply(file_paths, function(file_path) {
  read_csv(file_path) %>%
    mutate(
      Date = as.Date(Date,format = "%m/%d/%Y"))
}) %>%
  bind_rows

as.data.frame(data_all)  # Convert tibble to data.frame


data_all <- data_all %>% filter(!is.na(Date))  #filtering NAs only in column "Date"

data_all <- data_all %>% select(where(~ !all(is.na(.)))) #removing excess columns with NA


write.csv(data_all, "Master_files\\juv_growth_all_data.csv", row.names=FALSE)  #creating/printing csv file of all raw data merged together
```

#This code chunk with specify to R the order in which you want month presented. When not using a data and grouping by month, the default is to put in alphabetical order, this chuck will correct that. 

#This code chunk is not working. it is reading the format as dd/mm/yy instead of mm/dd/yy and giving a month associated with the date. 
```{r}
#The dates in the data files are reading as a character "chr" so we need to change them to date format

data_all <- data_all %>% dplyr::mutate(Month = month(Date))



#changing numeric month to month name
#data_all$Month <- factor(data_all$Month, levels = c("1","2","3","4","5","6","7", "8", "9", "10", "11", "12"),
        labels=c("Jan","Feb", "March","April","May", "June", "July", "Aug", "Sept", "Oct", "Nov", "Dec"))

#data_all

```


```{r}
# Summary of all data

st_height <- summarySE(data_all%>% filter(!is.na(Shell_length)), measurevar="Shell_length", groupvars=c("Site", "Date"))

st_height 



```
#Let's take a look at the data - Shell length! 

```{r}
#Average shell height per month per site

ggplot(data=data_all, aes(x=Site, y=Shell_length, fill=Site)) +
  geom_boxplot()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Mean Shell Height ", x ="Site", y = "Mean Shell Height (mm)") +
  facet_wrap(~Month)
```

```{r}
# size class distribution graph per site per month

ggplot(data=data_all, aes(x=Shell_length)) +
  geom_histogram()+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Juvenile Shell Height", x ="Height (mm)")+ scale_x_continuous(limits= c(0,80), breaks = seq(0,80, by =5) )+
  scale_y_continuous(limits = c(0,70), breaks = seq(0,70, by = 5))+
 facet_wrap(~ Site + Month, scales = "free", ncol = 1)
# add date to facet wrap after July collection
```

#Survival calculations
```{r}
#Lets great some summaries to see numbers and calculate the survival %
#Create a summary of counts across all bags
Survival_counts_all <- data_all %>% 
  dplyr::group_by(Site, Date, Survival) %>% 
  dplyr::summarise(count = n())
Survival_counts_all

#Create a summary of counts per bag
Survival_counts_bag <- data_all %>% 
  dplyr::group_by(Site, Date, Survival, Bag_number) %>% 
  dplyr::summarise(count = n())
Survival_counts_bag

#Survival summary
survival_sum_all <- summarySE(data_all, "Survival", groupvars=c("Site", "Date")) #creating stats (sd, se, ci) about data
survival_sum_all


```
#Proportions of survival - graphing survival summary
```{r}
#This chunk is creating a ggplot of the data
prop.survived <- ggplot(data=survival_sum, aes(x=Site, y=Survival, fill=Site))+ #describe what data frame to use and the what rows should be on the x and y axis. Fill is the data that color codes the individual bars
geom_col(color = "black", linewidth =  0.75) + #codes the outline of the bars
geom_bar(stat="identity")+ #defines the type of graph to be bar
geom_errorbar(aes(ymin=Survival-se, ymax=Survival+se), width=.2, position=position_dodge(.9))+ #adds error bars previously calculated
theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ #removing grid lines
scale_fill_manual(values = c("orange1", "cornflowerblue") )+ #filling bars with specific colors
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ #can adjust angle of axis text
labs(x ="Site", y = "Propotion Survived") +
#facet_wrap(~Date)+ # could add a facet_wrap for date but would need to add to data frame first
theme(axis.title = element_text(size = rel(1.7)), axis.text = element_text(size = rel(1.3)), plot.margin = margin(10, 150, 10, 150), legend.text = element_text(size = 13), legend.title = element_text(size = 19))+
#changes axis and legend text and title, also plot.margin removes the white space within the graph
  ylim(0,1) #restrcting y axis limits from 0 to 1
prop.survived


#output of graph
pdf(paste0(path = "Side_projects/Juvenile_growth/outputs/" ,"NEWprop_survived2024.pdf"), height = 7, width = 11) #printing a PDF within the path of the code, with specific dimensions of PDF
print(prop.survived) #specify the graph
dev.off()
```

#Calculating Growth Rate
```{r}

```

#graphing growth rate
```{r}
growth.rate <- ggplot(data=survival_sum_all, aes(x=Site, y=GR_mergedT0, fill=Site)) +
  geom_boxplot(width = 2)+  #scale_fill_manual(values=c("forestgreen","orange", "purple"))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+scale_fill_manual(values = c("orange1", "cornflowerblue") )+
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(x ="Site", y = "Growth Rate (mm / month)") +
# could add a facet_wrap for date
  theme(axis.title = element_text(size = rel(1.7)), axis.text = element_text(size = rel(1.3)), plot.margin = margin(10, 150, 10, 150))+
  ylim(0,16)
  

growth.rate
```


#Kaplan Meier Survival 
#This needs some work - the counts are not correct
```{r}

# Create a survival object per bag and plot 
data_all$survival <-as.numeric(data_all$Survival) #need to make sure everything is in numeric format
data_all$Month <-as.numeric(data_all$Month)

Surv1 <- Surv(time = data_all$Month, event = data_all$Survival)
fit.surv1 <- survfit(formula = Surv1 ~ Bag_number, data = data_all)

Survival_plot<-ggsurvplot(fit.surv1, data = data_all, break.x.by = 1,
           linetype= c(1, 2, 3),xlab = NULL, ylab= NULL, xlim = c(5,7), legend.labs= c("bag 1", "bag 2",
                                                                 "bag 3"),
           legend.title = "Replicate:", legend = "top", risk.table =TRUE )+ theme_survminer(base_size = 20,font.legend = c(15))
Survival_plot
plot + labs(title= "Eastern Oyster FRA")


```


#ALL OF THE CODE BELOW IS OLD CODE 


Testing assumptions for statistical analysis (Survival and Growth rate)

  #### Code not working - resume edits here (km, 7/14/2024).
```{r}
library(rstatix)

leveneTest(Survival ~ Site, data=df)
shapiro.test(df$Survival)

leveneTest(Growth_rate ~ Site, data=df
shapiro.test(df$Growth_rate)
```


```{r}
sessionInfo()
```


