---
title: "Juvenile Growth"
author: 
date: "6/20/2024"
output: html_document

description: 
---
Last updated 06/20/24 by K. Lenderman
  - Created script
  - Note: Check Kennedy's path


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = 'C:/Users/kennedy.mcgrath/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kennedy's
#knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
#knitr::opts_knit$set(root.dir = 'C:/Users/kelly.roper/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kelly's
```


```{r,echo = FALSE}
library("ggplot2")
library("readxl")
library("plyr")                                     
library("dplyr")
library("Rmisc")
library("readr")  
library("lubridate")
library("purrr")
library("tidyr")
```

### This code chunk merges all .csv files within the Tissue processing folder into one data fram and outputs the full dataset into a .csv master file. This allows us to download the raw data as a .csv, add it to the repository folder, and create the master data file without copying and pasting data in excel.
# reading in .csv files from local folder
```{r}
#Collecting and merging all raw data
data_all <- list.files(path = "Side_projects/Juvenile_growth/raw_data",  #need to have file with data in "raw_data"
                          pattern = "*.csv", full.names = TRUE) #only looking at csv files located in raw_data file
                          %>%
                          lapply(read_csv) %>%
                          bind_rows()
data_all

as.data.frame(data_all)  # Convert tibble to data.frame

data_all <- data_all %>% filter(!is.na(lab_id))  #filtering NAs

write.csv(data_all, "Master_files\\juv_growth_all_data.csv", row.names=FALSE)  #creating/printing csv file of all raw data merged together
```

```{r}
# Summary of all data

st_height <- summarySE(data_all%>% filter(!is.na(height_mm)), measurevar="", groupvars=c("", ""))

st_height 
```

```{r}
sessionInfo()
```


