---
title: "Recruitment"
author: "Katie McFarland"
date: "11/17/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r cars, echo=FALSE}
library("Rmisc")
library("ggplot2")
library(tidyr)
library("dplyr")
library(plyr)
```

#path for Mariah
```{r}
#Set Path
setwd("C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Recruitment")
```

# Path for others - comment out 
```{r}
setwd("C:/Users/katherine.mcfarland/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Recruitment")

data_all <- list.files(path = "C:/Users/katherine.mcfarland/Documents/GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Recruitment/RawData",                  # Identify all CSV files
  pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>%                              # Store all files in list
  bind_rows                                         # Combine data sets into one data set 
data_all                                            # Print data to RStudio console

as.data.frame(data_all)  
```


### This code chunk merges all .csv files within the Tissue processing folder into one data frame and outputs the full dataset into a .csv master file. This allows us to download the raw data as a .csv, add it to the repository folder, and create the master data file without copying and pasting data in excel.
# reading in .csv files from local folder
```{r}
data_all <- list.files(path = "C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance/Field_Data_Recruitment/RawData",                           # Identify all CSV files
  pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>%                              # Store all files in list
  bind_rows                                         # Combine data sets into one data set 
data_all                                            # Print data to RStudio console

as.data.frame(data_all)                            # Convert tibble to data.frame
```



```{r}

```











```{r}
sessionInfo()
```

