---
title: "RFTM"
author: "Katie McFarland"
date: "6/29/2023"
output: html_document

description: This R code is used to import and summarize RFTM (Rays Fluid Thioglycollate Medium) intensity scoring from the LISS Oyster Health Project's monthly sampling at Ash Creek and Fence Creek intertidal sites in Connecticut and Goldstar beach and Laurel Hollow subtidal sites on Long Island, NY. The scale used to score intensity for individuals is the Mackins Scale (citation). This score can be used to calculate prevalence, weighted prevalence and intensity across the population. 
---

Last updated 4/15/24 by M. Kachmar
  - CT April uploaded & QAQC complete
  - Accuracy %77.25




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
#knitr::opts_knit$set(root.dir = 'C:/Users/kelly.roper/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kelly's
```

```{r}
library("dplyr")                                    
library("plyr")                                     
library("readr")             
library("Rmisc")
library("ggplot2")
library("lubridate")
```

### This code chunk merges all .csv files within the Tissue processing folder into one data fram and outputs the full dataset into a .csv master file. This allows us to download the raw data as a .csv, add it to the repository folder, and create the master data file without copying and pasting data in excel.
# reading in .csv files from local folder
```{r}
data_all <- list.files(path = "Lab_Data_RFTM/raw_data/Files_by_Month",                           # Identify all CSV files
  pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>%                              # Store all files in list
  bind_rows                                         # Combine data sets into one data set 
data_all                                            # Print data to RStudio console

as.data.frame(data_all)                            # Convert tibble to data.frame

tail(data_all)

data_all <- data_all %>% filter(!is.na(lab_id))

write.csv(data_all, "Master_files\\RFTM_all_data.csv", row.names=FALSE)
```


## adding a month and year column to the data

```{r}
#month
data_all <- data_all %>%
  mutate(date_collected= as.Date(date_collected), month = month(date_collected))

#year
data_all <- data_all %>%
  mutate(date_collected= as.Date(date_collected), year = year(date_collected))

data_all
```

#Filtering NAs 
```{r}
data_all <- data_all %>% filter(!is.na(date_collected))
data_all

```

#This chunk of code is removing 0723LAUR_20 and 0723LAUR_26 from the datasheet as they have been identified as spat on shell to avoid bias in the data. During this sample collection there were animals that were significantly smaller than the single set oysters. 
```{r}
data_all <- data_all %>%
  subset(lab_id != "0723LAUR_20") %>%
  subset(lab_id != "0723LAUR_26")



```

# Summary of all data and Completeness Check
```{r}
st_rftm_final <- summarySE(data_all, measurevar="rftm_final", groupvars=c("site", "date_collected"))
st_rftm_final

#Calculate completeness for QC
st_rftm_final$Completeness <- st_rftm_final$N /30

st_rftm_final

write.csv(st_rftm_final, "Lab_Data_RFTM\\output\\Completeness_RFTM_intensity_data.csv", row.names=FALSE)
```

# Comparied reader 1 and reader 2

```{r}
data_all$results = ifelse(data_all$rftm_intensity_read1 < data_all$rftm_intensity_read2, 'FALSE',
  ifelse(data_all$rftm_intensity_read1 > data_all$rftm_intensity_read2, 'FALSE',
  ifelse(data_all$rftm_intensity_read1 == data_all$rftm_intensity_read2, 'TRUE', NA)))
  
data_all
```



```{r}
Data_Accuracy = data.frame(data_all$lab_id,data_all$date_collected, data_all$site, data_all$rftm_intensity_read1, data_all$rftm_intensity_read2, data_all$results)

Data_Accuracy <- na.omit(Data_Accuracy)
Data_Accuracy
```

# Accuracy Output
```{r}
#count TRUE values in vector
x <- Data_Accuracy %>% 
  dplyr::group_by(data_all.site, data_all.date_collected, data_all.results) %>% 
  dplyr::summarise(count = n())
x2 <- x %>% 
  dplyr::group_by()
x
T <- nrow(Data_Accuracy %>% filter(data_all.results == 'TRUE'))
F <- nrow(Data_Accuracy %>% filter(data_all.results == 'FALSE'))

Accuracy <- T/(T+F)
Accuracy

#write.csv(Data_Accuracy, "C:/Users/katherine.mcfarland/Documents/4. GitHub/EAD-ASEB_EPA_LISS_Disease_Surveillance/Lab_Data_RFTM\\Accuracy_RFTM_intenisty_data.csv", row.names=FALSE)
```

#Graphing Weighted prevalence(= Sum of individual intensity scores / total number of oyster sampled)

```{r, echo=FALSE}
ggplot(data=data_all, aes(x=month, y=rftm_final, fill=site)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted prevalence of Dermo infection", x ="Date", y = "Weighted prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
  facet_wrap(~site + year)

```

```{r}
#Graphing mean weighted prevalence over time
df_wp_summary <- data_all %>%
  dplyr::group_by(site, month, year, date_collected) %>% 
  dplyr::summarize( Weighted_prevalence = mean(rftm_final))
df_wp_summary

ggplot(data=df_wp_summary, aes(x=month, y=Weighted_prevalence, color=site)) +
  geom_point()+  
  geom_line(aes(group = site))+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted Prevalence of Dermo infection", x ="Month", y = "Weighted Prevalence Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12)) + facet_wrap(~ year, scales = "free", ncol=1)

```

# Prevalence calculations for all sites
# Prevalence = # infected/ total # sampled
```{r}
## Prevalence T/F

data_all<-data_all%>% filter(!is.na(rftm_final))
data_all

data_all$prevalent = ifelse(data_all$rftm_final == 0, '0',
  ifelse(data_all$rftm_final > 0, '1', NA))
  
data_all

# YEARLY PREVALENCE %
present <- nrow(data_all %>% filter(prevalent == '1'))
absent <- nrow(data_all %>% filter(prevalent == '0'))

prevalence_all <- present/(present+absent)
prevalence_all
# 67.9%

str(data_all$prevalent)
data_all$prevalent <- as.numeric(data_all$prevalent)

df_prevalence_summary <- data_all %>%
  dplyr::group_by(site, month, year) %>% 
  dplyr::summarize( prevalence_precentage= mean(prevalent)* 100)
df_prevalence_summary

```
#Graphing mean prevalence 
```{r}

ggplot(data=df_prevalence_summary, aes(x=month, y=prevalence_precentage, color=site)) +
  geom_point()+  
  geom_line(aes(group = site))+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence of Dermo infection", x ="Month", y = "Dermo Prevaence %")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12)) + facet_wrap(~ year, scales = "free", ncol=1)
```
```{r}

ggplot(data=df_prevalence_summary, aes(x=site, y=prevalence_precentage, fill = site)) +
 geom_boxplot()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence of Dermo infection", x ="Site", y = "Dermo Prevaence %")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)
```

# Intensity all sites (Sum of intensity scores/# of infected oysters)
# intensity calculation for august gold star needs to be fixed. 
```{r}
data_all

data_all$rftm_final<-as.numeric(as.character(data_all$rftm_final))

df_intensity_summary <- data_all %>%
  dplyr::group_by(site, month, year) %>% 
  dplyr::summarize( intensity = sum(rftm_final, na.rm= TRUE)/sum(prevalent, na.rm = TRUE))
df_intensity_summary

# Need to fix 0823GOLD? Looked at the raw data sheet and the scores were all 0. 
```
```{r}

ggplot(data=df_intensity_summary, aes(x=month, y=intensity, color=site)) +
  geom_point()+  
  geom_line(aes(group = site))+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Intensity of Dermo infection", x ="Month", y = "Intensity score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12)) + scale_y_continuous(limits = c(0, 3))+ facet_wrap(~ year, scales = "free", ncol=1)

```
```{r}

## Stacked bar graph showing proportions per month of intensity scores

## Not letting be add a 5 category - need to figure out why
## Also gold star is missing data? 


df_intensity_proportions<- data_all %>%
  mutate(rftm_final_numeric = as.factor(rftm_final),intensity_bin = case_when(rftm_final == 0 ~ "0", rftm_final == 0.5 ~"0.5",rftm_final == 1 ~ "1", rftm_final == 2 ~"2",rftm_final == 3 ~ "3", rftm_final == 4 ~"4",rftm_final == 5 ~ "5", TRUE ~ as.character(rftm_final))) %>%
  group_by(site, month,year, intensity_bin) %>%
  dplyr::summarise(Count= n()) %>%
  ungroup() %>%
  dplyr::mutate(Proportion = Count/sum(Count))

df_intensity_proportions<- na.omit(df_intensity_proportions)

df_intensity_proportions

ggplot(data=df_intensity_proportions, aes(x=month, y= Proportion, fill=intensity_bin)) +
  geom_bar(width = .5, stat="identity", position = "fill",colour = "black")+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(fill ="Dermo Intensity")+
  labs(title="Proportion of Intensity scores of Dermo infection", x ="month", y = "Proportion")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
scale_fill_brewer(palette = "YlOrBr")+
   scale_x_continuous("Month", breaks = c(3,4,5,6,7,8,9,10))+ 
  facet_wrap(~ year ~site)

```

# Ash Creek Summary
```{r}
df_ASHC <- data_all%>%
  filter(site=="ASHC")
df_ASHC 

#Weighted prevalence 
st_intensity_ASHC <- summarySE(df_ASHC, measurevar="rftm_final", groupvars=c("month", "year"))
st_intensity_ASHC

#Prevalence
df_ASHC_prevalence <- df_prevalence_summary %>% 
  filter(site == "ASHC")
df_ASHC_prevalence

#Intensity Index
df_ASHC_intensity <- df_intensity_summary %>%
  filter(site == "ASHC")
df_ASHC_intensity


```


```{r, echo=FALSE}
#Graphing weighted prevalence ASHC

ggplot(data=df_ASHC, aes(x=month, y=rftm_final, group= month)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Ash Creek Weighted Prevalence Dermo infection", x ="Month", y = "Weighted Prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)


#Weighted prevalence
ggplot(data=st_intensity_ASHC, aes(x=month, y=rftm_final)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted Prevalence of Dermo infection", x ="Month", y = "Weighted Prevalence Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)

##Prevalence
ggplot(data=df_ASHC_prevalence, aes(x=month, y=prevalence_precentage)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence", x ="Month", y = "Prevalence precent")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)+ facet_wrap(~ year, scales = "free", ncol=1)

#Intensity index
ggplot(data=df_ASHC_intensity, aes(x=month, y=intensity)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Ash Creek Intensity Index", x ="Month", y = "Intensity Index")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)
```



# Fence Creek Summary
```{r}
df_FENC <- data_all%>%
  filter(site=="FENC")
df_FENC 

#Weighted prevalence

st_intensity_FENC <- summarySE(df_FENC, measurevar="rftm_final", groupvars=c("month", "year"))
st_intensity_FENC

#Prevalence
df_FENC_prevalence <- df_prevalence_summary %>% 
  filter(site == "FENC")
df_FENC_prevalence

#Intensity Index
df_FENC_intensity <- df_intensity_summary %>%
  filter(site == "FENC")
df_FENC_intensity

```

```{r, echo=FALSE}
#Graphing weighted prevalence FENC

ggplot(data=df_FENC, aes(x=date_collected, y=rftm_final, group= date_collected)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Fence Creek Weighted prevalence Dermo infection", x ="Date", y = "Weighted prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)


#Weighted prevalence
ggplot(data=st_intensity_FENC, aes(x=month, y=rftm_final)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted Prevalence of Dermo infection", x ="Month", y = "Weighted Prevalence Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)

##Prevalence
ggplot(data=df_FENC_prevalence, aes(x=month, y=prevalence_precentage)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence", x ="Month", y = "Prevalence precent")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)

#Intensity index
ggplot(data=df_FENC_intensity, aes(x=month, y=intensity)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Fence Creek Intensity Index", x ="Month", y = "Intensity Index")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)

```
# Laurel Hollow summary
```{r}
df_LAUR <- data_all%>%
  filter(site=="LAUR")
df_LAUR 

#weighted prevalence
st_intensity_LAUR <- summarySE(df_LAUR, measurevar="rftm_final", groupvars=c("date_collected"))
st_intensity_LAUR

```

```{r, echo=FALSE}

#Graphing weighted prevalence LAUR

ggplot(data=df_LAUR, aes(x=date_collected, y=rftm_final, group= date_collected)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Laurel Hollow Weighted prevalence of Dermo infection", x ="Date", y = "Weighted Prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))

```

# Gold Star summary
```{r}
df_GOLD <- data_all%>%
  filter(site=="GOLD")
df_GOLD 

df_GOLD <- df_GOLD %>% filter(!is.na(rftm_final))

#Weighted prevalence
st_intensity_GOLD <- summarySE(df_GOLD, measurevar="rftm_final", groupvars=c("month", "year"))
st_intensity_GOLD

#Prevalence
df_GOLD_prevalence <- df_prevalence_summary %>% 
  filter(site == "GOLD")
df_GOLD_prevalence

#Intensity Index
df_GOLD_intensity <- df_intensity_summary %>%
  filter(site == "GOLD")
df_GOLD_intensity


df_GOLD_proportions<-df_intensity_proportions %>%
  filter(site =="GOLD")

df_GOLD_proportions
```

```{r, echo=FALSE}

#Graphing weighted prevalence GOLD

ggplot(data=df_GOLD, aes(x=month, y=rftm_final, group= date_collected)) +
  geom_boxplot()+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Gold Star Beach Weighted prevalence of Dermo infection", x ="Date", y = "Weighted Prevalence")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)

#Weighted prevalence
ggplot(data=st_intensity_GOLD, aes(x=month, y=rftm_final)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Weighted Prevalence of Dermo infection", x ="Month", y = "Weighted Prevalence Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)

##Prevalence
ggplot(data=df_GOLD_prevalence, aes(x=month, y=prevalence_precentage)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Prevalence", x ="Month", y = "Prevalence precent")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)

#Intensity index
ggplot(data=df_GOLD_intensity, aes(x=month, y=intensity)) +
  geom_point()+  
  geom_line()+
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Goldstar Beach Intensity Index", x ="Month", y = "Intensity Index")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+ facet_wrap(~ year, scales = "free", ncol=1)

#Proportions

ggplot(data=df_GOLD_proportions, aes(x=month, y= Proportion, fill=intensity_bin)) +
  geom_bar(width = .5, stat="identity", position = "fill", colour = "black")+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))+
  labs(title="Proportion of Intensity scores of Dermo infection", x ="month", y = "Proportion", fill = "Intensity Score")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+
   scale_fill_brewer() +
   scale_x_continuous( breaks = seq(5,12, by =1) )
#+facet_wrap(~ site)

```

```{r}
#Comparing body condition scores to rftm scores

#pulling in body condition score data
file_paths <- list.files(path = "Lab_Data_TissueProcessing/raw_data/Files_by_Month",
                          pattern = "*.csv", full.names = TRUE)


data_cond <- lapply(file_paths, function(file_path) {
  read_csv(file_path) %>%
    mutate(
      date_collected = as.Date(date_collected,format = "%m/%d/%Y"),
      date_processed = as.Date(date_processed,format = "%m/%d/%Y"),
      date_davidsons = as.Date(date_davidsons,format = "%m/%d/%Y"),
      date_etoh = as.Date(date_etoh,format = "%m/%d/%Y")
    )
}) %>%
  bind_rows
as.data.frame(data_cond)   

#removing unnecessary columns and NAs
data_cond <- select(data_cond,-lab_sample, -sample_notes, -dissection_notes, -light_regime, -oyster_zone, -...21:-...33)
data_cond <- data_cond %>% filter(!is.na(date_collected))
data_cond <- data_cond %>%
  subset(lab_id != "0723LAUR_20") %>%
  subset(lab_id != "0723LAUR_26") %>%
  subset(lab_id != "1023GOLD_23")

#changing body condition score format
data_cond<- data_cond %>%
  mutate(condition_score = dplyr::recode(condition, 
                                     "1_very_good" = 1, "2_good" = 2, "3_good_minus"= 3, "4_fair_plus"= 4, "5_fair"= 5,"6_fair_minus"= 6, "7_poor_plus"=7,
                                     "8_poor"= 8, "9_very_poor"= 9))

#adding rftm final scores to tissue processing data (body condition score included)
data_rftm.cond <- data_cond %>%
  mutate(rftm_final = data_all$rftm_final)

#creating proportions of rftm scores compared to body condtion scores
data_rftm.cond_prop<- data_rftm.cond %>%
  mutate(rftm_final_numeric = as.numeric(rftm_final),rftm_score = case_when(rftm_final == 0 ~ "0", rftm_final == 0.5 ~"0.5",rftm_final == 1 ~ "1", rftm_final == 2 ~"2",rftm_final == 3 ~ "3", rftm_final == 4 ~"4",rftm_final == 5 ~ "5", TRUE ~ as.character(rftm_final))) %>%
  group_by(date_collected, condition_score, rftm_score, site) %>% dplyr:: summarise(Count= n()) %>%
  ungroup() %>%
  mutate(Proportion = Count/sum(Count))

#adding column to easily show month collected for graphs
data_rftm.cond_prop <- data_rftm.cond_prop %>% dplyr::mutate(date_collected= as.Date(date_collected), month = month(date_collected))

data_rftm.cond_prop$date_collected <- factor(data_rftm.cond_prop$month, levels = c("3", "4","5","6","7", "8", "9", "10", "11"),
        labels=c("March", "April", "May", "June", "July", "Aug", "Sept", "Oct", "Nov"))

#removing month with NA body condition scores
data_rftm.cond_prop <- data_rftm.cond_prop %>% filter(!is.na(condition_score))


```

```{r}
#plotting the proportion of rftm scores to body condition (all sites, all months)
ggplot(data_rftm.cond_prop, aes(x=condition_score, y=Proportion, fill=rftm_score))+
  geom_bar(width = .8, stat="identity", position = "fill",colour = "black")+
  theme(axis.text.x = element_text(angle = 15, vjust = 1, hjust=1, size = 8), plot.title = element_text(size = 10), axis.text.y = element_text(size = 9))+
  labs(title="Proportion of RFTM scores within Body Condition Scores by Date Collected", x ="condition score", y = "Proportion")+ theme(axis.title.y = element_text(size = rel(1), angle =90), axis.title.x = element_text(size = rel(1), angle = 0))+
  theme(axis.text=element_text(size=7))+
  theme(legend.title = element_text(size=10))+
  labs(fill="RFTM Intesity Score")+
 scale_fill_brewer(palette = "YlOrBr")+
  scale_y_continuous("Proportion", breaks = c(0.00,0.50,1.00))+
   scale_x_continuous("Body Condition Score", breaks = c(1,2,3,4,5,6,7,8,9))+
  facet_grid(~site ~date_collected)
```
```{r}
#removing month with NA body condition scores
data_rftm.cond <- data_rftm.cond %>% filter(!is.na(condition_score))

#making rftm scores a factor
data_rftm.cond$rftm_final <- as.factor(data_rftm.cond$rftm_final)

#adding column to easily show month collected for graphs
data_rftm.cond <- data_rftm.cond %>% dplyr::mutate(date_collected= as.Date(date_collected), month = month(date_collected))

data_rftm.cond$date_collected <- factor(data_rftm.cond$month, levels = c("4","5","6","7", "8", "9", "10", "11"),
        labels=c("April", "May", "June", "July", "Aug", "Sept", "Oct", "Nov"))

#graphing number of oysters with specific body condition scores and rftm scores (all site, all months)
ggplot(data_rftm.cond, aes(x=condition_score, fill=rftm_final))+
  geom_histogram(binwidth = .5)+
  scale_fill_brewer(palette = "YlOrBr")+
   scale_x_continuous("Body Condition Score", breaks = c(1,2,3,4,5,6,7,8,9))+
  facet_grid(~site ~date_collected)
```

```{r}
#Coding graphs for LIS Confrence - only 2023 data
data_2023 <- data_all%>%  filter(!year=="2024")
data_2023 <- data_2023%>%  filter(!month=="4")

df_intensity_proportions<- data_2023 %>%
  mutate(intensity_bin = as.factor(rftm_final),rftm_score = case_when(rftm_final == 0 ~ "0", rftm_final == 0.5 ~"0.5",rftm_final == 1 ~ "1", rftm_final == 2 ~"2",rftm_final == 3 ~ "3", rftm_final == 4 ~"4",rftm_final == 5 ~ "5", TRUE ~ as.character(rftm_final))) %>%
  group_by(intensity_bin, site, month) %>% dplyr:: summarise(Count= n()) %>%
  ungroup() %>%
  mutate(Proportion = Count/sum(Count))

df_intensity_proportions<- na.omit(df_intensity_proportions)
df_intensity_proportions$month <- factor(df_intensity_proportions$month, levels = c("4","5","6","7", "8", "9", "10", "11"),
        labels=c("April","May", "June", "July", "Aug", "Sept", "Oct", "Nov"))
df_intensity_proportions$site <- factor(df_intensity_proportions$site, levels = c("ASHC","FENC","GOLD", "LAUR"),
        labels=c("Ash Creek", "Fence Creek", "Gold Star", "Laurel Hollow"))

ggplot(data=df_intensity_proportions, aes(x=month, y= Proportion, fill=intensity_bin)) +
  geom_bar(width = .5, stat="identity", position = "fill",colour = "black")+  
   theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = rel(.9)))+
  labs(fill ="Dermo Intensity")+
  labs(title="Prevelence of dermo in 2023", x ="Month", y = "Proportion of dermo intensity scores")+ theme(axis.title.y = element_text(size = rel(1.3), angle =90), axis.title.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.text=element_text(size=12))+scale_fill_brewer(palette = "YlOrBr")+
  facet_wrap(~ site)
```


```{r}
#Coding graphs for LIS Confrence - only 2023 data (continued)
#look at 3-5 scores rftm; look into bcs code

df_3_prop<- select(data_2023, -c("site"))

#Count and proportion table for 2023 rftm scores by month
rftm_table <- table(data_2023$rftm_final, data_2023$month)
names(dimnames(rftm_table)) <- c("RFTM Score", "Month")
rftm_table <- addmargins(rftm_table)

rftm_proportion_table <- prop.table(rftm_table)
rftm_proportion_table <- addmargins(rftm_proportion_table)
rftm_proportion_table


```

Version
```{r}
sessionInfo()
```

