---
title: "Recruitment"
author: "Katie McFarland & Mariah Kachmar"
date: "11/17/2023"
output: html_document

description: This R code is used to import and summarize recruitment data collected using shellstringers from the LISS Oyster Health Project at Ash Creek and Fence Creek intertidal sites in Connecticut and Goldstar beach and Laurel Hollow subtidal sites on Long Island, NY. 
---
#Last updated 12/4/2023 by M.Kachmar
#Accuracy of spat counting 0.75 - did not double read for all collections and we lost data due to shell stringers disappearing
#Would like to discuss this data - NAs frequent. Is this because stringers were not counted? I would like to add notes into the code explaining things like this. 
#Best way to report recruitment to stakeholders?



## R Markdown

```{r, echo=FALSE}
library("Rmisc")
library("ggplot2")
library("tidyverse")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/mariah.kachmar/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Mariah's
#knitr::opts_knit$set(root.dir = 'C:/Users/kyra.lenderman/Documents/Github/EAD-ASEB_EPA_LISS_Disease_Surveillance') #Kyra's
```
### This code chunk merges all .csv files within the Tissue processing folder into one data frame and outputs the full dataset into a .csv master file. This allows us to download the raw data as a .csv, add it to the repository folder, and create the master data file without copying and pasting data in excel.
# reading in .csv files from local folder
```{r}
data_all <- list.files(path = "Field_Data_Recruitment/raw_data",                           # Identify all CSV files
  pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>%                              # Store all files in list
  bind_rows                                         # Combine data sets into one data set 
data_all                                            # Print data to RStudio console


as.data.frame(data_all)                            # Convert tibble to data.frame

View(data_all)

data_all <- data_all %>% filter(!is.na(Count_1))

```





# Summary of all data 
```{r}
st_rec <- summarySE(data_all, measurevar="Count_1", groupvars=c("Site", "date_collected", "Replicate"))
st_rec 

#Calculate completeness for QC
st_rec$Completeness <- st_rec$N /24

st_rec

#write.csv(st_height, "Lab_Data_TissueProcessing/output\\Completeness_tissue_processing_data.csv", row.names=FALSE)
```

```{r}
Avg_spat_stringer <- summarySE(data_all, measurevar="Count_1", groupvars=c("Site", "date_collected"))
Avg_spat_stringer
```

```{r}
Avg_spat_stringer <- Avg_spat_stringer %>% dplyr::mutate(Year = year(date_collected))


#2023
spat_2023<- Avg_spat_stringer%>% filter(Year == 2023)
ggplot(data=spat_2023, aes( y=Count_1)) +
  geom_boxplot()+  
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Mean Recruitment 2023", x ="Site", y = "Mean Recruitment (spat/shell)")+
  facet_wrap(~Site)


#2024
spat_2024<- Avg_spat_stringer%>% filter(Year == 2024)
ggplot(data=spat_2024, aes( y=Count_1 )) +
  geom_boxplot()+  
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title="Mean Recruitment 2024", x ="Site", y = "Mean Recruitment (spat/shell)")+
  facet_wrap(~Site)

```


#Comparing counter 1 & counter 2

```{r}
data_all$results = ifelse(data_all$Count_1 < data_all$Count_2, 'FALSE',
  ifelse(data_all$Count_1 > data_all$Count_2, 'FALSE',
  ifelse(data_all$Count_1 == data_all$Count_2, 'TRUE', NA)))
  
data_all
```
#Counter accuracy
```{r}
#Compiling the data for accuracy
Data_Accuracy = data.frame(data_all$Replicate,data_all$Shell, data_all$Side,data_all$date_deployed, data_all$Site, data_all$Count_1, data_all$Count_2, data_all$results)

Data_Accuracy <- na.omit(Data_Accuracy)
Data_Accuracy

#count TRUE values in vector
x <- Data_Accuracy %>% 
  dplyr::group_by(data_all.Site, data_all.Shell, data_all.Side, data_all.date_deployed, data_all.results) %>% 
  dplyr::summarise(count = n())
x2 <- x %>% 
  dplyr::group_by()
x
T <- nrow(Data_Accuracy %>% filter(data_all.results == 'TRUE'))
F <- nrow(Data_Accuracy %>% filter(data_all.results == 'FALSE'))

Accuracy <- T/(T+F)
Accuracy


```
#Ash creek summary
```{r}

df_ASHC<- data_all %>%
  filter(Site == "ASHC")
df_ASHC

st_rec_ASHC <- summarySE(df_ASHC, measurevar="Count_1", groupvars=c("Site", "date_collected", "Replicate"))
st_rec_ASHC

#Mean spat per shell per replicate
ASHC_spat <- df_ASHC %>%
  group_by(Replicate, Shell, date_collected) %>%
  summarize(sum_count_1 = sum(Count_1),sum_count_2 = sum(Count_2))
ASHC_spat

ASHC_spat_avg <- ASHC_spat %>%
  group_by(Replicate, date_collected)%>%
  summarize(Mean_1 = mean(sum_count_1), Mean_2 = mean(sum_count_2))
ASHC_spat_avg

ASHC_spat_avg2 <- ASHC_spat_avg %>%
  group_by(date_collected)%>%
  summarize(mean_1 = mean(Mean_1), mean_2 = mean(Mean_2))
ASHC_spat_avg2


```

#Fence Creek summary
```{r}
df_FENC<- data_all %>%
  filter(Site == "FENC")
df_FENC

st_rec_FENC <- summarySE(df_FENC, measurevar="Count_1", groupvars=c("Site", "date_collected", "Replicate"))
st_rec_FENC


#Mean spat per shell per replicate
FENC_spat <- df_FENC %>%
  dplyr::group_by(Replicate, Shell, date_collected) %>%
  dplyr::summarize(sum_count_1 = sum(Count_1),sum_count_2 = sum(Count_2))
FENC_spat

FENC_spat_avg <- FENC_spat %>%
  dplyr::group_by(Replicate, date_collected)%>%
 dplyr::summarize(Mean_1 = mean(sum_count_1), Mean_2 = mean(sum_count_2))
FENC_spat_avg

FENC_spat_avg2 <- FENC_spat_avg %>%
  dplyr::group_by(date_collected)%>%
  dplyr::summarize(mean_1 = mean(Mean_1), mean_2 = mean(Mean_2))
FENC_spat_avg2
```

#Gold star beach summary
```{r}
df_GOLD<- data_all %>%
  filter(Site == "GOLD")

st_rec_GOLD <- summarySE(df_GOLD, measurevar="Count_1", groupvars=c("Site", "date_collected", "Replicate"))
st_rec_GOLD
```

#Laurel Hollow summary
```{r}
df_LAUR<- data_all %>%
  filter(Site == "LAUR")
df_LAUR
st_rec_LAUR <- summarySE(df_LAUR, measurevar="Count_1", groupvars=c("Site", "date_collected", "Replicate"))
st_rec_LAUR

#Mean spat per shell per replicate
LAUR_spat <- df_LAUR %>%
  group_by(Replicate, Shell, date_collected) %>%
  summarize(sum_count_1 = sum(Count_1),sum_count_2 = sum(Count_2))
LAUR_spat

LAUR_spat_avg <- LAUR_spat %>%
  group_by(Replicate, date_collected)%>%
  summarize(Mean_1 = mean(sum_count_1), Mean_2 = mean(sum_count_2))
LAUR_spat_avg

LAUR_spat_avg2 <- LAUR_spat_avg %>%
  group_by(date_collected)%>%
  summarize(mean_1 = mean(Mean_1), mean_2 = mean(Mean_2))
LAUR_spat_avg2
```






```{r}
sessionInfo()
```

